%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% The cruft above tells TeX editors (e.g. TeXShop) what this file contains.

%% Only tested with XeLaTeX.
%\RequireXeTeX

%% Unicode normalization of input text.
%%  0: no normalization (default)
%%  1: normalize to NFC
%%  2: normalize to NFD
\XeTeXinputnormalization 1

%% FIle prefix.
%% This is the unchanging part of all file names for this document.
\def \FILEPREFIX {verb-prefixes}

%% The Memoir class.
%% The manual is memman.pdf.
\documentclass[12pt,letterpaper,landscape,oneside,article]{memoir}

%% LaTeX3 command parsing.
%% Should be used by all modern, right thinking LaTeX programmers.
\usepackage{xparse}

%%%
%%% Memoir configuration.
%%%

\input{\FILEPREFIX-memconf}

%%%
%%% Font configuration.
%%%

\input{\FILEPREFIX-fonts}
\input{\FILEPREFIX-fonts-symbols}

%%%
%%% Bibliography configuration.
%%%

\input{\FILEPREFIX-bib}

%%%
%%% Example and glossing configuration.
%%%

\input{\FILEPREFIX-expex}

%%%
%%% Other packages.
%%%
\input{\FILEPREFIX-other}

%%%
%%% Hyperlinks and crossreferences.
%%%

\input{\FILEPREFIX-hyper}

%%%
%%% Miscellaneous macrology.
%%%

\input{\FILEPREFIX-macrology}

%% Questionable form marker.
%%
%% To be used at the end of a cell in a table. Uses \rlap to float it into
%% the following intercolumn space without affecting column alignment. This
%% overwrites the original \? command (for ¿) which we don’t need.
\DeclareDocumentCommand \supques {} {\textsuperscript*{\textbf{?}}}
\DeclareDocumentCommand \? {} {\rlap{\supques}}

%%%
%%% Colour macrology.
%%%
\RequirePackage{xcolor}

% Colour definitions.
% qualifiers
\definecolor{Qcolor}{rgb}{0.00,0.33,0.33}
% irrealis
\definecolor{Rcolor}{rgb}{0.90,0.50,0.50}
% irrealis coalescence
\definecolor{rcolor}{rgb}{1.00,0.95,0.95}
% aspect/conjugation
\definecolor{Acolor}{rgb}{0.70,0.40,0.00}
% aspect/conjugation coalescence
\definecolor{acolor}{rgb}{1.00,1.00,0.85}
% modality
\definecolor{Mcolor}{rgb}{0.00,0.66,0.66}
% modality coalescence
\definecolor{mcolor}{rgb}{0.90,1.00,1.00}
% subject
\definecolor{Scolor}{rgb}{0.50,0.00,0.66}
% d- prefix
\definecolor{Dcolor}{rgb}{0.00,0.00,0.75}
% d- prefix deletion
\definecolor{dcolor}{rgb}{0.90,0.90,1.00}
% s-/l-/sh- prefix
\definecolor{Fcolor}{rgb}{0.00,0.50,0.00}
% i- prefix
\definecolor{Icolor}{rgb}{0.75,0.00,0.00}
% epenthesis
\definecolor{Ecolor}{rgb}{0.75,0.75,0.75}
% deletion or coalescence
\definecolor{Xcolor}{rgb}{0.97,0.97,0.97}

% Uncomment to make everything black.
%\definecolor{Qcolor}{rgb}{0.00,0.00,0.00}
%\definecolor{Rcolor}{rgb}{0.00,0.00,0.00}
%\definecolor{Acolor}{rgb}{0.00,0.00,0.00}
%\definecolor{Mcolor}{rgb}{0.00,0.00,0.00}
%\definecolor{Scolor}{rgb}{0.00,0.00,0.00}
%\definecolor{Dcolor}{rgb}{0.00,0.00,0.00}
%\definecolor{Fcolor}{rgb}{0.00,0.00,0.00}
%\definecolor{Icolor}{rgb}{0.00,0.00,0.00}
%\definecolor{Ecolor}{rgb}{0.00,0.00,0.00}

% Uncomment to make everything light grey.
%\definecolor{Qcolor}{rgb}{0.90,0.90,0.90}
%\definecolor{Rcolor}{rgb}{0.90,0.90,0.90}
%\definecolor{Acolor}{rgb}{0.90,0.90,0.90}
%\definecolor{Mcolor}{rgb}{0.90,0.90,0.90}
%\definecolor{Scolor}{rgb}{0.90,0.90,0.90}
%\definecolor{Dcolor}{rgb}{0.90,0.90,0.90}
%\definecolor{Fcolor}{rgb}{0.90,0.90,0.90}
%\definecolor{Icolor}{rgb}{0.90,0.90,0.90}
%\definecolor{Ecolor}{rgb}{0.90,0.90,0.90}

%% A strut with 90 percent of normal height and width for the colorbox.
%% See http://tex.stackexchange.com/questions/74459/remove-space-before-colorbox
\ProvideDocumentCommand \colorboxstrut {} {\vrule width 0pt height 0.9\ht\strutbox depth 0.9\dp\strutbox\relax}

\ProvideDocumentCommand \Qf {m} {\textcolor{Qcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \Rf {m} {\textcolor{Rcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \rf {m} {\setlength{\fboxsep}{0pt}\colorbox{rcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \Af {m} {\textcolor{Acolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \af {m} {\setlength{\fboxsep}{0pt}\colorbox{acolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \Mf {m} {\textcolor{Mcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \mf {m} {\setlength{\fboxsep}{0pt}\colorbox{mcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \Sf {m} {\textcolor{Scolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \Df {m} {\textcolor{Dcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \Ff {m} {\textcolor{Fcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \If {m} {\textcolor{Icolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \Xf {m} {\setlength{\fboxsep}{0pt}\colorbox{Xcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \df {m} {\setlength{\fboxsep}{0pt}\colorbox{dcolor}{\colorboxstrut{}#1}}
\ProvideDocumentCommand \Ef {m} {\textcolor{Ecolor}{\colorboxstrut{}#1}}

%%%
%%% The document.
%%%
\begin{document}
\pagestyle{mine}

\title{Tlingit verb prefix paradigms}
\author{\textit{Dzéiwsh} James A.\ Crippen}
\maketitle

\begin{KeepFromToc}
\tableofcontents
\end{KeepFromToc}

\section{Introduction}\label{sec:intro}

\begin{multicols}{2}
\noindent
This document aims to provide a relatively exhaustive list of verb prefix paradigms in Tlingit.
It details all the basic patterns of possible combinations of verb prefixes including
the classifier prefixes (\fm{\Df{d}-}, \fm{\Ff{s}-}/\fm{\Ff{l}-}/\fm{\Ff{sh}-}, \fm{\If{i}-}),%
\footnote{Currently only the \fm{\Ff{s}-} /\ipa{\Ff{s}}/ prefix is represented in this document.
	The \fm{\Ff{l}-} /\ipa{\Ff{ɬ}}/ and \fm{\Ff{sh}-} /\ipa{\Ff{ʃ}}/ prefixes have phonological patterns that are essentially identical to \fm{\Ff{s}-} /\ipa{\Ff{s}}/.
	There are orthographic differences –
		e.g.{}
		\fm{\Df{d}-} + \fm{\Ff{l}-} + \fm{\If{i}-} → \fm{\Df{d}\Ff{l}\If{i}} /\ipa{\Df{t}\Ff{ɬ}\If{i}}/ 
		versus
		\fm{\Df{d}-} + \fm{\Ff{sh}-} + \fm{\If{i}-} → \fm{\df{\hspace{0.25ex}\Ff{j}}\If{i}} /\ipa{\Df{t}\Ff{ʃ}\If{i}}/
	– but these do not have any phonological consequences.
	Because of this the \fm{\Ff{l}-} /\ipa{\Ff{ɬ}}/ and \fm{\Ff{sh}-} /\ipa{\Ff{ʃ}}/ prefixes have been omitted (they would triple the size of this document), but a future revision may eventually include them.}
the subject prefixes (\fm{\Sf{x̱}-} \xx{1sg}, \fm{\Sf{tu}-} \xx{1pl}, \fm{\Sf{i}-} \xx{2sg}, \fm{\Sf{yi}-} \xx{2pl}, \fm{\Sf{du}-} \xx{4h}),
the aspect and conjugation prefixes (\fm{\Af{wu}-} \xx{pfv}, \fm{\Af{u}-} \xx{zpfv}, \fm{\Af{∅}} \xx{zcnj}, \fm{\Af{n}-} \xx{ncnj}, \fm{\Af{g̱}-} \xx{g̱cnj}, \fm{\Af{g}-} \xx{gcnj}),
the irrealis prefixes (\fm{\Rf{u}-}, \fm{\Rf{w}-}),
the modality prefix (\fm{\Mf{g̱}-}),
the 3>3 argument/expletive prefix (\fm{\Qf{a}-}),
and the four vowel patterns of CV prefixes in the Disjunct domain (\fm{\Qf{ka}-} qualifier, \fm{\Qf{x̱ʼe}-} ‘mouth’, \fm{\Qf{ji}-} ‘hand’, \fm{\Qf{tu}-} ‘inside’).
Every grammatically possible combination of these prefixes is demonstrated in this document.
The forms given here can be used to reliably predict forms using other prefixes like \fm{\Qf{se}-} ‘voice’ (like \fm{\Qf{x̱ʼe}-}), \fm{\Qf{ya}-} qualifier (like \fm{\Qf{ka}-}), and \fm{\Qf{i}-} \xx{2sg·o} (like \fm{\Qf{ji}-}).
Each type of prefix is colour-coded consistently throughout this document so that they can be more easily identified in the surface forms that result from the various prefix combinations.
This colour coding is only meant as a guide and should not be taken as a verified phonological analysis of underlying and surface correspondences.

This document is intended as a reference and aims to be brief but authoritative.
The primary audiences for this document are advanced language learners and linguists.
Explanations of the functions, meanings, and forms of the verb prefixes are beyond the scope of this document.

The initial versions of this document reflect only the most well documented patterns attested in Coastal Northern dialects of Tlingit spoken in northern parts of Southeast Alaska.
These are the typical forms found in most of the Dauenhauers’ transcriptions and in language teaching materials.
Other varieties of Tlingit – Inland Northern, Gulf Coast Northern, Transitional Northern, Sanya, Henya, and Tongass – are known to have different phonological patterns with the same sets of prefixes.
These will be documented in future versions of this document.

All prefixes in every table and example are coloured according to the list below. Plain black has no specific meaning.

\begin{itemize}[leftmargin=0.75em]\raggedyright
\item	\Qf{disjunct prefix}
	— any qualifier prefix (\fm{\Qf{ka}-}, \fm{\Qf{ya}-}),
	incorporated noun prefix (\fm{\Qf{tu}-}, \fm{\Qf{sha}-}, etc.),
	or object prefix (\fm{\Qf{i}-}, \fm{\Qf{a}-}, etc.)
\item	\Rf{irrealis prefix}
	– one of the irrealis prefixes \fm{\Rf{u}-} or \fm{\Rf{w}-}
\item	\Af{aspect prefix}
	– one of the perfective prefixes (\fm{\Af{wu}-}, \fm{\Af{u}-})
	or conjugation prefixes (\fm{\Af{n}-}, \fm{\Af{g̱}-}, \fm{\Af{g}-})
\item	\Mf{modality prefix}
	– the modality prefix \fm{\Mf{g̱}-}
\item	\Sf{subject prefix}
	– any subject prefix (\fm{\Sf{x̱}-}, \fm{\Sf{tu}-}, \fm{\Sf{i}-}, \fm{\Sf{yi}-}, \fm{\Sf{du}-})
\item	\Df{classifier \fm{d-} prefix}
	– the \fm{\Df{d}-} prefix of passive, antipassive, or middle voice
\item	\Ff{classifier \fm{s-}/\fm{l-}/\fm{sh-} prefix}
	– any of the \fm{\Ff{s}-}, \fm{\Ff{l}-}, or \fm{\Ff{sh}-} prefixes
\item	\If{classifier \fm{i-} prefix}
	– the stative \fm{\If{i}-} prefix
\item	\Ef{epenthesis}
	– insertion of a meaningless vowel or consonant to adjust syllable structure
\end{itemize}

In addition to the prefix colours above, there are also background shades used to indicate the complete or partial loss of material in surface forms.

\begin{itemize}[leftmargin=0.75em]
\item	\rf{irrealis coalescence}
	– coalescence of an irrealis prefix with some other prefix
\item	\af{aspect coalescence}
	– coalescence of an aspect prefix with some other prefix
\item	\mf{modality coalescence}
	– coalescence of the \fm{\Mf{g̱}-} modality prefix with some other prefix
\item	\df{classifier \fm{d-} deletion}
	– deletion of the \fm{\Df{d}-} prefix when one of \fm{\Ff{s}-}, \fm{\Ff{l}-}, or \fm{\Ff{sh}-} is present and \fm{\If{i}-} is absent
\item	\Xf{unspecified deletion or coalescence}
	– any other unexpected disappearance of a prefix (eventually coded with separate colours)
\end{itemize}

Only some of the logically possible combinations of prefixes are permitted by the grammar of Tlingit.
Combinations of prefixes that are known to be grammatically prohibited are indicated by an ungrammaticality star ‘⁎’.
For example, any combination of \fm{\Sf{du}-} + \fm{\Ff{s}-} without \fm{\Df{d}-} is known to be ungrammatical in all varieties of Tlingit.
Any cell where this combination would occur is filled with ‘⁎’.

Some combinations of prefixes are logically predicted but are not attested in any existing documentary material.
These unverified forms are followed by a superscript question mark ‘\hspace{0.125ex}\supques{}\hspace{0.125ex}’.
For example, it is logically possible that a verb could have the expletive \fm{\Qf{a}-} prefix, the first person singular subject \fm{\Sf{x̱}-} ‘I’, and the three classifier prefixes \fm{\Df{d}-}, \fm{\Ff{s}-}, and \fm{\If{i}-}, and the predicted form would be \fm{\Qf{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}}\supques{} [\ipa{\Qf{ʔà}\Sf{χ}.\Df{t}\Ff{s}\If{ì}}]\supques{}, but there are currently no examples of this in the existing documentation of Tlingit.
Researchers should generally treat questioned forms as possible until future investigation shows otherwise.

Each section is devoted to one major paradigmatic pattern.
The first section gives the unmarked aspect pattern which covers forms that lack an overt aspectual prefix (sec.\ \ref{sec:zero}), i.e.\ neither a perfective prefix \fm{\Af{wu}-} or \fm{\Af{u}-} nor an overt conjugation prefix \fm{\Af{n}-}, \fm{\Af{g̱}-}, or \fm{\Af{g}-}.
The next three sections are patterns with each of the overt conjugation prefixes \fm{\Af{n}-} (sec.\ \ref{sec:nconj}), \fm{\Af{g̱}-} (sec.\ \ref{sec:ghconj}), and \fm{\Af{g}-} (sec.\ \ref{sec:gconj}).
Following these are two sections for the distinct patterns of the perfective aspect (sec.\ \ref{sec:pfv}) and the prospective aspect (sec.\ \ref{sec:prosp}).

Each section is divided up into subsections reflecting the prefixes that accompany the aspectual prefixes, namely the irrealis prefix \fm{\Rf{u}-} and the modality prefix \fm{\Mf{g̱}-}.
The section body gives forms with no irrealis prefix and no modality prefix.
The first subsection gives forms with the irrealis prefix \fm{\Rf{u}-}, the second subsection gives forms with the modality prefix \fm{\Mf{g̱}-}, and the third subsection gives forms with both.
The perfective and prospective aspect sections do not include any subsections.
For the perfective aspect this is because neither the irrealis prefix nor the modality prefix can be detected.
For the prospective aspect this is because both the irrealis prefix \fm{\Rf{w}-} and the modality prefix \fm{\Mf{g̱}-} are obligatory.

Each set of tables in a section or subsection is organized by subject prefix.
The tables are given in pairs, first using the orthography and second using the IPA, with both on the same page.
The first pair of tables in each section or subsection gives forms where there either is no subject (object intransitives) or where the subject is third person and thus not indicated with a subject prefix.
The next two pairs of tables give the first person singular subject \fm{\Sf{x̱}-} ‘I’ and first person plural subject \fm{\Sf{tu}-} ‘we’.
Then the following two pairs of tables give the second person singular subject \fm{\Sf{i}-} ‘you sg.’ and second person plural subject \fm{\Sf{yi} -} ‘you guys’.
Finally, the last pair of tables gives the fourth person (indefinite, nonspecific) human subject \fm{\Sf{du}-} ‘someone, people, they’.

Absence of a form is indicated explicitly by an em-dash ‘—’.
This applies to both the prefix listings in the left hand columns as well as to the classifier prefixes in the table headers.
There is exactly one case where the surface form is nothing at all, namely the unmarked aspect without irrealis or modality prefixes and with no overt subject, and this case is represented by ‘—’.
All blank areas in the tables are continuation lines as discussed in the next paragraph.

Lines with blank space in the first columns are continuations of a preceding line.
These lines show documented variations of forms in the preceding line.
The lack of a documented variant is left blank in the surface forms to avoid confusing this with a surface form that has no content.
Although it would be nice to list the specific conditioning factors where these are known, in most cases this is difficult to represent concisely.
The sole exception to this is an initial ‘…’ which indicates that the variant form occurs when preceded by a word ending with an open syllable.
Some of the conditioning factors are explained in Leer 1991, but in many cases the reasons for variation are still unexplored.

The IPA data intentionally omit tone marking.
All varieties of Northern Tlingit contrast high and low tone.
But all of the verb prefixation paradigms given here predictably have only low tone vowels.
Readers should infer low tone /à, ì, è, ù/ on every vowel symbol in the IPA representations.
Note that Southern varieties of Tlingit (Sanya, Henya) may have high tone on some syllables in the verb prefix complex.
Because this document does not yet include data for any Southern varieties, there is no potential for confusion.

\FIXME{Disjunct prefixes that are closed syllables like \fm{\Qf{waḵ}-} ‘eye’ or \fm{\Qf{sʼaan-}} ‘limb’ will have the same result as no prefix.
Disjunct prefixes that are open syllables with long vowels like \fm{\Qf{daa}-} ‘around’ will behave like \fm{\Qf{ka}-}.}

\FIXME{Why we include \fm{\Qf{a}-} even when it’s not third person – it’s possible as an expletive or ‘dummy’ object.}

\FIXME{In the future we will develop tables for specific aspect paradigms, e.g.\ a table of \fm{n}-conjugation hortatives with \fm{\Af{n}-} + \fm{\Mf{g̱}-} and a table of \fm{g}-conjugation potentials with \fm{\Rf{u}-} + \fm{\Af{g}-} + \fm{\Mf{g̱}-}. This will cut down on the number of forms per table because e.g.\ hortatives must lack \fm{\If{i}-} and potentials must include \fm{\If{i}-}. It should be straightforward – though slow – to derive those paradigm tables from the purely combinatorial tables here.}
\end{multicols}

\clearpage
%%%
%%% Unmarked aspect.
%%%

\section{Unmarked aspect: imperfective or \textit{∅}-conjugation prefix}\label{sec:zero}

\begin{multicols}{2}
\noindent
Unmarked aspect is any form without an overt aspect prefix, i.e.\ no perfective prefix (\fm{\Af{wu}-} or \fm{\Af{u}-}) and no overt conjugation prefix (\fm{\Af{n}-}, \fm{\Af{g̱}-}, or \fm{\Af{g}-}).
Typical cases of unmarked aspect include imperfective aspect forms and imperative mood forms.
The simplest case of unmarked aspect is the imperfective aspect form of most activity and state verbs like the examples of an imperfective activity and an imperfective state in (\ref{ex:zero-imperfectives}).

\pex\label{ex:zero-imperfectives}%
\a\label{ex:zero-imperfectives-activity}%
\exrtcmt{∅-imperfective activity}%
\begingl
	\gla	\rlap{\Sf{Yi}x̱á.} @ {} @ {} @ {} //
	\glb	{} \Sf{yi}- \rt[²]{x̱a} -μH //
	\glc	{} \Sf{\xx{2pl·s}}- \rt[²]{eat} -\xx{var} //
	\gld	\rlap{3.\xx{impfv}.you·\xx{pl}.eat} {} {} {} //
	\glft	‘You guys eat him/her/it.’, ‘You guys are eating him/her/it.’
		//
\endgl
\a\label{ex:zero-imperfectives-state}%
\exrtcmt{∅-imperfective state}%
\begingl
	\gla	\rlap{\Qf{I}\Sf{tu}\If{w}\Ef{a}téen.} @ {} @ {} @ {} @ {} //
	\glb	\Qf{i}- \Sf{tu}- \If{i}- \rt[²]{tin} -μH //
	\glc	\Qf{\xx{2sg·o}}- \Sf{\xx{1pl·s}}- \If{\xx{stv}}- \rt[²]{see} -\xx{var} //
	\gld	\rlap{you·\xx{sg}.\xx{impfv}.we.can·see} {} {} {} {} {} //
	\glft	‘We can see you.’
		//
\endgl
\xe

Imperfective aspect forms like those in (\ref{ex:zero-imperfectives}) have no overt prefix for aspect since they have neither a perfective prefix \fm{\Af{wu}-} or \fm{\Af{u}-} nor an overt conjugation prefix \fm{\Af{n}-}, \fm{\Af{g̱}-}, or \fm{\Af{g}-}.
It is possible to analyze imperfectives as having a \fm{\Af{∅}} conjugation prefix, but it is equally possible to analyze them as having no aspect prefix.
Both analyses give rise to the same verb forms so for verb prefix phonology and verb paradigm patterns the difference between these two analyses is irrelevant.

Another simple case of unmarked aspect is the imperative mood form of verbs that belong to the \fm{∅}-conjugation class.
Imperative mood selects a prefix corresponding to the conjugation class membership of the verb.
Thus a verb belonging to the \fm{n}-conjugation class will contain a \fm{\Af{n}-} conjugation prefix, and similarly a verb of the \fm{g}-conjugation class will contain a \fm{\Af{g}-} conjugation prefix.
For a \fm{∅}-conjugation class verb the imperative simply lacks a conjugation prefix.
This lack of a prefix is analyzed as the \fm{\Af{∅}} conjugation prefix.
Compare the \fm{∅}-conjugation class imperative in (\ref{ex:zero-imperatives-z}) with the other three conjugation class imperatives in (\ref{ex:zero-imperatives-n})–(\ref{ex:zero-imperatives-g}).

\pex\label{ex:zero-imperatives}%
\a\label{ex:zero-imperatives-z}%
\exrtcmt{∅-conjugation imperative}%
\begingl
	\gla	\rlap{\Sf{Yi}jáḵ!} @ {} @ {} @ {} //
	\glb	\Af{∅} \Sf{yi}- \rt[²]{jaḵ} -μH //
	\glc	\Af{\xx{zcnj}}\· \Sf{\xx{2pl·s}}- \rt[²]{kill} -\xx{var} //
	\gld	\rlap{3.\xx{imp}.you·\xx{pl}.kill} {} {} {} //
	\glft	‘You guys kill him/her/it!’
		//
\endgl
\a\label{ex:zero-imperatives-n}%
\exrtcmt{n-conjugation imperative}%
\begingl
	\gla	\rlap{\Af{N}\Ef{a}\Sf{y}hoon!} @ {} @ {} @ {} //
	\glb	\Af{n}- \Sf{yi}- \rt[²]{hun} -μμL //
	\glc	\Af{\xx{ncnj}}- \Sf{\xx{2pl·s}}- \rt[²]{sell} -\xx{var} //
	\gld	\rlap{3.\xx{imp}.you·\xx{pl}.sell} {} {} {} //
	\glft	‘You guys sell him/her/it!’
		//
\endgl
\a\label{ex:zero-imperatives-gh}%
\exrtcmt{g̱-conjugation imperative}%
\begingl
	\gla	\rlap{\Af{G̱}\Ef{a}\Sf{y}x̱oox̱!} @ {} @ {} @ {} //
	\glb	\Af{g̱}- \Sf{yi}- \rt[²]{x̱ux̱} -μμL //
	\glc	\Af{\xx{g̱cnj}}- \Sf{\xx{2pl·s}}- \rt[²]{summon} -\xx{var} //
	\gld	\rlap{3.\xx{imp}.you·\xx{pl}.summon} {} {} {} //
	\glft	‘You guys summon him/her/it!’
		//
\endgl
\a\label{ex:zero-imperatives-g}%
\exrtcmt{g-conjugation imperative}%
\begingl
	\gla	\rlap{\Af{G}\Ef{a}\Sf{y}shí!} @ {} @ {} @ {} //
	\glb	\Af{g}- \Sf{yi}- \rt[²]{shiʰ} -μμL //
	\glc	\Af{\xx{gcnj}}- \Sf{\xx{2pl·s}}- \rt[²]{sing} -\xx{var} //
	\gld	\rlap{3.\xx{imp}.you·\xx{pl}.sing} {} {} {} //
	\glft	‘You guys sing him/her/it!’
		//
\endgl
\xe

\FIXME{List of all environments in which unmarked aspect forms can occur: imperfective (including activity, state, repetitive), imperative, realizational, consecutive, conditional, hortative, contingent, admonitive, potential. Note combinations with negation or prohibitive/optative that would introduce irrealis \fm{\Rf{u}-}.}
\end{multicols}

\clearpage
%% Zero, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&		&\multicolumn{8}{c}{Classifier prefixes}\\
									\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes	&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			& —		& —		& —		&\Df{d}\Ff{z}\If{i}		&\Df{d}\If{i}				&\Ff{s}\If{i}				&\Df{d}\Ef{a}				&\Ef{i}\df{\Ff{s}}			&\Ff{s}\Ef{a}				&\If{y}\Ef{a}				&—\\
\Qf{a}- arg./expl.	& —		& —		&\Qf{a}-	&\Qf{a}\Df{d}\Ff{z}\If{i}	&\Qf{a}\Df{d}\If{i}			&\Qf{a}\Ff{s}\If{i}			&\Qf{a}\Df{d}\Ef{a}			&\Qf{a}\df{\Ff{s}}			&\Qf{a}\Ff{s}				&\Qf{a}\If{y}\Ef{a}			&\Qf{a}\\
\Qf{ka}- qualifier	& —		& —		&\Qf{ka}-	&\Qf{ka}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\Df{d}\If{i}			&\Qf{ka}\Ff{s}\If{i}			&\Qf{ka}\Df{d}\Ef{a}			&\Qf{ka}\df{\Ff{s}}			&\Qf{ka}\Ff{s}\Ef{a}			&\Qf{ka}\If{y}\Ef{a}			&\Qf{ka}\\
			&		&		&		&				&					&					&					&					&					&\Qf{ka}\If{a}				&\\
\Qf{x̱ʼe}- ‘mouth’	& —		& —		&\Qf{x̱ʼe}-	&\Qf{x̱ʼa}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Df{d}\If{i}			&\Qf{x̱ʼa}\Ff{s}\If{i}			&\Qf{x̱ʼa}\Df{d}\Ef{a}			&\Qf{x̱ʼa}\df{\Ff{s}}			&\Qf{x̱ʼa}\Ff{s}\Ef{a}			&\Qf{x̱ʼa}\If{y}\Ef{a}			&\Qf{x̱ʼa}\\
			&		&		&		&				&					&					&					&					&					&\Qf{x̱ʼa}\If{a}				&\\
\Qf{ji}- ‘hand’		& —		& —		&\Qf{ji}-	&\Qf{ji}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\Df{d}\If{i}			&\Qf{ji}\Ff{s}\If{i}			&\Qf{ji}\Df{d}\Ef{a}			&\Qf{ji}\df{\Ff{s}}			&\Qf{ji}\Ff{s}\Ef{a}			&\Qf{ji}\If{y}\Ef{a}			&\Qf{ji}\\
\Qf{tu}- ‘inside’	& —		& —		&\Qf{tu}-	&\Qf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\Df{d}\If{i}			&\Qf{tu}\Ff{s}\If{i}			&\Qf{tu}\Df{d}\Ef{a}			&\Qf{tu}\df{\Ff{s}}			&\Qf{tu}\Ff{s}\Ef{a}			&\Qf{tu}\If{w}\Ef{a}			&\Qf{tu}\\
			&		&		&		&				&					&					&					&					&					&\Qf{tu}\If{y}\Ef{a}			&\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), unmarked subject (third person or no subject)}
\end{table}

%% Zero, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&		&\multicolumn{8}{c}{Classifier prefixes}\\
									\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes	&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-		&\Df{t}-\Ff{s}\rlap{-}	&\Ff{s}-		&\If{i}-		&—\\
\midrule
—			& —		& —		& —		&\Df{t}\Ff{s}\If{i}		&\Df{t}\If{i}		&\Ff{s}\If{i}		&\Df{t}\Ef{a}		&\Ef{ʔi}\df{\Ff{s}}	&\Ff{s}\Ef{a}		&\If{j}\Ef{a}		&—\\
\Qf{ʔa}- arg./expl.	& —		& —		&\Qf{ʔa}-	&\Qf{ʔa}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔa}.\Df{t}\If{i}	&\Qf{ʔa}.\Ff{s}\If{i}	&\Qf{ʔa}.\Df{t}\Ef{a}	&\Qf{ʔa}\df{\Ff{s}}	&\Qf{ʔa}\Ff{s}		&\Qf{ʔa}.\If{j}\Ef{a}	&\Qf{ʔa}\\
\Qf{kʰa}- qualifier	& —		& —		&\Qf{kʰa}-	&\Qf{kʰa}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}.\Df{t}\If{i}	&\Qf{kʰa}.\Ff{s}\If{i}	&\Qf{kʰa}.\Df{t}\Ef{a}	&\Qf{kʰa}\df{\Ff{s}}	&\Qf{kʰa}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\If{j}\Ef{a}	&\Qf{kʰa}\\
			&		&		&		&				&			&			&			&			&			&\Qf{kʰa}\If{ː}		&\\
\Qf{χʼe}- ‘mouth’	& —		& —		&\Qf{χʼe}-	&\Qf{χʼa}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}.\Df{t}\If{i}	&\Qf{χʼa}.\Ff{s}\If{i}	&\Qf{χʼa}.\Df{t}\Ef{a}	&\Qf{χʼa}\df{\Ff{s}}	&\Qf{χʼa}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\If{j}\Ef{a}	&\Qf{χʼa}\\
			&		&		&		&				&			&			&			&			&			&\Qf{χʼa}\If{ː}		&\\
\Qf{tʃi}- ‘hand’	& —		& —		&\Qf{tʃi}-	&\Qf{tʃi}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}.\Df{t}\If{i}	&\Qf{tʃi}.\Ff{s}\If{i}	&\Qf{tʃi}.\Df{t}\Ef{a}	&\Qf{tʃi}\df{\Ff{s}}	&\Qf{tʃi}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\If{j}\Ef{a}	&\Qf{tʃi}\\
\Qf{tʰu}- ‘inside’	& —		& —		&\Qf{tʰu}-	&\Qf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}.\Df{t}\If{i}	&\Qf{tʰu}.\Ff{s}\If{i}	&\Qf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}\df{\Ff{s}}	&\Qf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\If{w}\Ef{a}	&\Qf{tʰu}\\
			&		&		&		&				&			&			&			&			&			&\Qf{tʰu}.\If{j}\Ef{a}	&\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), unmarked subject (third person or no subject), IPA}
\end{table}

%% Zero, 1SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&—		&\Sf{x̱}-	&\Sf{x̱}-		&\Sf{x̱}\Ef{a}\Df{d}\Ff{z}\If{i}		&\Sf{x̱}\Ef{a}\Df{d}\If{i}	&\Sf{x̱}\Ef{a}\Ff{s}\If{i}	&\Sf{x̱}\Ef{a}\Df{d}\Ef{a}	&\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Sf{x̱}\Ef{a}\Ff{s}\Ef{a}	&\Sf{x̱}\Ef{a}\If{y}\Ef{a}	&\Sf{x̱}\Ef{a}\\
			&		&		&			&					&				&				&				&					&				&\Sf{x̱}\Ef{a}\If{a}		&\\
\Qf{a}- expletive	&—		&\Sf{x̱}-	&\Qf{a}-\Sf{x̱}-		&\Qf{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Sf{x̱}\Df{d}\If{i}	&\Qf{a}\Sf{x̱}\Ff{s}\If{i}	&\Qf{a}\Sf{x̱}\Df{d}\Ef{a}\?	&\Qf{a}\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Qf{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{a}\Sf{x̱}\Ef{a}\If{a}	&\Qf{a}\Sf{x̱}\Ef{a}\\
\Qf{ka}- qualifier	&—		&\Sf{x̱}-	&\Qf{ka}-\Sf{x̱}-	&\Qf{ka}\Sf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\Sf{x̱}\Df{d}\If{i}	&\Qf{ka}\Sf{x̱}\Ff{s}\If{i}	&\Qf{ka}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{ka}\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Qf{ka}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{ka}\Sf{x̱}\Ef{a}\If{a}	&\Qf{ka}\Sf{x̱}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&—		&\Sf{x̱}-	&\Qf{x̱ʼe}-\Sf{x̱}-	&\Qf{x̱ʼa}\Sf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Sf{x̱}\Df{d}\If{i}	&\Qf{x̱ʼa}\Sf{x̱}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Sf{x̱}\Ef{a}\If{a}	&\Qf{x̱ʼa}\Sf{x̱}\Ef{a}\\
\Qf{ji}- ‘hand’		&—		&\Sf{x̱}-	&\Qf{ji}-\Sf{x̱}-	&\Qf{ji}\Sf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\Sf{x̱}\Df{d}\If{i}	&\Qf{ji}\Sf{x̱}\Ff{s}\If{i}	&\Qf{ji}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{ji}\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Qf{ji}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{ji}\Sf{x̱}\Ef{a}\If{a}	&\Qf{ji}\Sf{x̱}\Ef{a}\\
\Qf{tu}- ‘inside’	&—		&\Sf{x̱}-	&\Qf{tu}-\Sf{x̱}-	&\Qf{tu}\Sf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\Sf{x̱}\Df{d}\If{i}	&\Qf{tu}\Sf{x̱}\Ff{s}\If{i}	&\Qf{tu}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{tu}\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Qf{tu}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{tu}\Sf{x̱}\Ef{a}\If{a}	&\Qf{tu}\Sf{x̱}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), first person singular subject \textit{x̱-}}
\end{table}

%% Zero, 1SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-			&—\\
\midrule
—			&—		&\Sf{χ}-	&\Sf{χ}-		&\Sf{χ}\Ef{a}.\Df{t}\Ff{s}\If{i}		&\Sf{χ}\Ef{a}.\Df{t}\If{i}		&\Sf{χ}\Ef{a}.\Ff{s}\If{i}		&\Sf{χ}\Ef{a}.\Df{t}\Ef{a}		&\Sf{χ}\Ef{a}.\df{\Ff{s}}		&\Sf{χ}\Ef{a}.\Ff{s}\Ef{a}		&\Sf{χ}\Ef{a}.\If{j}\Ef{a}	&\Sf{χ}\Ef{a}\\
			&		&		&			&						&					&					&					&					&					&\Sf{χ}\Ef{a}\If{ː}		&\\
\Qf{ʔa}- arg./expl.	&—		&\Sf{χ}-	&\Qf{ʔa}-\Sf{χ}-	&\Qf{ʔa}\Sf{χ}.\Df{t}\Ff{s}\If{i}\?		&\Qf{ʔa}\Sf{χ}.\Df{t}\If{i}		&\Qf{ʔa}\Sf{χ}.\Ff{s}\If{i}		&\Qf{ʔa}\Sf{χ}.\Df{t}\Ef{a}\?		&\Qf{ʔa}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}\Sf{χ}.\Ff{s}\Ef{a}		&\Qf{ʔa}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{ʔa}.\Sf{χ}\Ef{a}\\
\Qf{kʰa}- qualifier	&—		&\Sf{χ}-	&\Qf{kʰa}-\Sf{χ}-	&\Qf{kʰa}\Sf{χ}.\Df{t}\Ff{s}\If{i}		&\Qf{kʰa}\Sf{χ}.\Df{t}\If{i}		&\Qf{kʰa}\Sf{χ}.\Ff{s}\If{i}		&\Qf{kʰa}\Sf{χ}.\Df{t}\Ef{a}		&\Qf{kʰa}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}\Sf{χ}.\Ff{s}\Ef{a}		&\Qf{kʰa}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{kʰa}.\Sf{χ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&—		&\Sf{χ}-	&\Qf{χʼe}-\Sf{χ}-	&\Qf{χʼa}\Sf{χ}.\Df{t}\Ff{s}\If{i}		&\Qf{χʼa}\Sf{χ}.\Df{t}\If{i}		&\Qf{χʼa}\Sf{χ}.\Ff{s}\If{i}		&\Qf{χʼa}\Sf{χ}.\Df{t}\Ef{a}		&\Qf{χʼa}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}\Sf{χ}.\Ff{s}\Ef{a}		&\Qf{χʼa}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{χʼa}.\Sf{χ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&—		&\Sf{χ}-	&\Qf{tʃi}-\Sf{χ}-	&\Qf{tʃi}\Sf{χ}.\Df{t}\Ff{s}\If{i}		&\Qf{tʃi}\Sf{χ}.\Df{t}\If{i}		&\Qf{tʃi}\Sf{χ}.\Ff{s}\If{i}		&\Qf{tʃi}\Sf{χ}.\Df{t}\Ef{a}		&\Qf{tʃi}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}\Sf{χ}.\Ff{s}\Ef{a}		&\Qf{tʃi}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{tʃi}.\Sf{χ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&—		&\Sf{χ}-	&\Qf{tʰu}-\Sf{χ}-	&\Qf{tʰu}\Sf{χ}\Qf{ʷ}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}\Sf{χ}\Qf{ʷ}.\Df{t}\If{i}	&\Qf{tʰu}\Sf{χ}\Qf{ʷ}.\Ff{s}\If{i}	&\Qf{tʰu}\Sf{χ}\Qf{ʷ}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}\Sf{χ}\Qf{ʷ}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{tʰu}.\Sf{χ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), first person singular subject /{χ-}/, IPA}
\end{table}

\clearpage
%% Zero, 1PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&—		&\Sf{tu}-	&\Sf{tu}-		&\Sf{tu}\Df{d}\Ff{z}\If{i}		&\Sf{tu}\Df{d}\If{i}		&\Sf{tu}\Ff{s}\If{i}		&\Sf{tu}\Df{d}\Ef{a}		&\Sf{too}\df{\Ff{s}}		&\Sf{tu}\Ff{s}\Ef{a}		&\Sf{tu}\If{w}\Ef{a}		&\Sf{too}\\
\Qf{a}- expletive	&—		&\Sf{tu}-	&\Qf{a}-\Sf{tu}-	&\Qf{a}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Sf{tu}\Df{d}\If{i}	&\Qf{a}\Sf{tu}\Ff{s}\If{i}	&\Qf{a}\Sf{tu}\Df{d}\Ef{a}	&\Qf{a}\Sf{too}\df{\Ff{s}}	&\Qf{a}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{a}\Sf{tu}\If{w}\Ef{a}	&\Qf{a}\Sf{too}\\
\Qf{ka}- qualifier	&—		&\Sf{tu}-	&\Qf{ka}-\Sf{tu}-	&\Qf{ka}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\Sf{tu}\Df{d}\If{i}	&\Qf{ka}\Sf{tu}\Ff{s}\If{i}	&\Qf{ka}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ka}\Sf{too}\df{\Ff{s}}	&\Qf{ka}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ka}\Sf{tu}\If{w}\Ef{a}	&\Qf{ka}\Sf{too}\\
\Qf{x̱ʼe}- ‘mouth’	&—		&\Sf{tu}-	&\Qf{x̱ʼe}-\Sf{tu}-	&\Qf{x̱ʼa}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Sf{tu}\Df{d}\If{i}	&\Qf{x̱ʼa}\Sf{tu}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Sf{tu}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Sf{too}\df{\Ff{s}}	&\Qf{x̱ʼa}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Sf{tu}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Sf{too}\\
\Qf{ji}- ‘hand’		&—		&\Sf{tu}-	&\Qf{ji}-\Sf{tu}-	&\Qf{ji}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\Sf{tu}\Df{d}\If{i}	&\Qf{ji}\Sf{tu}\Ff{s}\If{i}	&\Qf{ji}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ji}\Sf{too}\df{\Ff{s}}	&\Qf{ji}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ji}\Sf{tu}\If{w}\Ef{a}	&\Qf{ji}\Sf{too}\\
\Qf{tu}- ‘inside’	&—		&\Sf{tu}-	&\Qf{tu}-\Sf{tu}-	&\Qf{tu}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\Sf{tu}\Df{d}\If{i}	&\Qf{tu}\Sf{tu}\Ff{s}\If{i}	&\Qf{tu}\Sf{tu}\Df{d}\Ef{a}	&\Qf{tu}\Sf{too}\df{\Ff{s}}	&\Qf{tu}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{tu}\Sf{tu}\If{w}\Ef{a}	&\Qf{tu}\Sf{too}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), first person plural subject \textit{tu-}}
\end{table}

%% Zero, 1PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{t}-			&\Df{t}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&—		&\Sf{tʰu}-	&\Sf{tʰu}-		&\Sf{tʰu}.\Df{t}\Ff{s}\If{i}		&\Sf{tʰu}.\Df{t}\If{i}		&\Sf{tʰu}.\Ff{s}\If{i}		&\Sf{tʰu}.\Df{t}\Ef{a}		&\Sf{tʰuː}\df{\Ff{s}}		&\Sf{tʰu}.\Ff{s}\Ef{a}		&\Sf{tʰu}.\If{w}\Ef{a}		&\Sf{tʰuː}\\
\Qf{ʔa}- expletive	&—		&\Sf{tʰu}-	&\Qf{ʔa}-\Sf{tʰu}-	&\Qf{ʔa}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{ʔa}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{ʔa}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{ʔa}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{ʔa}.\Sf{tʰuː}\\
\Qf{kʰa}- qualifier	&—		&\Sf{tʰu}-	&\Qf{kʰa}-\Sf{tʰu}-	&\Qf{kʰa}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{kʰa}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{kʰa}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{kʰa}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{kʰa}.\Sf{tʰuː}\\
\Qf{χʼe}- ‘mouth’	&—		&\Sf{tʰu}-	&\Qf{χʼe}-\Sf{tʰu}-	&\Qf{χʼa}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{χʼa}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{χʼa}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{χʼa}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{χʼa}.\Sf{tʰuː}\\
\Qf{tʃi}- ‘hand’	&—		&\Sf{tʰu}-	&\Qf{tʃi}-\Sf{tʰu}-	&\Qf{tʃi}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{tʃi}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{tʃi}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʃi}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʃi}.\Sf{tʰuː}\\
\Qf{tʰu}- ‘inside’	&—		&\Sf{tʰu}-	&\Qf{tʰu}-\Sf{tʰu}-	&\Qf{tʰu}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{tʰu}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{tʰu}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʰu}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʰu}.\Sf{tʰuː}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), first person plural subject /{tʰu-}/, IPA}
\end{table}

\clearpage
%% Zero, 2SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&—		&\Sf{i}-	&\Sf{i}-		&\Sf{i}\Df{d}\Ff{z}\If{i}		&\Sf{i}\Df{d}\If{i}		&\Sf{i}\Ff{s}\If{i}		&\Sf{i}\Df{d}\Ef{a}		&\Sf{ee}\df{\Ff{s}}		&\Sf{i}\Ff{s}\Ef{a}		&\Sf{i}\If{y}\Ef{a}		&\Sf{ee}\\
\Qf{a}- expletive	&—		&\Sf{i}-	&\Qf{a}-\Sf{i}-		&\Qf{e}\Sf{e}\Df{d}\Ff{z}\If{i}		&\Qf{e}\Sf{e}\Df{d}\If{i}	&\Qf{e}\Sf{e}\Ff{s}\If{i}	&\Qf{e}\Sf{e}\Df{d}\Ef{a}	&\Qf{e}\Sf{e}\df{\Ff{s}}	&\Qf{e}\Sf{e}\Ff{s}\Ef{a}	&\Qf{e}\Sf{e}\If{y}\Ef{a}	&\Qf{e}\Sf{e}\\
\Qf{ka}- qualifier	&—		&\Sf{i}-	&\Qf{ka}-\Sf{i}-	&\Qf{k}\Sf{ee}\Df{d}\Ff{z}\If{i}	&\Qf{k}\Sf{ee}\Df{d}\If{i}	&\Qf{k}\Sf{ee}\Ff{s}\If{i}	&\Qf{k}\Sf{ee}\Df{d}\Ef{a}	&\Qf{k}\Sf{ee}\df{\Ff{s}}	&\Qf{k}\Sf{ee}\Ff{s}\Ef{a}	&\Qf{k}\Sf{ee}\If{y}\Ef{a}	&\Qf{k}\Sf{ee}\\
\Qf{x̱ʼe}- ‘mouth’	&—		&\Sf{i}-	&\Qf{x̱ʼe}-\Sf{i}-	&\Qf{x̱ʼ}\Sf{ee}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼ}\Sf{ee}\Df{d}\If{i}	&\Qf{x̱ʼ}\Sf{ee}\Ff{s}\If{i}	&\Qf{x̱ʼ}\Sf{ee}\Df{d}\Ef{a}	&\Qf{x̱ʼ}\Sf{ee}\df{\Ff{s}}	&\Qf{x̱ʼ}\Sf{ee}\Ff{s}\Ef{a}	&\Qf{x̱ʼ}\Sf{ee}\If{y}\Ef{a}	&\Qf{x̱ʼ}\Sf{ee}\\
\Qf{ji}- ‘hand’		&—		&\Sf{i}-	&\Qf{ji}-\Sf{i}-	&\Qf{j}\Sf{ee}\Df{d}\Ff{z}\If{i}	&\Qf{j}\Sf{ee}\Df{d}\If{i}	&\Qf{j}\Sf{ee}\Ff{s}\If{i}	&\Qf{j}\Sf{ee}\Df{d}\Ef{a}	&\Qf{j}\Sf{ee}\df{\Ff{s}}	&\Qf{j}\Sf{ee}\Ff{s}\Ef{a}	&\Qf{j}\Sf{ee}\If{y}\Ef{a}	&\Qf{j}\Sf{ee}\\
\Qf{tu}- ‘inside’	&—		&\Sf{i}-	&\Qf{tu}-\Sf{i}-	&\Qf{t}\Sf{ee}\Df{d}\Ff{z}\If{i}	&\Qf{t}\Sf{ee}\Df{d}\If{i}	&\Qf{t}\Sf{ee}\Ff{s}\If{i}	&\Qf{t}\Sf{ee}\Df{d}\Ef{a}	&\Qf{t}\Sf{ee}\df{\Ff{s}}	&\Qf{t}\Sf{ee}\Ff{s}\Ef{a}	&\Qf{t}\Sf{ee}\If{y}\Ef{a}	&\Qf{t}\Sf{ee}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), second person singular subject \textit{i-}}
\end{table}

%% Zero, 2SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&—		&\Sf{i}-	&\Sf{i}-		&\Sf{ʔi}.\Df{t}\Ff{s}\If{i}		&\Sf{ʔi}.\Df{t}\If{i}			&\Sf{ʔi}.\Ff{s}\If{i}			&\Sf{ʔi}.\Df{t}\Ef{a}			&\Sf{ʔiː}\df{\Ff{s}}			&\Sf{ʔi}.\Ff{s}\Ef{a}			&\Sf{ʔi}.\If{j}\Ef{a}			&\Sf{ʔiː}\\
\Qf{ʔa}- expletive	&—		&\Sf{i}-	&\Qf{ʔa}-\Sf{i}-	&\Qf{ʔ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{ʔ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{ʔ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{ʔ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{ʔ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{ʔ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{ʔ}\Sf{i}\Qf{ː}\\
\Qf{kʰa}- qualifier	&—		&\Sf{i}-	&\Qf{kʰa}-\Sf{i}-	&\Qf{kʰ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{kʰ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{kʰ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{kʰ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{kʰ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{kʰ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{kʰ}\Sf{i}\Qf{ː}\\
\Qf{χʼe}- ‘mouth’	&—		&\Sf{i}-	&\Qf{χʼe}-\Sf{i}-	&\Qf{χʼ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{χʼ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{χʼ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{χʼ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{χʼ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{χʼ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{χʼ}\Sf{i}\Qf{ː}\\
\Qf{tʃi}- ‘hand’	&—		&\Sf{i}-	&\Qf{tʃi}-\Sf{i}-	&\Qf{tʃ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{tʃ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{tʃ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{tʃ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{tʃ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{tʃ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{tʃ}\Sf{i}\Qf{ː}\\
\Qf{tʰu}- ‘inside’	&—		&\Sf{i}-	&\Qf{tʰu}-\Sf{i}-	&\Qf{tʰ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{tʰ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{tʰ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{tʰ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{tʰ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{tʰ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{tʰ}\Sf{i}\Qf{ː}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), second person singular subject /{i-}/, IPA}
\end{table}

\clearpage
%% Zero, 2PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&—		&\Sf{yi}-	&\Sf{yi}-		&\Sf{yeey}\Df{d}\Ff{z}\If{i}		&\Sf{yeey}\Df{d}\If{i}		&\Sf{yeey}\Ff{s}\If{i}		&\Sf{yi}\Df{d}\Ef{a}		&\Sf{yi}\df{\Ff{s}}		&\Sf{yi}\Ff{s}\Ef{a}		&\Sf{yee}\If{y}			&\Sf{yi}\\
\Qf{a}- expletive	&—		&\Sf{yi}-	&\Qf{a}-\Sf{yi}-	&\Qf{a}\Sf{y}\Df{d}\Ff{z}\If{i}		&\Qf{a}\Sf{y}\Df{d}\If{i}	&\Qf{a}\Sf{y}\Ff{s}\If{i}	&\Qf{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{a}\Sf{yi}\df{\Ff{s}}	&\Qf{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{a}\Sf{yee}\If{y}		&\Qf{a}\Sf{y}\\
\Qf{ka}- qualifier	&—		&\Sf{yi}-	&\Qf{ka}-\Sf{yi}-	&\Qf{ka}\Sf{y}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\Sf{y}\Df{d}\If{i}	&\Qf{ka}\Sf{y}\Ff{s}\If{i}	&\Qf{ka}\Sf{y}\Df{d}\Ef{a}	&\Qf{ka}\Sf{yi}\df{\Ff{s}}	&\Qf{ka}\Sf{y}\Ff{s}\Ef{a}	&\Qf{ka}\Sf{yee}\If{y}		&\Qf{ka}\Sf{y}\\
\Qf{x̱ʼe}- ‘mouth’	&—		&\Sf{yi}-	&\Qf{x̱ʼe}-\Sf{yi}-	&\Qf{x̱ʼa}\Sf{y}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Sf{y}\Df{d}\If{i}	&\Qf{x̱ʼa}\Sf{y}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Sf{y}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Sf{yi}\df{\Ff{s}}	&\Qf{x̱ʼa}\Sf{y}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Sf{yee}\If{y}		&\Qf{x̱ʼa}\Sf{y}\\
\Qf{ji}- ‘hand’		&—		&\Sf{yi}-	&\Qf{ji}-\Sf{yi}-	&\Qf{ji}\Sf{y}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\Sf{y}\Df{d}\If{i}	&\Qf{ji}\Sf{y}\Ff{s}\If{i}	&\Qf{ji}\Sf{y}\Df{d}\Ef{a}	&\Qf{ji}\Sf{yi}\df{\Ff{s}}	&\Qf{ji}\Sf{y}\Ff{s}\Ef{a}	&\Qf{ji}\Sf{yee}\If{y}		&\Qf{ji}\Sf{y}\\
\Qf{tu}- ‘inside’	&—		&\Sf{yi}-	&\Qf{tu}-\Sf{yi}-	&\Qf{tu}\Sf{y}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\Sf{y}\Df{d}\If{i}	&\Qf{tu}\Sf{y}\Ff{s}\If{i}	&\Qf{tu}\Sf{y}\Df{d}\Ef{a}	&\Qf{tu}\Sf{yi}\df{\Ff{s}}	&\Qf{tu}\Sf{y}\Ff{s}\Ef{a}	&\Qf{tu}\Sf{yee}\If{y}		&\Qf{tu}\Sf{y}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), second person plural subject \textit{yi-}}
\end{table}

%% Zero, 2PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{t}-			&\Df{t}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&—		&\Sf{ji}-	&\Sf{ji}-		&\Sf{jiːj}.\Df{t}\Ff{s}\If{i}		&\Sf{jiːj}.\Df{t}\If{i}		&\Sf{jiːj}.\Ff{s}\If{i}		&\Sf{ji}.\Df{t}\Ef{a}		&\Sf{ji}\df{\Ff{s}}		&\Sf{ji}.\Ff{s}\Ef{a}		&\Sf{jiː}\If{j}			&\Sf{ji}\\
\Qf{ʔa}- expletive	&—		&\Sf{ji}-	&\Qf{ʔa}-\Sf{ji}-	&\Qf{ʔa}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔa}\Sf{j}.\Df{t}\If{i}	&\Qf{ʔa}\Sf{j}.\Ff{s}\If{i}	&\Qf{ʔa}\Sf{j}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Sf{ji}\df{\Ff{s}}	&\Qf{ʔa}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Sf{jiː}\If{j}		&\Qf{ʔa}\Sf{j}\\
\Qf{kʰa}- qualifier	&—		&\Sf{ji}-	&\Qf{kʰa}-\Sf{ji}-	&\Qf{kʰa}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}\Sf{j}.\Df{t}\If{i}	&\Qf{kʰa}\Sf{j}.\Ff{s}\If{i}	&\Qf{kʰa}\Sf{j}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Sf{ji}\df{\Ff{s}}	&\Qf{kʰa}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Sf{jiː}\If{j}	&\Qf{kʰa}\Sf{j}\\
\Qf{χʼe}- ‘mouth’	&—		&\Sf{ji}-	&\Qf{χʼe}-\Sf{ji}-	&\Qf{χʼa}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}\Sf{j}.\Df{t}\If{i}	&\Qf{χʼa}\Sf{j}.\Ff{s}\If{i}	&\Qf{χʼa}\Sf{j}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Sf{ji}\df{\Ff{s}}	&\Qf{χʼa}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Sf{jiː}\If{j}	&\Qf{χʼa}\Sf{j}\\
\Qf{tʃi}- ‘hand’	&—		&\Sf{ji}-	&\Qf{tʃi}-\Sf{ji}-	&\Qf{tʃi}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}\Sf{j}.\Df{t}\If{i}	&\Qf{tʃi}\Sf{j}.\Ff{s}\If{i}	&\Qf{tʃi}\Sf{j}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʃi}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Sf{jiː}\If{j}	&\Qf{tʃi}\Sf{j}\\
\Qf{tʰu}- ‘inside’	&—		&\Sf{ji}-	&\Qf{tʰu}-\Sf{ji}-	&\Qf{tʰu}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}\Sf{j}.\Df{t}\If{i}	&\Qf{tʰu}\Sf{j}.\Ff{s}\If{i}	&\Qf{tʰu}\Sf{j}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʰu}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Sf{jiː}\If{j}	&\Qf{tʰu}\Sf{j}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), second person plural subject /{ji-}/, IPA}
\end{table}

\clearpage
%% Zero, 4H
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}\rlap{-}	&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}\rlap{-}	&\If{i}-			&—\\
\midrule
—			&—		&\Sf{du}-	&\Sf{du}-		&\Sf{du}\Df{d}\Ff{z}\If{i}		&⁎			&⁎			&⁎		&\Sf{du}\df{\Ff{s}}		&⁎		&\Sf{du}\If{w}\Ef{a}		&\Sf{du}\\
\Qf{a}- expletive	&—		&\Sf{du}-	&\Qf{a}-\Sf{du}-	&\Qf{a}\Sf{du}\Df{d}\Ff{z}\If{i}	&⁎			&⁎			&⁎		&\Qf{a}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{a}\Sf{du}\If{w}\Ef{a}	&\Qf{a}\Sf{du}\\
\Qf{ka}- qualifier	&—		&\Sf{du}-	&\Qf{ka}-\Sf{du}-	&\Qf{ka}\Sf{du}\Df{d}\Ff{z}\If{i}	&⁎			&⁎			&⁎		&\Qf{ka}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ka}\Sf{du}\If{w}\Ef{a}	&\Qf{ka}\Sf{du}\\
\Qf{x̱ʼe}- ‘mouth’	&—		&\Sf{du}-	&\Qf{x̱ʼe}-\Sf{du}-	&\Qf{x̱ʼa}\Sf{du}\Df{d}\Ff{z}\If{i}	&⁎			&⁎			&⁎		&\Qf{x̱ʼa}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{x̱ʼa}\Sf{du}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Sf{du}\\
\Qf{ji}- ‘hand’		&—		&\Sf{du}-	&\Qf{ji}-\Sf{du}-	&\Qf{ji}\Sf{du}\Df{d}\Ff{z}\If{i}	&⁎			&⁎			&⁎		&\Qf{ji}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ji}\Sf{du}\If{w}\Ef{a}	&\Qf{ji}\Sf{du}\\
\Qf{tu}- ‘inside’	&—		&\Sf{du}-	&\Qf{tu}-\Sf{du}-	&\Qf{tu}\Sf{du}\Df{d}\Ff{z}\If{i}	&⁎			&⁎			&⁎		&\Qf{tu}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{tu}\Sf{du}\If{w}\Ef{a}	&\Qf{tu}\Sf{du}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), fourth person (indefinite) human subject \textit{du-}}
\end{table}

%% Zero, 4H, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}\rlap{-}	&\Df{t}-\Ff{s}\rlap{-}		&\Ff{s}\rlap{-}	&\If{i}-			&—\\
\midrule
—			&—		&\Sf{tu}-	&\Sf{tu}-		&\Sf{tu}.\Df{t}\Ff{s}\If{i}		&⁎			&⁎			&⁎		&\Sf{tu}\df{\Ff{s}}		&⁎		&\Sf{tu}.\If{w}\Ef{a}		&\Sf{tu}\\
\Qf{ʔa}- expletive	&—		&\Sf{tu}-	&\Qf{ʔa}-\Sf{tu}-	&\Qf{ʔa}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{ʔa}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{ʔa}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{ʔa}\Sf{tu}\\
\Qf{kʰa}- qualifier	&—		&\Sf{tu}-	&\Qf{kʰa}-\Sf{tu}-	&\Qf{kʰa}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{kʰa}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{kʰa}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{kʰa}\Sf{tu}\\
\Qf{χʼe}- ‘mouth’	&—		&\Sf{tu}-	&\Qf{χʼe}-\Sf{tu}-	&\Qf{χʼa}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{χʼa}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{χʼa}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{χʼa}\Sf{tu}\\
\Qf{tʃi}- ‘hand’	&—		&\Sf{tu}-	&\Qf{tʃi}-\Sf{tu}-	&\Qf{tʃi}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{tʃi}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{tʃi}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{tʃi}\Sf{tu}\\
\Qf{tʰu}- ‘inside’	&—		&\Sf{tu}-	&\Qf{tʰu}-\Sf{tu}-	&\Qf{tʰu}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{tʰu}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{tʰu}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{tʰu}\Sf{tu}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect (imperfective or \textit{∅}-conjugation), fourth person (indefinite) human subject /{tu-}/, IPA}
\end{table}

%%%
%%% Unmarked aspect with irrealis
%%%
\clearpage
\subsection{Unmarked aspect with irrealis \textit{u-}}\label{sec:zero-irrealis}

\begin{multicols}{2}
\noindent
The irrealis prefix \fm{\Rf{u}-} can occur in unmarked aspect forms.
One situation that requires irrealis \fm{\Rf{u}-} is negation with the negative particle \fm{tléil} ‘not’ or its various allomorphs.
Compare the affirmative imperfective activity in (\ref{ex:zero-irrealis-negation-aff}) below with the negative in (\ref{ex:zero-irrealis-negation-neg}).

\pex\label{ex:zero-irrealis-negation}%
\a\label{ex:zero-irrealis-negation-aff}%
\exrtcmt{affirmative}%
\begingl
	\gla	\rlap{\Qf{A}x̱á.} @ {} @ {} @ {} //
	\glb	\Qf{a}- \rt[²]{x̱a} -μH //
	\glc	\Qf{\xx{arg}}- \rt[²]{eat} -\xx{var} //
	\gld	\rlap{3>3.\xx{impfv}.eat} {} {} {} //
	\glft	‘S/he/it eats it.’, ‘S/he/it is eating it.’
		//
\endgl
\a\label{ex:zero-irrealis-negation-neg}%
\exrtcmt{negative}%
\begingl
	\gla	Tléil \rlap{\Qf{o}\Rf{o}x̱á.} @ {} @ {} @ {} //
	\glb	tléil \Qf{a}- \Rf{u}- \rt[²]{x̱a} -μH //
	\glc	\xx{neg} \Qf{\xx{arg}}- \Rf{\xx{irr}}- \rt[²]{eat} -\xx{var} //
	\gld	not \rlap{3>3.\xx{irr}.\xx{impfv}.eat} {} {} {} //
	\glft	‘S/he/it does not eat it.’, ‘S/he/it is not eating it.’
		//
\endgl
\xe

Another situation that requires irrealis \fm{\Rf{u}-} is when it is specified as part of the lexical entry of a verb.
A typical verb with lexically specified irrealis is \fm{yéi oowajée} (\fm{n}; \fm{-μμH} state impfv.)\ ‘s/he/it thinks so about him/her/it’.
Compare the imperfective aspect form of this verb in (\ref{ex:zero-irrealis-lexical-with}) with its ungrammatical counterpart in (\ref{ex:zero-irrealis-lexical-without}) that lacks irrealis \fm{\Rf{u}-}.

\pex\label{ex:zero-irrealis-lexical}%
\a\label{ex:zero-irrealis-lexical-with}%
\exrtcmt{with irrealis}%
\begingl
	\gla	Yéi @ \rlap{\Qf{o}\Rf{o}\If{w}\Ef{a}jée.} @ {} @ {} @ {} @ {} //
	\glb	yéi= \Qf{a}- \Rf{u}- \If{i}- \rt[²]{jiʰ} -μμH //
	\glc	thus= \Qf{\xx{arg}}- \Rf{\xx{irr}}- \If{\xx{stv}}- \rt[²]{think} -\xx{var} //
	\gld	so \rlap{3>3.\xx{irr}.\xx{impfv}.think} {} {} {} {} //
	\glft	‘S/he/it thinks so about him/her/it’
		//
\endgl
\a\label{ex:zero-irrealis-lexical-without}%
\ljudge{*}%
\exrtcmt{*without irrealis}%
\begingl
	\gla	Yéi @ \rlap{\Qf{a}\If{y}\Ef{a}jée.} @ {} @ {} @ {} @ {} //
	\glb	yéi= \Qf{a}- \phantom{\Rf{u}-} \If{i}- \rt[²]{jiʰ} -μμH //
	\glc	thus= \Qf{\xx{arg}}- \phantom{\Rf{\xx{irr}}-} \If{\xx{stv}}- \rt[²]{think} -\xx{var} //
	\gld	so \rlap{3>3.\xx{impfv}.think} {} {} {} {} //
	\glft	‘S/he/it thinks so about him/her/it’
		//
\endgl
\xe

Irrealis marking with the \fm{\Rf{u}-} prefix is visible only in some unmarked aspect forms and can be undetectable in others.
Irrealis can be reliably detected in forms with an unmarked subject (third person or no subject) and forms with a first person singular subject \fm{\Sf{x̱}-} ‘I’.
Irrealis can sometimes be detected in forms with a fourth person human (indefinite or nonspecific) subject \fm{\Sf{du}-} ‘someone, people, they’ (Leer 1991: 176 \#5a), but this is not always reliable and for some speakers is limited to frozen forms in song lyrics and proverbs.

Irrealis cannot be detected in any unmarked aspect forms with
\begin{inlineenum}
	\item	first person plural subject \fm{\Sf{tu}-} ‘we’
	\item	second person singular subject \fm{\Sf{i}-} ‘you sg.’
	\item	second person plural subject \fm{\Sf{yi}-} ‘you guys’.
\end{inlineenum}
Tables of these forms are given in this subsection for completeness but they are identical to the tables in the previous section.
In such forms where irrealis \fm{\Rf{u}-} is predicted but cannot be detected, we analyze the irrealis prefix as still being logically present but having somehow been hidden.
The reasons for this disappearance of the irrealis prefix are still unclear, but they probably have to do with the phonology of the vowel /\ipa{u}/ and its interactions with nearby /\ipa{i}/ and /\ipa{u}/ vowels in the same form.

Irrealis unmarked aspect forms with the stative classifier prefix \fm{\If{i}-} are underdocumented.
This is because they are only possible with imperfective state verbs where the irrealis \fm{\Rf{u}-} is lexically specified.
In some cases there may simply be no verb with lexically specified irrealis \fm{\Rf{u}-} that takes a subject and includes a qualifier or incorporate prefix.
Such forms are thus grammatically plausible but do not exist, meaning that they are accidental gaps in the language.

There is a remarkable amount of variation in unmarked aspect forms with irrealis \fm{\Rf{u}-} and the first person singular subject \fm{\Sf{x̱}-} ‘I’.
The reasons for this extensive variation are unknown.
Some of this variation is probably specific to particular dialects, but the details of the variation and its geographic distribution have yet to be clearly characterized.
A number of grammatically likely forms are not attested and need to be elicited from speakers of different varieties.
\end{multicols}

\clearpage
%% Zero, Irrealis, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}-		&\If{i}-			&—\\
\midrule
—			&\Rf{u}-	&—		&\Rf{u}-		&\Rf{u}\Df{d}\Ff{z}\If{i}		&\Rf{u}\Df{d}\If{i}		&\Rf{u}\Ff{s}\If{i}		&\Rf{u}\Df{d}\Ef{a}		&\Rf{u}\df{\Ff{s}}		&\Rf{u}\Ff{s}		&\Rf{u}\If{w}\Ef{a}		&\Rf{u}\\
\Qf{a}- arg./expl.	&\Rf{u}-	&—		&\Qf{a}-\Rf{u}-		&\Qf{o}\Rf{o}\Df{d}\Ff{z}\If{i}		&\Qf{o}\Rf{o}\Df{d}\If{i}	&\Qf{o}\Rf{o}\Ff{s}\If{i}	&\Qf{o}\Rf{o}\Df{d}\Ef{a}	&\Qf{o}\Rf{o}\df{\Ff{s}}	&\Qf{o}\Rf{o}\Ff{s}	&\Qf{o}\Rf{o}\If{w}\Ef{a}	&\Qf{o}\Rf{o}\\
\Qf{ka}- qualifier	&\Rf{u}-	&—		&\Qf{ka}-\Rf{u}-	&\Qf{ko}\Rf{o}\Df{d}\Ff{z}\If{i}	&\Qf{ko}\Rf{o}\Df{d}\If{i}	&\Qf{ko}\Rf{o}\Ff{s}\If{i}	&\Qf{ko}\Rf{o}\Df{d}\Ef{a}	&\Qf{ko}\Rf{o}\df{\Ff{s}}	&\Qf{ko}\Rf{o}\Ff{s}	&\Qf{ko}\Rf{o}\If{w}\Ef{a}	&\Qf{ko}\Rf{o}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{u}-	&—		&\Qf{x̱ʼe}-\Rf{u}-	&\Qf{x̱ʼe}\Rf{i}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼe}\Rf{i}\Df{d}\If{i}	&\Qf{x̱ʼe}\Rf{i}\Ff{s}\If{i}	&\Qf{x̱ʼe}\Rf{i}\Df{d}\Ef{a}	&\Qf{x̱ʼe}\Rf{i}\df{\Ff{s}}	&\Qf{x̱ʼe}\Rf{i}\Ff{s}	&\Qf{x̱ʼe}\Rf{i}\If{w}\Ef{a}	&\Qf{x̱ʼe}\Rf{i}\\
\Qf{ji}- ‘hand’		&\Rf{u}-	&—		&\Qf{ji}-\Rf{u}-	&\Qf{je}\Rf{e}\Df{d}\Ff{z}\If{i}	&\Qf{je}\Rf{e}\Df{d}\If{i}	&\Qf{je}\Rf{e}\Ff{s}\If{i}	&\Qf{je}\Rf{e}\Df{d}\Ef{a}	&\Qf{je}\Rf{e}\df{\Ff{s}}	&\Qf{je}\Rf{e}\Ff{s}	&\Qf{je}\Rf{e}\If{y}\Ef{a}	&\Qf{je}\Rf{e}\\
\Qf{tu}- ‘inside’	&\Rf{u}-	&—		&\Qf{tu}-\Rf{u}-	&\Qf{to}\Rf{o}\Df{d}\Ff{z}\If{i}	&\Qf{to}\Rf{o}\Df{d}\If{i}	&\Qf{to}\Rf{o}\Ff{s}\If{i}	&\Qf{to}\Rf{o}\Df{d}\Ef{a}	&\Qf{to}\Rf{o}\df{\Ff{s}}	&\Qf{to}\Rf{o}\Ff{s}	&\Qf{to}\Rf{o}\If{w}\Ef{a}	&\Qf{to}\Rf{o}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis \textit{u-}, unmarked subject (third person or no subject)}
\end{table}

%% Zero, Irrealis, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Rf{u}-	&—		&\Rf{u}-		&\Ef{ʔ}\Rf{u}.\Df{t}\Ff{s}\If{i}		&\Ef{ʔ}\Rf{u}.\Df{t}\If{i}		&\Ef{ʔ}\Rf{u}.\Ff{s}\If{i}		&\Ef{ʔ}\Rf{u}.\Df{t}\Ef{a}		&\Ef{ʔ}\Rf{u}\df{\Ff{s}}		&\Ef{ʔ}\Rf{u}\Ff{s}			&\Ef{ʔ}\Rf{u}.\If{w}\Ef{a}		&\Ef{ʔ}\Rf{u}\\
\Qf{ʔa}- arg./expl.	&\Rf{u}-	&—		&\Qf{ʔa}-\Rf{u}-	&\Qf{ʔu}\Rf{ː}.\Df{t}\Ff{s}\If{i}		&\Qf{ʔu}\Rf{ː}.\Df{t}\If{i}		&\Qf{ʔu}\Rf{ː}.\Ff{s}\If{i}		&\Qf{ʔu}\Rf{ː}.\Df{t}\Ef{a}		&\Qf{ʔu}\Rf{ː}\df{\Ff{s}}		&\Qf{ʔu}\Rf{ː}\Ff{s}			&\Qf{ʔu}\Rf{ː}.\If{w}\Ef{a}		&\Qf{ʔu}\Rf{ː}\\
\Qf{kʰa}- qualifier	&\Rf{u}-	&—		&\Qf{kʰa}-\Rf{u}-	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Df{t}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Ff{s}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Df{t}\Ef{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\df{\Ff{s}}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Ff{s}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\If{w}\Ef{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\\
\Qf{χʼe}- ‘mouth’	&\Rf{u}-	&—		&\Qf{χʼe}-\Rf{u}-	&\Qf{χʼe}\Rf{ː}.\Df{t}\Ff{s}\If{i}		&\Qf{χʼe}\Rf{ː}.\Df{t}\If{i}		&\Qf{χʼe}\Rf{ː}.\Ff{s}\If{i}		&\Qf{χʼe}\Rf{ː}.\Df{t}\Ef{a}		&\Qf{χʼe}\Rf{ː}\df{\Ff{s}}		&\Qf{χʼe}\Rf{ː}\Ff{s}			&\Qf{χʼe}\Rf{ː}.\If{w}\Ef{a}		&\Qf{χʼe}\Rf{ː}\\
\Qf{tʃi}- ‘hand’	&\Rf{u}-	&—		&\Qf{tʃi}-\Rf{u}-	&\Qf{tʃi}\Rf{ː}.\Df{t}\Ff{s}\If{i}		&\Qf{tʃi}\Rf{ː}.\Df{t}\If{i}		&\Qf{tʃi}\Rf{ː}.\Ff{s}\If{i}		&\Qf{tʃi}\Rf{ː}.\Df{t}\Ef{a}		&\Qf{tʃi}\Rf{ː}\df{\Ff{s}}		&\Qf{tʃi}\Rf{ː}\Ff{s}			&\Qf{tʃi}\Rf{ː}.\If{j}\Ef{a}		&\Qf{tʃi}\Rf{ː}\\
\Qf{tʰu}- ‘inside’	&\Rf{u}-	&—		&\Qf{tʰu}-\Rf{u}-	&\Qf{tʰu}\Rf{ː}.\Df{t}\Ff{s}\If{i}		&\Qf{tʰu}\Rf{ː}.\Df{t}\If{i}		&\Qf{tʰu}\Rf{ː}.\Ff{s}\If{i}		&\Qf{tʰu}\Rf{ː}.\Df{t}\Ef{a}		&\Qf{tʰu}\Rf{ː}\df{\Ff{s}}		&\Qf{tʰu}\Rf{ː}\Ff{s}			&\Qf{tʰu}\Rf{ː}.\If{w}\Ef{a}		&\Qf{tʰu}\Rf{ː}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis /{u-}/, unmarked subject (third person or no subject), IPA}
\end{table}

%% Zero, Irrealis, 1SG
\begin{table}
\centerfloat
% Decrease \arraystretch because both tables are too tall.
\renewcommand{\arraystretch}{0.95}
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}				&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Rf{u}-	&\Sf{x̱}-	&\Rf{u}-\Sf{x̱}-			&\Sf{x̱}\Rf{w}\Ef{a}\Df{d}\Ff{z}\If{i}		&\Sf{x̱}\Rf{w}\Ef{a}\Df{d}\If{i}		&\Sf{x̱}\Rf{w}\Ef{a}\Ff{s}\If{i}		&\Sf{x̱}\Rf{w}\Ef{a}\Df{d}\Ef{a}		&\Sf{x̱}\Rf{w}\Ef{a}\df{\Ff{s}}			&\Sf{x̱}\Rf{w}\Ef{a}\Ff{s}\Ef{a}		&\Sf{x̱}\Rf{w}\Ef{a}\If{a}		&\Sf{x̱}\Rf{w}\Ef{a}\\
			&		&		&				&\Rf{u}\Sf{x̱}\Df{d}\Ff{z}\If{i}			&\Rf{u}\Sf{x̱}\Df{d}\If{i}		&\Rf{u}\Sf{x̱}\Ff{s}\If{i}		&\Rf{u}\Sf{x̱}\Df{d}\Ef{a}		&						&\Rf{u}\Sf{x̱}\Ff{s}\Ef{a}		&\Rf{u}\Sf{x̱}\Ef{a}\If{a}		&\Rf{u}\Sf{x̱}\Ef{a}\\
\Qf{a}- expletive	&\Rf{u}-	&\Sf{x̱}-	&\Qf{a}-\Rf{u}-\Sf{x̱}-		&\Qf{a}\Sf{x̱}\Rf{w}\Df{d}\Ff{z}\If{i}\?		&\Qf{a}\Sf{x̱}\Rf{w}\Df{d}\If{i}\?	&\Qf{a}\Sf{x̱}\Rf{w}\Ff{s}\If{i}\?	&\Qf{a}\Sf{x̱}\Rf{w}\Df{d}\Ef{a}\?	&\Qf{a}\Sf{x̱}\Rf{w}\Ef{a}\df{\Ff{s}}\?		&\Qf{a}\Sf{x̱}\Rf{w}\Ff{s}\Ef{a}\?	&\Qf{a}\Sf{x̱}\Rf{w}\Ef{a}\If{a}\?	&\Qf{a}\Sf{x̱}\Rf{w}\Ef{a}\?\\
			&		&		&				&\Qf{o}\Rf{o}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?		&\Qf{o}\Rf{o}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{o}\Rf{o}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{o}\Rf{o}\Sf{x̱}\Df{d}\Ef{a}\?	&\Qf{o}\Rf{o}\Sf{x̱}\Ef{a}\df{\Ff{s}}\?		&\Qf{o}\Rf{o}\Sf{x̱}\Ff{s}\Ef{a}\?	&\Qf{o}\Rf{o}\Sf{x̱}\Ef{a}\If{a}\?	&\Qf{o}\Rf{o}\Sf{x̱}\Ef{a}\\
\Qf{ka}- qualifier	&\Rf{u}-	&\Sf{x̱}-	&\Qf{ka}-\Rf{u}-\Sf{x̱}-		&\Qf{ko}\Rf{o}\Sf{x̱}\Df{d}\Ff{z}\If{i}		&\Qf{ko}\Rf{o}\Sf{x̱}\Df{d}\If{i}	&\Qf{ko}\Rf{o}\Sf{x̱}\Ff{s}\If{i}	&\Qf{ko}\Rf{o}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{ko}\Rf{o}\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Qf{ko}\Rf{o}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{ko}\Rf{o}\Sf{x̱}\Ef{a}\If{a}	&\Qf{ko}\Rf{o}\Sf{x̱}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{u}-	&\Sf{x̱}-	&\Qf{x̱ʼe}-\Rf{u}-\Sf{x̱}-	&\Qf{x̱ʼe}\Rf{i}\Sf{x̱}\Df{d}\Ff{z}\If{i}		&\Qf{x̱ʼe}\Rf{i}\Sf{x̱}\Df{d}\If{i}	&\Qf{x̱ʼe}\Rf{i}\Sf{x̱}\Ff{s}\If{i}	&\Qf{x̱ʼe}\Rf{i}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{x̱ʼe}\Rf{i}\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Qf{x̱ʼe}\Rf{i}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{x̱ʼe}\Rf{i}\Sf{x̱}\Ef{a}\If{a}	&\Qf{x̱ʼe}\Rf{i}\Sf{x̱}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Rf{u}-	&\Sf{x̱}-	&\Qf{ji}-\Rf{u}-\Sf{x̱}-		&\Qf{je}\Rf{e}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{je}\Rf{e}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{je}\Rf{e}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{je}\Rf{e}\Sf{x̱}\Df{d}\Ef{a}\?	&\Qf{je}\Rf{e}\Sf{x̱}\Ef{a}\df{\Ff{s}}\?		&\Qf{je}\Rf{e}\Sf{x̱}\Ff{s}\Ef{a}\?	&\Qf{je}\Rf{e}\Sf{x̱}\Ef{a}\If{a}\?	&\Qf{je}\Rf{e}\Sf{x̱}\Ef{a}\?\\
			&		&		&				&\Qf{ji}\Sf{x̱}\Rf{w}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Sf{x̱}\Rf{w}\Df{d}\If{i}\?	&\Qf{ji}\Sf{x̱}\Rf{w}\Ff{s}\If{i}\?	&\Qf{ji}\Sf{x̱}\Rf{w}\Df{d}\Ef{a}\?	&\Qf{ji}\Sf{x̱}\Rf{w}\Ef{a}\df{\Ff{s}}\?		&\Qf{ji}\Sf{x̱}\Rf{w}\Ff{s}\Ef{a}\?	&\Qf{ji}\Sf{x̱}\Rf{w}\Ef{a}\If{a}\?	&\Qf{ji}\Sf{x̱}\Rf{w}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Rf{u}-	&\Sf{x̱}-	&\Qf{tu}-\Rf{u}-\Sf{x̱}-		&\Qf{to}\Rf{o}\Sf{x̱}\Df{d}\Ff{z}\If{i}		&\Qf{to}\Rf{o}\Sf{x̱}\Df{d}\If{i}	&\Qf{to}\Rf{o}\Sf{x̱}\Ff{s}\If{i}	&\Qf{to}\Rf{o}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{to}\Rf{o}\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Qf{to}\Rf{o}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{to}\Rf{o}\Sf{x̱}\Ef{a}\If{a}	&\Qf{to}\Rf{o}\Sf{x̱}\Ef{a}\\
			&		&		&				&						&					&					&					&\Qf{tu}\Sf{x̱}\Rf{w}\Ef{a}\df{\Ff{s}}\?		&					&\Qf{tu}\Sf{x̱}\Rf{w}\Ef{a}\If{a}\?	&\Qf{tu}\Sf{x̱}\Rf{w}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis \textit{u-}, first person singular subject \textit{x̱-}}
% Omit table breaks to keep both tables together on one page.
%\end{table}

%% Zero, Irrealis, 1SG, IPA
%\begin{table}
\centerfloat
\setlength{\tabcolsep}{0.875ex}
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}					&\Df{t}-\If{i}\rlap{-}					&\Ff{s}-\If{i}\rlap{-}					&\Df{t}-						&\Df{t}-\Ff{s}\rlap{-}					&\Ff{s}-						&\If{i}-					&—\\
\midrule
—			&\Rf{u}-	&\Sf{χ}-	&\Rf{u}-\Sf{χ}-			&\Sf{χ}\Rf{ʷ}\Ef{a}.\Df{t}\Ff{s}\If{i}				&\Sf{χ}\Rf{ʷ}\Ef{a}.\Df{t}\If{i}			&\Sf{χ}\Rf{ʷ}\Ef{a}.\Ff{s}\If{i}			&\Sf{χ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}			&\Sf{χ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}				&\Sf{χ}\Rf{ʷ}\Ef{a}.\Ff{s}\Ef{a}			&\Sf{χ}\Rf{ʷ}\Ef{a}\If{ː}			&\Sf{χ}\Rf{ʷ}\Ef{a}\\
			&		&		&				&\Ef{ʔ}\Rf{u}\Sf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}			&\Ef{ʔ}\Rf{u}\Sf{χ}\Rf{ʷ}.\Df{t}\If{i}			&\Ef{ʔ}\Rf{u}\Sf{χ}\Rf{ʷ}.\Ff{s}\If{i}			&\Ef{ʔ}\Rf{u}\Sf{χ}\Rf{ʷ}.\Df{t}\Ef{a}			&							&\Ef{ʔ}\Rf{u}\Sf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}			&\Ef{ʔ}\Rf{u}.\Sf{χ}\Ef{a}\If{ː}		&\Ef{ʔ}\Rf{u}.\Sf{χ}\Ef{a}\\
\Qf{ʔa}- expletive	&\Rf{u}-	&\Sf{χ}-	&\Qf{ʔa}-\Rf{u}-\Sf{χ}-		&\Qf{ʔa}\Sf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}\?			&\Qf{ʔa}\Sf{χ}\Rf{ʷ}.\Df{t}\If{i}\?			&\Qf{ʔa}\Sf{χ}\Rf{ʷ}.\Ff{s}\If{i}\?			&\Qf{ʔa}\Sf{χ}\Rf{ʷ}.\Df{t}\Ef{a}\?			&\Qf{ʔa}.\Sf{χ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}\?		&\Qf{ʔa}\Sf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}\?			&\Qf{ʔa}.\Sf{χ}\Rf{ʷ}\Ef{a}\If{ː}\?		&\Qf{ʔa}.\Sf{χ}\Rf{ʷ}\Ef{a}\?\\
			&		&		&				&\Qf{ʔu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}\?			&\Qf{ʔu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\If{i}\?		&\Qf{ʔu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Ff{s}\If{i}\?		&\Qf{ʔu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\Ef{a}\?		&\Qf{ʔu}\Rf{ː}.\Sf{χ}\Ef{a}\df{\Ff{s}}\?		&\Qf{ʔu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}\?		&\Qf{ʔu}\Rf{ː}.\Sf{χ}\Ef{a}\If{ː}\?		&\Qf{ʔu}\Rf{ː}.\Sf{χ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Rf{u}-	&\Sf{χ}-	&\Qf{kʰa}-\Rf{u}-\Sf{χ}-	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Ff{s}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\Ef{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Sf{χ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Rf{u}-	&\Sf{χ}-	&\Qf{χʼe}-\Rf{u}-\Sf{χ}-	&\Qf{χʼe}\Rf{ː}\Sf{χ}.\Df{t}\Ff{s}\If{i}			&\Qf{χʼe}\Rf{ː}\Sf{χ}.\Df{t}\If{i}			&\Qf{χʼe}\Rf{ː}\Sf{χ}.\Ff{s}\If{i}			&\Qf{χʼe}\Rf{ː}\Sf{χ}.\Df{t}\Ef{a}			&\Qf{χʼe}\Rf{ː}.\Sf{χ}\Ef{a}\df{\Ff{s}}			&\Qf{χʼe}\Rf{ː}\Sf{χ}.\Ff{s}\Ef{a}			&\Qf{χʼe}\Rf{ː}.\Sf{χ}\Ef{a}\If{ː}		&\Qf{χʼe}\Rf{ː}.\Sf{χ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Rf{u}-	&\Sf{χ}-	&\Qf{tʃi}-\Rf{u}-\Sf{χ}-	&\Qf{tʃi}\Rf{ː}\Sf{χ}.\Df{t}\Ff{s}\If{i}\?			&\Qf{tʃi}\Rf{ː}\Sf{χ}.\Df{t}\If{i}\?			&\Qf{tʃi}\Rf{ː}\Sf{χ}.\Ff{s}\If{i}\?			&\Qf{tʃi}\Rf{ː}\Sf{χ}.\Df{t}\Ef{a}\?			&\Qf{tʃi}\Rf{ː}.\Sf{χ}\Ef{a}\df{\Ff{s}}\?		&\Qf{tʃi}\Rf{ː}\Sf{χ}.\Ff{s}\Ef{a}\?			&\Qf{tʃi}\Rf{ː}.\Sf{χ}\Ef{a}\If{ː}\?		&\Qf{tʃi}\Rf{ː}.\Sf{χ}\Ef{a}\?\\
			&		&		&				&\Qf{tʃi}\Sf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}\?			&\Qf{tʃi}\Sf{χ}\Rf{ʷ}.\Df{t}\If{i}\?			&\Qf{tʃi}\Sf{χ}\Rf{ʷ}.\Ff{s}\If{i}\?			&\Qf{tʃi}\Sf{χ}\Rf{ʷ}.\Df{t}\Ef{a}\?			&\Qf{tʃi}.\Sf{χ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}\?		&\Qf{tʃi}\Sf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}\?			&\Qf{tʃi}.\Sf{χ}\Rf{ʷ}\Ef{a}\If{ː}\?		&\Qf{tʃi}.\Sf{χ}\Rf{ʷ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Rf{u}-	&\Sf{χ}-	&\Qf{tʰu}-\Rf{u}-\Sf{χ}-	&\Qf{tʰu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}			&\Qf{tʰu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\If{i}		&\Qf{tʰu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Ff{s}\If{i}		&\Qf{tʰu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Df{t}\Ef{a}		&\Qf{tʰu}\Rf{ː}.\Sf{χ}\Ef{a}\df{\Ff{s}}			&\Qf{tʰu}\Rf{ː}\Sf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}		&\Qf{tʰu}\Rf{ː}.\Sf{χ}\Ef{a}\If{ː}		&\Qf{tʰu}\Rf{ː}.\Sf{χ}\Ef{a}\\
			&		&		&				&								&							&							&							&\Qf{tu}.\Sf{χ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}\?		&							&\Qf{tu}.\Sf{χ}\Rf{ʷ}\Ef{a}\If{ː}\?		&\Qf{tu}.\Sf{χ}\Rf{ʷ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis /{u-}/, first person singular subject /{χ-}/, IPA}
\end{table}

\clearpage
%% Zero, Irrealis, 1PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Rf{u}-	&\Sf{tu}-	&\Rf{u}-\Sf{tu}-		&\Sf{tu}\Df{d}\Ff{z}\If{i}		&\Sf{tu}\Df{d}\If{i}		&\Sf{tu}\Ff{s}\If{i}		&\Sf{tu}\Df{d}\Ef{a}		&\Sf{too}\df{\Ff{s}}		&\Sf{tu}\Ff{s}\Ef{a}		&\Sf{tu}\If{w}\Ef{a}		&\Sf{too}\\
\Qf{a}- expletive	&\Rf{u}-	&\Sf{tu}-	&\Qf{a}-\Rf{u}-\Sf{tu}-		&\Qf{a}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Sf{tu}\Df{d}\If{i}	&\Qf{a}\Sf{tu}\Ff{s}\If{i}	&\Qf{a}\Sf{tu}\Df{d}\Ef{a}	&\Qf{a}\Sf{too}\df{\Ff{s}}	&\Qf{a}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{a}\Sf{tu}\If{w}\Ef{a}	&\Qf{a}\Sf{too}\\
\Qf{ka}- qualifier	&\Rf{u}-	&\Sf{tu}-	&\Qf{ka}-\Rf{u}-\Sf{tu}-	&\Qf{ka}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\Sf{tu}\Df{d}\If{i}	&\Qf{ka}\Sf{tu}\Ff{s}\If{i}	&\Qf{ka}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ka}\Sf{too}\df{\Ff{s}}	&\Qf{ka}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ka}\Sf{tu}\If{w}\Ef{a}	&\Qf{ka}\Sf{too}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{u}-	&\Sf{tu}-	&\Qf{x̱ʼe}-\Rf{u}-\Sf{tu}-	&\Qf{x̱ʼa}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Sf{tu}\Df{d}\If{i}	&\Qf{x̱ʼa}\Sf{tu}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Sf{tu}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Sf{too}\df{\Ff{s}}	&\Qf{x̱ʼa}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Sf{tu}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Sf{too}\\
\Qf{ji}- ‘hand’		&\Rf{u}-	&\Sf{tu}-	&\Qf{ji}-\Rf{u}-\Sf{tu}-	&\Qf{ji}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\Sf{tu}\Df{d}\If{i}	&\Qf{ji}\Sf{tu}\Ff{s}\If{i}	&\Qf{ji}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ji}\Sf{too}\df{\Ff{s}}	&\Qf{ji}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ji}\Sf{tu}\If{w}\Ef{a}	&\Qf{ji}\Sf{too}\\
\Qf{tu}- ‘inside’	&\Rf{u}-	&\Sf{tu}-	&\Qf{tu}-\Rf{u}-\Sf{tu}-	&\Qf{tu}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\Sf{tu}\Df{d}\If{i}	&\Qf{tu}\Sf{tu}\Ff{s}\If{i}	&\Qf{tu}\Sf{tu}\Df{d}\Ef{a}	&\Qf{tu}\Sf{too}\df{\Ff{s}}	&\Qf{tu}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{tu}\Sf{tu}\If{w}\Ef{a}	&\Qf{tu}\Sf{too}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis \textit{u-}, first person plural subject \textit{tu-}}
\end{table}

%% Zero, Irrealis, 1PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{t}-			&\Df{t}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Rf{u}-	&\Sf{tʰu}-	&\Rf{u}-\Sf{tʰu}-		&\Sf{tʰu}.\Df{t}\Ff{s}\If{i}		&\Sf{tʰu}.\Df{t}\If{i}		&\Sf{tʰu}.\Ff{s}\If{i}		&\Sf{tʰu}.\Df{t}\Ef{a}		&\Sf{tʰuː}\df{\Ff{s}}		&\Sf{tʰu}.\Ff{s}\Ef{a}		&\Sf{tʰu}.\If{w}\Ef{a}		&\Sf{tʰuː}\\
\Qf{ʔa}- expletive	&\Rf{u}-	&\Sf{tʰu}-	&\Qf{ʔa}-\Rf{u}-\Sf{tʰu}-	&\Qf{ʔa}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{ʔa}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{ʔa}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{ʔa}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{ʔa}.\Sf{tʰuː}\\
\Qf{kʰa}- qualifier	&\Rf{u}-	&\Sf{tʰu}-	&\Qf{kʰa}-\Rf{u}-\Sf{tʰu}-	&\Qf{kʰa}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{kʰa}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{kʰa}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{kʰa}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{kʰa}.\Sf{tʰuː}\\
\Qf{χʼe}- ‘mouth’	&\Rf{u}-	&\Sf{tʰu}-	&\Qf{χʼe}-\Rf{u}-\Sf{tʰu}-	&\Qf{χʼa}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{χʼa}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{χʼa}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{χʼa}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{χʼa}.\Sf{tʰuː}\\
\Qf{tʃi}- ‘hand’	&\Rf{u}-	&\Sf{tʰu}-	&\Qf{tʃi}-\Rf{u}-\Sf{tʰu}-	&\Qf{tʃi}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{tʃi}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{tʃi}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʃi}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʃi}.\Sf{tʰuː}\\
\Qf{tʰu}- ‘inside’	&\Rf{u}-	&\Sf{tʰu}-	&\Qf{tʰu}-\Rf{u}-\Sf{tʰu}-	&\Qf{tʰu}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{tʰu}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{tʰu}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʰu}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʰu}.\Sf{tʰuː}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis /{u-}/, first person plural subject /{tʰu-}/, IPA}
\end{table}

\clearpage
%% Zero, Irrealis, 2SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Rf{u}-	&\Sf{i}-	&\Rf{u}-\Sf{i}-			&\Sf{i}\Df{d}\Ff{z}\If{i}		&\Sf{i}\Df{d}\If{i}		&\Sf{i}\Ff{s}\If{i}		&\Sf{i}\Df{d}\Ef{a}		&\Sf{ee}\df{\Ff{s}}		&\Sf{i}\Ff{s}\Ef{a}		&\Sf{i}\If{y}\Ef{a}		&\Sf{ee}\\
\Qf{a}- expletive	&\Rf{u}-	&\Sf{i}-	&\Qf{a}-\Rf{u}-\Sf{i}-		&\Qf{e}\Sf{e}\Df{d}\Ff{z}\If{i}		&\Qf{e}\Sf{e}\Df{d}\If{i}	&\Qf{e}\Sf{e}\Ff{s}\If{i}	&\Qf{e}\Sf{e}\Df{d}\Ef{a}	&\Qf{e}\Sf{e}\df{\Ff{s}}	&\Qf{e}\Sf{e}\Ff{s}\Ef{a}	&\Qf{e}\Sf{e}\If{y}\Ef{a}	&\Qf{e}\Sf{e}\\
\Qf{ka}- qualifier	&\Rf{u}-	&\Sf{i}-	&\Qf{ka}-\Rf{u}-\Sf{i}-		&\Qf{k}\Sf{ee}\Df{d}\Ff{z}\If{i}	&\Qf{k}\Sf{ee}\Df{d}\If{i}	&\Qf{k}\Sf{ee}\Ff{s}\If{i}	&\Qf{k}\Sf{ee}\Df{d}\Ef{a}	&\Qf{k}\Sf{ee}\df{\Ff{s}}	&\Qf{k}\Sf{ee}\Ff{s}\Ef{a}	&\Qf{k}\Sf{ee}\If{y}\Ef{a}	&\Qf{k}\Sf{ee}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{u}-	&\Sf{i}-	&\Qf{x̱ʼe}-\Rf{u}-\Sf{i}-	&\Qf{x̱ʼ}\Sf{ee}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼ}\Sf{ee}\Df{d}\If{i}	&\Qf{x̱ʼ}\Sf{ee}\Ff{s}\If{i}	&\Qf{x̱ʼ}\Sf{ee}\Df{d}\Ef{a}	&\Qf{x̱ʼ}\Sf{ee}\df{\Ff{s}}	&\Qf{x̱ʼ}\Sf{ee}\Ff{s}\Ef{a}	&\Qf{x̱ʼ}\Sf{ee}\If{y}\Ef{a}	&\Qf{x̱ʼ}\Sf{ee}\\
\Qf{ji}- ‘hand’		&\Rf{u}-	&\Sf{i}-	&\Qf{ji}-\Rf{u}-\Sf{i}-		&\Qf{j}\Sf{ee}\Df{d}\Ff{z}\If{i}	&\Qf{j}\Sf{ee}\Df{d}\If{i}	&\Qf{j}\Sf{ee}\Ff{s}\If{i}	&\Qf{j}\Sf{ee}\Df{d}\Ef{a}	&\Qf{j}\Sf{ee}\df{\Ff{s}}	&\Qf{j}\Sf{ee}\Ff{s}\Ef{a}	&\Qf{j}\Sf{ee}\If{y}\Ef{a}	&\Qf{j}\Sf{ee}\\
\Qf{tu}- ‘inside’	&\Rf{u}-	&\Sf{i}-	&\Qf{tu}-\Rf{u}-\Sf{i}-		&\Qf{t}\Sf{ee}\Df{d}\Ff{z}\If{i}	&\Qf{t}\Sf{ee}\Df{d}\If{i}	&\Qf{t}\Sf{ee}\Ff{s}\If{i}	&\Qf{t}\Sf{ee}\Df{d}\Ef{a}	&\Qf{t}\Sf{ee}\df{\Ff{s}}	&\Qf{t}\Sf{ee}\Ff{s}\Ef{a}	&\Qf{t}\Sf{ee}\If{y}\Ef{a}	&\Qf{t}\Sf{ee}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis \textit{u-}, second person singular subject \textit{i-}}
\end{table}

%% Zero, Irrealis, 2SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Rf{u}-	&\Sf{i}-	&\Rf{u}-\Sf{i}-			&\Sf{ʔi}.\Df{t}\Ff{s}\If{i}		&\Sf{ʔi}.\Df{t}\If{i}			&\Sf{ʔi}.\Ff{s}\If{i}			&\Sf{ʔi}.\Df{t}\Ef{a}			&\Sf{ʔiː}\df{\Ff{s}}			&\Sf{ʔi}.\Ff{s}\Ef{a}			&\Sf{ʔi}.\If{j}\Ef{a}			&\Sf{ʔiː}\\
\Qf{ʔa}- expletive	&\Rf{u}-	&\Sf{i}-	&\Qf{ʔa}-\Rf{u}-\Sf{i}-		&\Qf{ʔ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{ʔ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{ʔ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{ʔ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{ʔ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{ʔ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{ʔ}\Sf{i}\Qf{ː}\\
\Qf{kʰa}- qualifier	&\Rf{u}-	&\Sf{i}-	&\Qf{kʰa}-\Rf{u}-\Sf{i}-	&\Qf{kʰ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{kʰ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{kʰ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{kʰ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{kʰ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{kʰ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{kʰ}\Sf{i}\Qf{ː}\\
\Qf{χʼe}- ‘mouth’	&\Rf{u}-	&\Sf{i}-	&\Qf{χʼe}-\Rf{u}-\Sf{i}-	&\Qf{χʼ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{χʼ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{χʼ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{χʼ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{χʼ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{χʼ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{χʼ}\Sf{i}\Qf{ː}\\
\Qf{tʃi}- ‘hand’	&\Rf{u}-	&\Sf{i}-	&\Qf{tʃi}-\Rf{u}-\Sf{i}-	&\Qf{tʃ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{tʃ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{tʃ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{tʃ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{tʃ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{tʃ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{tʃ}\Sf{i}\Qf{ː}\\
\Qf{tʰu}- ‘inside’	&\Rf{u}-	&\Sf{i}-	&\Qf{tʰu}-\Rf{u}-\Sf{i}-	&\Qf{tʰ}\Sf{i}\Qf{ː}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰ}\Sf{i}\Qf{ː}.\Df{t}\If{i}	&\Qf{tʰ}\Sf{i}\Qf{ː}.\Ff{s}\If{i}	&\Qf{tʰ}\Sf{i}\Qf{ː}.\Df{t}\Ef{a}	&\Qf{tʰ}\Sf{i}\Qf{ː}\df{\Ff{s}}		&\Qf{tʰ}\Sf{i}\Qf{ː}.\Ff{s}\Ef{a}	&\Qf{tʰ}\Sf{i}\Qf{ː}.\If{j}\Ef{a}	&\Qf{tʰ}\Sf{i}\Qf{ː}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis /{u-}/, second person singular subject /{i-}/, IPA}
\end{table}

\clearpage
%% Zero, Irrealis, 2PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Rf{u}-	&\Sf{yi}-	&\Rf{u}-\Sf{yi}-		&\Sf{yeey}\Df{d}\Ff{z}\If{i}		&\Sf{yeey}\Df{d}\If{i}		&\Sf{yeey}\Ff{s}\If{i}		&\Sf{yi}\Df{d}\Ef{a}		&\Sf{yi}\df{\Ff{s}}		&\Sf{yi}\Ff{s}\Ef{a}		&\Sf{yee}\If{y}			&\Sf{yi}\\
\Qf{a}- expletive	&\Rf{u}-	&\Sf{yi}-	&\Qf{a}-\Rf{u}-\Sf{yi}-		&\Qf{a}\Sf{y}\Df{d}\Ff{z}\If{i}		&\Qf{a}\Sf{y}\Df{d}\If{i}	&\Qf{a}\Sf{y}\Ff{s}\If{i}	&\Qf{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{a}\Sf{yi}\df{\Ff{s}}	&\Qf{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{a}\Sf{yee}\If{y}		&\Qf{a}\Sf{y}\\
\Qf{ka}- qualifier	&\Rf{u}-	&\Sf{yi}-	&\Qf{ka}-\Rf{u}-\Sf{yi}-	&\Qf{ka}\Sf{y}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\Sf{y}\Df{d}\If{i}	&\Qf{ka}\Sf{y}\Ff{s}\If{i}	&\Qf{ka}\Sf{y}\Df{d}\Ef{a}	&\Qf{ka}\Sf{yi}\df{\Ff{s}}	&\Qf{ka}\Sf{y}\Ff{s}\Ef{a}	&\Qf{ka}\Sf{yee}\If{y}		&\Qf{ka}\Sf{y}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{u}-	&\Sf{yi}-	&\Qf{x̱ʼe}-\Rf{u}-\Sf{yi}-	&\Qf{x̱ʼa}\Sf{y}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Sf{y}\Df{d}\If{i}	&\Qf{x̱ʼa}\Sf{y}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Sf{y}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Sf{yi}\df{\Ff{s}}	&\Qf{x̱ʼa}\Sf{y}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Sf{yee}\If{y}		&\Qf{x̱ʼa}\Sf{y}\\
\Qf{ji}- ‘hand’		&\Rf{u}-	&\Sf{yi}-	&\Qf{ji}-\Rf{u}-\Sf{yi}-	&\Qf{ji}\Sf{y}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\Sf{y}\Df{d}\If{i}	&\Qf{ji}\Sf{y}\Ff{s}\If{i}	&\Qf{ji}\Sf{y}\Df{d}\Ef{a}	&\Qf{ji}\Sf{yi}\df{\Ff{s}}	&\Qf{ji}\Sf{y}\Ff{s}\Ef{a}	&\Qf{ji}\Sf{yee}\If{y}		&\Qf{ji}\Sf{y}\\
\Qf{tu}- ‘inside’	&\Rf{u}-	&\Sf{yi}-	&\Qf{tu}-\Rf{u}-\Sf{yi}-	&\Qf{tu}\Sf{y}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\Sf{y}\Df{d}\If{i}	&\Qf{tu}\Sf{y}\Ff{s}\If{i}	&\Qf{tu}\Sf{y}\Df{d}\Ef{a}	&\Qf{tu}\Sf{yi}\df{\Ff{s}}	&\Qf{tu}\Sf{y}\Ff{s}\Ef{a}	&\Qf{tu}\Sf{yee}\If{y}		&\Qf{tu}\Sf{y}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis \textit{u-}, second person plural subject \textit{yi-}}
\end{table}

%% Zero, Irrealis, 2PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{t}-			&\Df{t}-\Ff{s}\rlap{-}		&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Rf{u}-	&\Sf{ji}-	&\Rf{u}-\Sf{ji}-		&\Sf{jiːj}.\Df{t}\Ff{s}\If{i}		&\Sf{jiːj}.\Df{t}\If{i}		&\Sf{jiːj}.\Ff{s}\If{i}		&\Sf{ji}.\Df{t}\Ef{a}		&\Sf{ji}\df{\Ff{s}}		&\Sf{ji}.\Ff{s}\Ef{a}		&\Sf{jiː}\If{j}			&\Sf{ji}\\
\Qf{ʔa}- expletive	&\Rf{u}-	&\Sf{ji}-	&\Qf{ʔa}-\Rf{u}-\Sf{ji}-	&\Qf{ʔa}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔa}\Sf{j}.\Df{t}\If{i}	&\Qf{ʔa}\Sf{j}.\Ff{s}\If{i}	&\Qf{ʔa}\Sf{j}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Sf{ji}\df{\Ff{s}}	&\Qf{ʔa}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Sf{jiː}\If{j}		&\Qf{ʔa}\Sf{j}\\
\Qf{kʰa}- qualifier	&\Rf{u}-	&\Sf{ji}-	&\Qf{kʰa}-\Rf{u}-\Sf{ji}-	&\Qf{kʰa}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}\Sf{j}.\Df{t}\If{i}	&\Qf{kʰa}\Sf{j}.\Ff{s}\If{i}	&\Qf{kʰa}\Sf{j}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Sf{ji}\df{\Ff{s}}	&\Qf{kʰa}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Sf{jiː}\If{j}	&\Qf{kʰa}\Sf{j}\\
\Qf{χʼe}- ‘mouth’	&\Rf{u}-	&\Sf{ji}-	&\Qf{χʼe}-\Rf{u}-\Sf{ji}-	&\Qf{χʼa}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}\Sf{j}.\Df{t}\If{i}	&\Qf{χʼa}\Sf{j}.\Ff{s}\If{i}	&\Qf{χʼa}\Sf{j}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Sf{ji}\df{\Ff{s}}	&\Qf{χʼa}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Sf{jiː}\If{j}	&\Qf{χʼa}\Sf{j}\\
\Qf{tʃi}- ‘hand’	&\Rf{u}-	&\Sf{ji}-	&\Qf{tʃi}-\Rf{u}-\Sf{ji}-	&\Qf{tʃi}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}\Sf{j}.\Df{t}\If{i}	&\Qf{tʃi}\Sf{j}.\Ff{s}\If{i}	&\Qf{tʃi}\Sf{j}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʃi}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Sf{jiː}\If{j}	&\Qf{tʃi}\Sf{j}\\
\Qf{tʰu}- ‘inside’	&\Rf{u}-	&\Sf{ji}-	&\Qf{tʰu}-\Rf{u}-\Sf{ji}-	&\Qf{tʰu}\Sf{j}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}\Sf{j}.\Df{t}\If{i}	&\Qf{tʰu}\Sf{j}.\Ff{s}\If{i}	&\Qf{tʰu}\Sf{j}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʰu}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Sf{jiː}\If{j}	&\Qf{tʰu}\Sf{j}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis /{u-}/, second person plural subject /{ji-}/, IPA}
\end{table}

\clearpage
%% Zero, Irrealis, 4H
\begin{table}
\centerfloat
% Decrease \arraystretch because both tables are too tall.
\renewcommand{\arraystretch}{0.79}
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}\rlap{-}	&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}\rlap{-}	&\If{i}-				&—\\
\midrule
—			&\Rf{u}-	&\Sf{du}-	&\Rf{u}-\Sf{du}-		&\Sf{du}\Df{d}\Ff{z}\If{i}			&⁎			&⁎			&⁎		&\Sf{du}\df{\Ff{s}}			&⁎		&\Sf{du}\If{w}\Ef{a}			&\Sf{du}\\
			&		&		&				&\Rf{u}\Sf{du}\Df{d}\Ff{z}\If{i}\?		&⁎			&⁎			&⁎		&\Rf{u}\Sf{du}\df{\Ff{s}}		&⁎		&\Rf{u}\Sf{du}\If{w}\Ef{a}\?		&\Rf{u}\Sf{du}\\
\Qf{a}- expletive	&\Rf{u}-	&\Sf{du}-	&\Qf{a}-\Rf{u}-\Sf{du}-		&\Qf{a}\Sf{du}\Df{d}\Ff{z}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{a}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{a}\Sf{du}\If{w}\Ef{a}\?		&\Qf{a}\Sf{du}\\
\Qf{ka}- qualifier	&\Rf{u}-	&\Sf{du}-	&\Qf{ka}-\Rf{u}-\Sf{du}-	&\Qf{ko}\Rf{o}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{ko}\Rf{o}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ko}\Rf{o}\Sf{du}\If{w}\Ef{a}\?	&\Qf{ko}\Rf{o}\Sf{du}\\
			&		&		&				&\Qf{k}\Rf{u}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{k}\Rf{u}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{k}\Rf{u}\Sf{du}\If{w}\Ef{a}\?	&\Qf{k}\Rf{u}\Sf{du}\\
			&		&		&				&\Qf{ka}\Sf{du}\Df{d}\Ff{z}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{ka}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{ka}\Sf{du}\If{w}\Ef{a}\?		&\Qf{ka}\Sf{du}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{u}-	&\Sf{du}-	&\Qf{x̱ʼe}-\Rf{u}-\Sf{du}-	&\Qf{x̱ʼa}\Sf{du}\Df{d}\Ff{z}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{x̱ʼa}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{x̱ʼa}\Sf{du}\If{w}\Ef{a}\?		&\Qf{x̱ʼa}\Sf{du}\\
\Qf{ji}- ‘hand’		&\Rf{u}-	&\Sf{du}-	&\Qf{ji}-\Rf{u}-\Sf{du}-	&\Qf{je}\Rf{e}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{je}\Rf{e}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{je}\Rf{e}\Sf{du}\If{w}\Ef{a}\?	&\Qf{je}\Rf{e}\Sf{du}\\
			&		&		&				&\Qf{j}\Rf{u}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{j}\Rf{u}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{j}\Rf{u}\Sf{du}\If{w}\Ef{a}\?	&\Qf{j}\Rf{u}\Sf{du}\\
			&		&		&				&\Qf{ji}\Sf{du}\Df{d}\Ff{z}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{ji}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{ji}\Sf{du}\If{w}\Ef{a}\?		&\Qf{ji}\Sf{du}\\
\Qf{tu}- ‘inside’	&\Rf{u}-	&\Sf{du}-	&\Qf{tu}-\Rf{u}-\Sf{du}-	&\Qf{tu}\Sf{du}\Df{d}\Ff{z}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{tu}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{tu}\Sf{du}\If{w}\Ef{a}\?		&\Qf{tu}\Sf{du}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis \textit{u-}, fourth person (indefinite) human subject \textit{du-}}
% Omit table breaks to keep both tables together on one page.
%\end{table}

%% Zero, Irrealis, 4H, IPA
%\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}\rlap{-}	&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}\rlap{-}	&\If{i}-						&—\\
\midrule
—			&\Rf{u}-	&\Sf{tu}-	&\Rf{u}-\Sf{tu}-		&\Sf{tu}.\Df{t}\Ff{s}\If{i}				&⁎			&⁎			&⁎		&\Sf{tu}\df{\Ff{s}}				&⁎		&\Sf{tu}.\If{w}\Ef{a}\?					&\Sf{tu}\\
			&		&		&				&\Ef{ʔ}\Rf{u}\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Ef{ʔ}\Rf{u}\Sf{tu}\df{\Ff{s}}			&⁎		&\Ef{ʔ}\Rf{u}\Sf{tu}.\If{w}\Ef{a}\?			&\Ef{ʔ}\Rf{u}.\Sf{tu}\\
\Qf{ʔa}- expletive	&\Rf{u}-	&\Sf{tu}-	&\Qf{ʔa}-\Rf{u}-\Sf{tu}-	&\Qf{ʔa}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?			&⁎			&⁎			&⁎		&\Qf{ʔa}.\Sf{tu}\df{\Ff{s}}			&⁎		&\Qf{ʔa}.\Sf{tu}.\If{w}\Ef{a}\?				&\Qf{ʔa}\Sf{tu}\\
\Qf{kʰa}- qualifier	&\Rf{u}-	&\Sf{tu}-	&\Qf{kʰa}-\Rf{u}-\Sf{tu}-	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Sf{tu}.\If{w}\Ef{a}\?	&\Qf{kʰa}\Sf{tu}\\
			&		&		&				&\Qf{kʰ}\Rf{ʷ}\Qf{u}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{kʰ}\Rf{ʷ}\Qf{u}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{kʰ}\Rf{ʷ}\Qf{u}.\Sf{tu}.\If{w}\Ef{a}\?		&\Qf{kʰa}\Sf{tu}\\
			&		&		&				&\Qf{kʰa}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?			&⁎			&⁎			&⁎		&\Qf{kʰa}.\Sf{tu}\df{\Ff{s}}			&⁎		&\Qf{kʰa}.\Sf{tu}.\If{w}\Ef{a}\?			&\Qf{kʰa}\Sf{tu}\\
\Qf{χʼe}- ‘mouth’	&\Rf{u}-	&\Sf{tu}-	&\Qf{χʼe}-\Rf{u}-\Sf{tu}-	&\Qf{χʼa}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?			&⁎			&⁎			&⁎		&\Qf{χʼa}.\Sf{tu}\df{\Ff{s}}			&⁎		&\Qf{χʼa}.\Sf{tu}.\If{w}\Ef{a}\?			&\Qf{χʼa}\Sf{tu}\\
\Qf{tʃi}- ‘hand’	&\Rf{u}-	&\Sf{tu}-	&\Qf{tʃi}-\Rf{u}-\Sf{tu}-	&\Qf{tʃi}\Rf{ː}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{tʃi}\Rf{ː}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{tʃi}\Rf{ː}.\Sf{tu}.\If{w}\Ef{a}\?			&\Qf{tʃi}\Sf{tu}\\
			&		&		&				&\Qf{tʃ}\Rf{u}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{tʃ}\Rf{u}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{tʃ}\Rf{u}.\Sf{tu}.\If{w}\Ef{a}\?			&\Qf{tʃi}\Sf{tu}\\
			&		&		&				&\Qf{tʃi}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?			&⁎			&⁎			&⁎		&\Qf{tʃi}.\Sf{tu}\df{\Ff{s}}			&⁎		&\Qf{tʃi}.\Sf{tu}.\If{w}\Ef{a}\?			&\Qf{tʃi}\Sf{tu}\\
\Qf{tʰu}- ‘inside’	&\Rf{u}-	&\Sf{tu}-	&\Qf{tʰu}-\Rf{u}-\Sf{tu}-	&\Qf{tʰu}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?			&⁎			&⁎			&⁎		&\Qf{tʰu}.\Sf{tu}\df{\Ff{s}}			&⁎		&\Qf{tʰu}.\Sf{tu}.\If{w}\Ef{a}\?			&\Qf{tʰu}\Sf{tu}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis /{u-}/, fourth person (indefinite) human subject /{tu-}/, IPA}
\end{table}

\clearpage
%%%
%%% Unmarked aspect with modal
%%%
\subsection{Unmarked aspect with modal \textit{g̱-}}\label{sec:zero-modal}

\begin{multicols}{2}
\noindent
The modal prefix \fm{\Mf{g̱}-} can occur in unmarked aspect forms.
Imperfective aspect does not occur with the modal prefix \fm{\Mf{g̱}-}.
This means that the only unmarked aspect forms with \fm{\Mf{g̱}-} are \fm{∅}-conjugation class verbs with the combination of \fm{\Af{\xx{cnj}}-} + \fm{\Mf{g̱}-} where \fm{\Af{\xx{cnj}}-} = \fm{\Af{∅}}.
The \fm{\Mf{g̱}-} modal prefix only occurs in
\begin{inlineenum}
	\item	prospective (‘future’) aspect
	\item	potential modality
	\item	hortative mood
	\item	contingent mood.
\end{inlineenum}
The prospective aspect can only be formed with the \fm{\Af{g}-} conjugation prefix and so cannot have \fm{\Af{∅}}.
The potential modality can occur with \fm{\Af{∅}} but it also requires the presence of irrealis \fm{\Rf{u}-} (see section \ref{sec:zero-irrealis+modal}).
These restrictions mean that the only two contexts for forms with just \fm{\Af{∅}} and \fm{\Mf{g̱}-} are the hortative and the contingent of \fm{∅}-conjugation class verbs.

The forms in (\ref{ex:zero-modal-forms}) illustrate this pattern using the \fm{∅}-conjugation verb \fm{ax̱á} (\fm{∅}; \fm{-μH} activity) ‘s/he/it eats him/her/it’.
The imperative in (\ref{ex:zero-modal-forms-imp}) confirms that this is \fm{∅}-conjugation.
The hortative in (\ref{ex:zero-modal-forms-hort}) and the contingent in (\ref{ex:zero-modal-forms-hort}) show the resulting appearance of the argument marking \fm{\Qf{a}-}, the \fm{\Af{∅}} conjugation, and the \fm{\Mf{g̱}-} modal.

\pex\label{ex:zero-modal-forms}%
\a\label{ex:zero-modal-forms-imp}%
\exrtcmt{imperative}%
\begingl
	\gla	\rlap{\Sf{Yi}x̱á!} @ {} @ {} @ {} //
	\glb	\Af{∅} \Sf{yi}- \rt[²]{x̱a} -μH //
	\glc	\Af{\xx{zcnj}}\· \Sf{\xx{2sg·s}}- \rt[²]{eat} -\xx{var} //
	\gld	\rlap{3.\xx{imp}.you·\xx{pl}.eat} {} {} {} //
	\glft	‘You guys eat him/her/it!’
		//
\endgl
\a\label{ex:zero-modal-forms-hort}%
\exrtcmt{hortative}%
\begingl
	\gla	\rlap{\Qf{A}\Mf{g̱}\Ef{a}x̱aa.} @ {} @ {} @ {} @ {} //
	\glb	\Qf{a}- \Af{∅} \Mf{g̱}- \rt[²]{x̱a} -μμL //
	\glc	\Qf{\xx{arg}}- \Af{\xx{zcnj}}\· \Mf{\xx{mod}}- \rt[²]{eat} -\xx{var} //
	\gld	\rlap{3>3.\xx{hort}.eat}{} {} {} {}  //
	\glft	‘Let him/her/it eat him/her/it.’
		//
\endgl
\a\label{ex:zero-modal-forms-ctng}%
\exrtcmt{contingent}%
\begingl
	\gla	\rlap{\Qf{A}\Mf{g̱}\Ef{a}x̱éinín,} @ {} @ {} @ {} @ {} @ {} @ {} +
		\rlap{\Qf{a}\Af{k}\Ff{s}\Ef{a}néekwch.} @ {} @ {} @ {} @ {} @ {} //
	\glb	\Qf{a}- \Af{∅} \Mf{g̱}- \rt[²]{x̱a} -eμH -n -ín
		\Qf{a}- \Af{g}- \Ff{s}- \rt[¹]{nikw} -μμH -ch //
	\glc	\Qf{\xx{arg}}- \Af{\xx{zcnj}}\· \Mf{\xx{mod}}- \rt[²]{eat} -\xx{var} -\xx{nsfx} -\xx{ctng}
		\Qf{\xx{arg}}- \Af{\xx{gcnj}}- \Ff{\xx{csv}-} \rt[¹]{sick} -\xx{var} -\xx{rep} //
	\gld	\rlap{3>3.\xx{ctng}.eat} {} {} {} {} {} {}
		\rlap{3>3.\xx{hab}.\xx{csv}.sick} {} {} {} {} {} //
	\glft	‘Whenever s/he/it eats it, it makes him/her/it sick.’
		//
\endgl
\xe

The \fm{\Mf{g̱}-} modal prefix is homophonous with the \fm{\Af{g̱}-} conjugation prefix, but they can occur together (sec.\ \ref{sec:ghconj-modal}) so they cannot be analyzed as the being the same prefix.
Because these two prefixes are homophonous, unmarked aspect forms with the \fm{\Mf{g̱}-} modal prefix look identical to corresponding forms with the \fm{\Af{g̱}-} conjugation prefix.
But there are still crucial semantic and paradigmatic differences between modal \fm{\Mf{g̱}-} and conjugation \fm{\Af{g̱}-}.
Semantically, the \fm{\Mf{g̱}-} modal prefix only occurs in forms that express possibility or necessity which is not necessarily the case for forms with the \fm{\Af{g̱}-} conjugation prefix.
Paradigmatically, the hortative and contingent mentioned above are never found with the \fm{\If{i}-} stative prefix.
The tables in this section therefore have forms that are similar to those in section \ref{sec:ghconj} for the \fm{\Af{g̱}-} conjugation prefix, but the possible combinations of prefixes are different.
\end{multicols}

\clearpage
%% Zero, Modal, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-			&\If{i}-	&—\\
\midrule
—			&\Mf{g̱}-	&—		&\Mf{g̱}-		&⁎				&⁎			&⁎			&\Mf{g̱}\Ef{a}\Df{d}\Ef{a}	&\Mf{g̱}\Ef{a}\df{\Ff{s}}		&\Mf{g̱}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Mf{g̱}\Ef{a}\\
			&		&		&			&				&			&			&				&					&\#\Mf{g̱}\Ef{a}\Ff{s}		&		&\\
\Qf{a}- arg./expl.	&\Mf{g̱}-	&—		&\Qf{a}-\Mf{g̱}-		&⁎				&⁎			&⁎			&\Qf{a}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{a}\Mf{g̱}\Ef{a}\df{\Ff{s}}		&\Qf{a}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\Mf{g̱}\Ef{a}\\
\Qf{ka}- qualifier	&\Mf{g̱}-	&—		&\Qf{ka}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{ka}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{ka}\Mf{g̱}\Ef{a}\df{\Ff{s}}		&\Qf{ka}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Mf{g̱}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Mf{g̱}-	&—		&\Qf{x̱ʼe}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Mf{g̱}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Mf{g̱}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Mf{g̱}-	&—		&\Qf{ji}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{ji}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{ji}\Mf{g̱}\Ef{a}\df{\Ff{s}}		&\Qf{ji}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Mf{g̱}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Mf{g̱}-	&—		&\Qf{tu}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{tu}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{tu}\Mf{g̱}\Ef{a}\df{\Ff{s}}		&\Qf{tu}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Mf{g̱}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal \textit{g̱-}, unmarked subject (third person or no subject)}
\end{table}

%% Zero, Modal, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-	&—\\
\midrule
—			&\Mf{q}-	&—		&\Mf{q}-		&⁎				&⁎			&⁎			&\Mf{q}\Ef{a}.\Df{t}\Ef{a}		&\Mf{q}\Ef{a}\df{\Ff{s}}		&\Mf{q}\Ef{a}.\Ff{s}\Ef{a}		&⁎		&\Mf{q}\Ef{a}\\
			&		&		&			&				&			&			&					&					&\#\Mf{q}\Ef{a}\Ff{s}			&		&\\
\Qf{ʔa}- arg./expl.	&\Mf{q}-	&—		&\Qf{ʔa}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{ʔa}\Mf{χ}.\Df{t}\Ef{a}		&\Qf{ʔa}.\Mf{q}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}\Mf{χ}.\Ff{s}\Ef{a}		&⁎		&\Qf{ʔa}.\Mf{q}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Mf{q}-	&—		&\Qf{kʰa}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{kʰa}\Mf{χ}.\Df{t}\Ef{a}		&\Qf{kʰa}.\Mf{q}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}\Mf{χ}.\Ff{s}\Ef{a}		&⁎		&\Qf{kʰa}.\Mf{q}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Mf{q}-	&—		&\Qf{χʼe}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{χʼa}\Mf{χ}.\Df{t}\Ef{a}		&\Qf{χʼa}.\Mf{q}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}\Mf{χ}.\Ff{s}\Ef{a}		&⁎		&\Qf{χʼa}.\Mf{q}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Mf{q}-	&—		&\Qf{tʃi}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{tʃi}\Mf{χ}.\Df{t}\Ef{a}		&\Qf{tʃi}.\Mf{q}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}\Mf{χ}.\Ff{s}\Ef{a}		&⁎		&\Qf{tʃi}.\Mf{q}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Mf{q}-	&—		&\Qf{tʰu}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Mf{q}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}.\Mf{q}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal /{q-}/, unmarked subject (third person or no subject), IPA}
\end{table}

\clearpage
%% Zero, Modal, 1SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-	&—\\
\midrule
—			&\Mf{g̱}-	&\Sf{x̱}-	&\Mf{g̱}-\Sf{x̱}-			&⁎				&⁎			&⁎			&\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}		&\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}		&\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}		&⁎		&\mf{\Sf{ḵ}}\Ef{a}\\
\Qf{a}- expletive	&\Mf{g̱}-	&\Sf{x̱}-	&\Qf{a}-\Mf{g̱}-\Sf{x̱}-		&⁎				&⁎			&⁎			&\Qf{a}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{a}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{a}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\mf{\Sf{ḵ}}\Ef{a}\\
\Qf{ka}- qualifier	&\Mf{g̱}-	&\Sf{x̱}-	&\Qf{ka}-\Mf{g̱}-\Sf{x̱}-		&⁎				&⁎			&⁎			&\Qf{ka}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{ka}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{ka}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\mf{\Sf{ḵ}}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Mf{g̱}-	&\Sf{x̱}-	&\Qf{x̱ʼe}-\Mf{g̱}-\Sf{x̱}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Mf{g̱}-	&\Sf{x̱}-	&\Qf{ji}-\Mf{g̱}-\Sf{x̱}-		&⁎				&⁎			&⁎			&\Qf{ji}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{ji}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{ji}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\mf{\Sf{ḵ}}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Mf{g̱}-	&\Sf{x̱}-	&\Qf{tu}-\Mf{g̱}-\Sf{x̱}-		&⁎				&⁎			&⁎			&\Qf{tu}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{tu}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{tu}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\mf{\Sf{ḵ}}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal \textit{g̱-}, first person singular subject \textit{x̱-}}
\end{table}

%% Zero, Modal, 1SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-					&\If{i}-	&—\\
\midrule
—			&\Mf{q}-	&\Sf{χ}-	&\Mf{q}-\Sf{χ}-			&⁎				&⁎			&⁎			&\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}		&\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}		&\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}		&⁎		&\Mf{q}\Sf{ʰ}\Ef{a}\\
\Qf{ʔa}- expletive	&\Mf{q}-	&\Sf{χ}-	&\Qf{ʔa}-\Mf{q}-\Sf{χ}-		&⁎				&⁎			&⁎			&\Qf{ʔa}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&⁎		&\Qf{ʔa}.\Mf{q}\Sf{ʰ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Mf{q}-	&\Sf{χ}-	&\Qf{kʰa}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{kʰa}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&⁎		&\Qf{kʰa}.\Mf{q}\Sf{ʰ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Mf{q}-	&\Sf{χ}-	&\Qf{χʼe}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&⁎		&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Mf{q}-	&\Sf{χ}-	&\Qf{tʃi}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Mf{q}-	&\Sf{χ}-	&\Qf{tʰu}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{tʰu}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}.\Mf{q}\Sf{ʰ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal /{q-}/, first person singular subject /{χ-}/, IPA}
\end{table}

\clearpage
%% Zero, Modal, 1PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-	&—\\
\midrule
—			&\Mf{g̱}-	&\Sf{tu}-	&\Mf{g̱}-\Sf{tu}-		&⁎				&⁎			&⁎			&\Mf{g̱}\Ef{a}\Sf{tu}\Df{d}\Ef{a}	&\Mf{g̱}\Ef{a}\Sf{too}\df{\Ff{s}}	&\Mf{g̱}\Ef{a}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Mf{g̱}\Ef{a}\Sf{too}\\
\Qf{a}- expletive	&\Mf{g̱}-	&\Sf{tu}-	&\Qf{a}-\Mf{g̱}-\Sf{tu}-		&⁎				&⁎			&⁎			&\Qf{a}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{a}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{a}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\Mf{x̱}\Sf{too}\\
\Qf{ka}- qualifier	&\Mf{g̱}-	&\Sf{tu}-	&\Qf{ka}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{ka}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ka}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{ka}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Mf{x̱}\Sf{too}\\
\Qf{x̱ʼe}- ‘mouth’	&\Mf{g̱}-	&\Sf{tu}-	&\Qf{x̱ʼe}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{x̱ʼa}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Mf{x̱}\Sf{too}\\
\Qf{ji}- ‘hand’		&\Mf{g̱}-	&\Sf{tu}-	&\Qf{ji}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{ji}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ji}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{ji}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Mf{x̱}\Sf{too}\\
\Qf{tu}- ‘inside’	&\Mf{g̱}-	&\Sf{tu}-	&\Qf{tu}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{tu}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{tu}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{tu}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Mf{x̱}\Sf{too}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal \textit{g̱-}, first person plural subject \textit{tu-}}
\end{table}

%% Zero, Modal, 1PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-	&—\\
\midrule                                                                                                                                                                                                                                                                                                                                
—			&\Mf{q}-	&\Sf{tʰu}-	&\Mf{q}-\Sf{tʰu}-		&⁎				&⁎			&⁎			&\Mf{q}\Ef{a}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Mf{q}\Ef{a}.\Sf{tʰuː}\df{\Ff{s}}		&\Mf{q}\Ef{a}.\Sf{tʰu}.\Ff{s}\Ef{a}		&⁎		&\Mf{q}\Ef{a}.\Sf{tʰuː}\\
\Qf{ʔa}- expletive	&\Mf{q}-	&\Sf{tʰu}-	&\Qf{ʔa}-\Mf{q}-\Sf{tʰu}-	&⁎				&⁎			&⁎			&\Qf{ʔa}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{ʔa}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{ʔa}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&⁎		&\Qf{ʔa}\Mf{χ}.\Sf{tʰuː}\\
\Qf{kʰa}- qualifier	&\Mf{q}-	&\Sf{tʰu}-	&\Qf{kʰa}-\Mf{q}-\Sf{tʰu}-	&⁎				&⁎			&⁎			&\Qf{kʰa}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{kʰa}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{kʰa}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&⁎		&\Qf{kʰa}\Mf{χ}.\Sf{tʰuː}\\
\Qf{χʼe}- ‘mouth’	&\Mf{q}-	&\Sf{tʰu}-	&\Qf{χʼe}-\Mf{q}-\Sf{tʰu}-	&⁎				&⁎			&⁎			&\Qf{χʼa}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{χʼa}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{χʼa}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&⁎		&\Qf{χʼa}\Mf{χ}.\Sf{tʰuː}\\
\Qf{tʃi}- ‘hand’	&\Mf{q}-	&\Sf{tʰu}-	&\Qf{tʃi}-\Mf{q}-\Sf{tʰu}-	&⁎				&⁎			&⁎			&\Qf{tʃi}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{tʃi}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{tʃi}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&⁎		&\Qf{tʃi}\Mf{χ}.\Sf{tʰuː}\\
\Qf{tʰu}- ‘inside’	&\Mf{q}-	&\Sf{tʰu}-	&\Qf{tʰu}-\Mf{q}-\Sf{tʰu}-	&⁎				&⁎			&⁎			&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{tʰu}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{tʰuː}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal /{q-}/, first person plural subject /{tʰu-}/, IPA}
\end{table}

\clearpage
%% Zero, Modal, 2SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-	&—\\
\midrule                                                                                                                                                                                                                                                                                                        
—			&\Mf{g̱}-	&\Sf{i}-	&\Mf{g̱}-\Sf{i}-			&⁎				&⁎			&⁎			&\Mf{g̱}\Sf{i}\Df{d}\Ef{a}		&\Mf{g̱}\Sf{ee}\df{\Ff{s}}		&\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}		&⁎		&\Mf{g̱}\Sf{ee}\\
\Qf{a}- expletive	&\Mf{g̱}-	&\Sf{i}-	&\Qf{a}-\Mf{g̱}-\Sf{i}-		&⁎				&⁎			&⁎			&\Qf{a}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}		&\Qf{a}\Mf{g̱}\Sf{ee}\df{\Ff{s}}		&\Qf{a}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}		&⁎		&\Qf{a}\Mf{g̱}\Sf{ee}\\
\Qf{ka}- qualifier	&\Mf{g̱}-	&\Sf{i}-	&\Qf{ka}-\Mf{g̱}-\Sf{i}-		&⁎				&⁎			&⁎			&\Qf{ka}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{ka}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{ka}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Mf{g̱}\Sf{ee}\\
\Qf{x̱ʼe}- ‘mouth’	&\Mf{g̱}-	&\Sf{i}-	&\Qf{x̱ʼe}-\Mf{g̱}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{x̱ʼa}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Mf{g̱}\Sf{ee}\\
\Qf{ji}- ‘hand’		&\Mf{g̱}-	&\Sf{i}-	&\Qf{ji}-\Mf{g̱}-\Sf{i}-		&⁎				&⁎			&⁎			&\Qf{ji}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{ji}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{ji}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Mf{g̱}\Sf{ee}\\
\Qf{tu}- ‘inside’	&\Mf{g̱}-	&\Sf{i}-	&\Qf{tu}-\Mf{g̱}-\Sf{i}-		&⁎				&⁎			&⁎			&\Qf{tu}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{tu}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{tu}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Mf{g̱}\Sf{ee}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal \textit{g̱-}, second person singular subject \textit{i-}}
\end{table}

%% Zero, Modal, 2SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-	&—\\
\midrule                                                                                                                                                                                                                                                                                                        
—			&\Mf{q}-	&\Sf{i}-	&\Mf{q}-\Sf{i}-			&⁎				&⁎			&⁎			&\Mf{q}\Sf{i}.\Df{t}\Ef{a}		&\Mf{q}\Sf{iː}\df{\Ff{s}}		&\Mf{q}\Sf{i}.\Ff{s}\Ef{a}		&⁎		&\Mf{q}\Sf{iː}\\
\Qf{ʔa}- expletive	&\Mf{q}-	&\Sf{i}-	&\Qf{ʔa}-\Mf{q}-\Sf{i}-		&⁎				&⁎			&⁎			&\Qf{ʔa}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{ʔa}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{ʔa}.\Mf{q}\Sf{iː}\\
\Qf{kʰa}- qualifier	&\Mf{q}-	&\Sf{i}-	&\Qf{kʰa}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{kʰa}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{kʰa}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{kʰa}.\Mf{q}\Sf{iː}\\
\Qf{χʼe}- ‘mouth’	&\Mf{q}-	&\Sf{i}-	&\Qf{χʼe}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{χʼa}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{χʼa}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{χʼa}.\Mf{q}\Sf{iː}\\
\Qf{tʃi}- ‘hand’	&\Mf{q}-	&\Sf{i}-	&\Qf{tʃi}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{tʃi}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{tʃi}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʃi}.\Mf{q}\Sf{iː}\\
\Qf{tʰu}- ‘inside’	&\Mf{q}-	&\Sf{i}-	&\Qf{tʰu}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{tʰu}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{tʰu}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}.\Mf{q}\Sf{iː}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal /{q-}/, second person singular subject /{i-}/, IPA}
\end{table}

\clearpage
%% Zero, Modal, 2PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-	&—\\
\midrule                                                                                                                                                                                                                                                                                                        
—			&\Mf{g̱}-	&\Sf{yi}-	&\Mf{g̱}-\Sf{yi}-		&⁎				&⁎			&⁎			&\Mf{g̱}\Ef{a}\Sf{y}\Df{d}\Ef{a}		&\Mf{g̱}\Ef{a}\Sf{yi}\df{\Ff{s}}		&\Mf{g̱}\Ef{a}\Sf{y}\Ff{s}\Ef{a}		&⁎		&\Mf{g̱}\Ef{a}\Sf{yi}\\
\Qf{a}- expletive	&\Mf{g̱}-	&\Sf{yi}-	&\Qf{a}-\Mf{g̱}-\Sf{yi}-		&⁎				&⁎			&⁎			&\Qf{a}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{a}\Mf{x̱}\Sf{yi}\df{\Ff{s}}		&\Qf{a}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\Mf{x̱}\Sf{yi}\\
\Qf{ka}- qualifier	&\Mf{g̱}-	&\Sf{yi}-	&\Qf{ka}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{ka}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{ka}\Mf{x̱}\Sf{yi}\df{\Ff{s}}	&\Qf{ka}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Mf{x̱}\Sf{yi}\\
\Qf{x̱ʼe}- ‘mouth’	&\Mf{g̱}-	&\Sf{yi}-	&\Qf{x̱ʼe}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Mf{x̱}\Sf{yi}\df{\Ff{s}}	&\Qf{x̱ʼa}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Mf{x̱}\Sf{yi}\\
\Qf{ji}- ‘hand’		&\Mf{g̱}-	&\Sf{yi}-	&\Qf{ji}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{ji}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{ji}\Mf{x̱}\Sf{yi}\df{\Ff{s}}	&\Qf{ji}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Mf{x̱}\Sf{yi}\\
\Qf{tu}- ‘inside’	&\Mf{g̱}-	&\Sf{yi}-	&\Qf{tu}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{tu}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{tu}\Mf{x̱}\Sf{yi}\df{\Ff{s}}	&\Qf{tu}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Mf{x̱}\Sf{yi}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal \textit{g̱-}, second person plural subject \textit{yi-}}
\end{table}

%% Zero, Modal, 2PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-	&—\\
\midrule                                                                                                                                                                                                                                                                                                                                
—			&\Mf{q}-	&\Sf{ji}-	&\Mf{q}-\Sf{ji}-		&⁎				&⁎			&⁎			&\Mf{q}\Ef{a}\Sf{j}.\Df{t}\Ef{a}		&\Mf{q}\Ef{a}\Sf{ji}\df{\Ff{s}}			&\Mf{q}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}		&⁎		&\Mf{q}\Ef{a}.\Sf{ji}\\
\Qf{ʔa}- expletive	&\Mf{q}-	&\Sf{ji}-	&\Qf{ʔa}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{ʔa}\Mf{χ}.\Sf{ji}.\Df{t}\Ef{a}		&\Qf{ʔa}\Mf{χ}.\Sf{ji}\df{\Ff{s}}		&\Qf{ʔa}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&⁎		&\Qf{ʔa}\Mf{χ}.\Sf{ji}\\
\Qf{kʰa}- qualifier	&\Mf{q}-	&\Sf{ji}-	&\Qf{kʰa}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{kʰa}\Mf{χ}.\Sf{ji}.\Df{t}\Ef{a}		&\Qf{kʰa}\Mf{χ}.\Sf{ji}\df{\Ff{s}}		&\Qf{kʰa}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&⁎		&\Qf{kʰa}\Mf{χ}.\Sf{ji}\\
\Qf{χʼe}- ‘mouth’	&\Mf{q}-	&\Sf{ji}-	&\Qf{χʼe}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{χʼa}\Mf{χ}.\Sf{ji}.\Df{t}\Ef{a}		&\Qf{χʼa}\Mf{χ}.\Sf{ji}\df{\Ff{s}}		&\Qf{χʼa}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&⁎		&\Qf{χʼa}\Mf{χ}.\Sf{ji}\\
\Qf{tʃi}- ‘hand’	&\Mf{q}-	&\Sf{ji}-	&\Qf{tʃi}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{tʃi}\Mf{χ}.\Sf{ji}.\Df{t}\Ef{a}		&\Qf{tʃi}\Mf{χ}.\Sf{ji}\df{\Ff{s}}		&\Qf{tʃi}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&⁎		&\Qf{tʃi}\Mf{χ}.\Sf{ji}\\
\Qf{tʰu}- ‘inside’	&\Mf{q}-	&\Sf{ji}-	&\Qf{tʰu}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{ji}.\Df{t}\Ef{a}	&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{ji}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{ji}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal /{q-}/, second person plural subject /{ji-}/, IPA}
\end{table}

\clearpage
%% Zero, Modal, 4H
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccc
		rccr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-	&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-	&\If{i}-	&—\\
\midrule                                                                                                                                                                                                                                                        
—			&\Mf{g̱}-	&\Sf{du}-	&\Mf{g̱}-\Sf{du}-		&⁎				&⁎			&⁎			&⁎		&\Mf{g̱}\Ef{a}\Sf{du}\df{\Ff{s}}		&⁎		&⁎		&\Mf{g̱}\Ef{a}\Sf{du}\\
\Qf{a}- expletive	&\Mf{g̱}-	&\Sf{du}-	&\Qf{a}-\Mf{g̱}-\Sf{du}-		&⁎				&⁎			&⁎			&⁎		&\Qf{a}\Mf{x̱}\Sf{du}\df{\Ff{s}}		&⁎		&⁎		&\Qf{a}\Mf{x̱}\Sf{du}\\
\Qf{ka}- qualifier	&\Mf{g̱}-	&\Sf{du}-	&\Qf{ka}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{ka}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{ka}\Mf{x̱}\Sf{du}\\
\Qf{x̱ʼe}- ‘mouth’	&\Mf{g̱}-	&\Sf{du}-	&\Qf{x̱ʼe}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{x̱ʼa}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{x̱ʼa}\Mf{x̱}\Sf{du}\\
\Qf{ji}- ‘hand’		&\Mf{g̱}-	&\Sf{du}-	&\Qf{ji}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{ji}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{ji}\Mf{x̱}\Sf{du}\\
\Qf{tu}- ‘inside’	&\Mf{g̱}-	&\Sf{du}-	&\Qf{tu}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{tu}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{tu}\Mf{x̱}\Sf{du}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal \textit{g̱-}, fourth person (indefinite) human subject \textit{du-}}
\end{table}

%% Zero, Modal, 4H, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccc
		rccr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-	&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-	&\If{i}-	&—\\
\midrule                                                                                                                                                                                                                                                                
—			&\Mf{q}-	&\Sf{tu}-	&\Mf{q}-\Sf{tu}-		&⁎				&⁎			&⁎			&⁎		&\Mf{q}\Ef{a}.\Sf{tu}\df{\Ff{s}}		&⁎		&⁎		&\Mf{q}\Ef{a}.\Sf{tu}\\
\Qf{ʔa}- expletive	&\Mf{q}-	&\Sf{tu}-	&\Qf{ʔa}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{ʔa}\Mf{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&⁎		&\Qf{ʔa}\Mf{χ}.\Sf{tu}\\
\Qf{kʰa}- qualifier	&\Mf{q}-	&\Sf{tu}-	&\Qf{kʰa}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{kʰa}\Mf{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&⁎		&\Qf{kʰa}\Mf{χ}.\Sf{tu}\\
\Qf{χʼe}- ‘mouth’	&\Mf{q}-	&\Sf{tu}-	&\Qf{χʼe}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{χʼa}\Mf{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&⁎		&\Qf{χʼa}\Mf{χ}.\Sf{tu}\\
\Qf{tʃi}- ‘hand’	&\Mf{q}-	&\Sf{tu}-	&\Qf{tʃi}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{tʃi}\Mf{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&⁎		&\Qf{tʃi}\Mf{χ}.\Sf{tu}\\
\Qf{tʰu}- ‘inside’	&\Mf{q}-	&\Sf{tu}-	&\Qf{tʰu}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{tu}\df{\Ff{s}}	&⁎		&⁎		&\Qf{tʰu}\Mf{χ}\Qf{ʷ}.\Sf{tu}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with modal /{q-}/, fourth person (indefinite) human subject /{tu-}/, IPA}
\end{table}

%%%
%%% Unmarked aspect with irrealis and modal
%%%
\clearpage
\subsection{Unmarked aspect with irrealis \textit{u-} and modal \textit{g̱-}}\label{sec:zero-irrealis+modal}

\begin{multicols}{2}
\noindent
The combination of irrealis \fm{\Rf{u}-} and modal \fm{\Mf{g̱}-} is possible with unmarked aspect.
Since the imperfective aspect does not occur with modal \fm{\Mf{g̱}-}, it is not a surprise that the addition of \fm{\Rf{u}-} to \fm{\Mf{g̱}-} is also impossible for imperfective aspect.
All unmarked aspect forms with irrealis \fm{\Rf{u}-} and modal \fm{\Mf{g̱}-} are therefore \fm{∅}-conjugation class verbs where the prefix for conjugation class is required.
As noted earlier in subsection \ref{sec:zero-modal}, the only context for all three of irrealis \fm{\Rf{u}-}, the \fm{∅} conjugation prefix, and modal \fm{\Mf{g̱}-} is the potential modality.
All prefix combinations in this subsection therefore represent a subset of potential modality forms.
The examples in (\ref{ex:zero-irrealis+modal-forms}) illustrate one \fm{∅}-conjugation verb with potential modality, namely the verb \fm{as.ée} (\fm{∅}; \fm{-μμH} activity) ‘s/he/it makes him/her/it become cooked’.

Potential modality forms normally include the stative \fm{\If{i}-} classifier prefix as seen in (\ref{ex:zero-irrealis+modal-forms-pot}).
The only context where they are known to lack \fm{\If{i}-} is when they are marked for past tense (“decessive”) with the past suffix \fm{-ín}.
The combination of past tense with potential modality is shown in (\ref{ex:zero-irrealis+modal-forms-pot+past}).
We would expect subordinate clause forms of potential modality to also lack \fm{\If{i}-} but there are no attested examples and no records of testing this possibility.
Crucially, negation of a potential modality form does not suppress \fm{\If{i}-} unlike negation of other forms with \fm{\If{i}-}.

\pex\label{ex:zero-irrealis+modal-forms}%
\a\label{ex:zero-irrealis+modal-forms-imp}%
\exrtcmt{imperative}%
\begingl
	\gla	\rlap{\Sf{Yi}\Ff{s}\Ef{a}.í!} @ {} @ {} @ {} @ {} //
	\glb	\Af{∅} \Sf{yi}- \Ff{s}- \rt[¹]{.i} -μH //
	\glc	\Af{\xx{zcnj}}\· \Sf{\xx{2pl·s}}- \Ff{\xx{csv}}- \rt[¹]{cook} -\xx{var} //
	\gld	\rlap{\xx{imp}.you·\xx{pl}.make.cooked} {} {} {} {} //
	\glft	‘You guys cook it!’
		//
\endgl
\a\label{ex:zero-irrealis+modal-forms-pot}%
\exrtcmt{potential}%
\begingl
	\gla	\rlap{\Qf{O}\Rf{o}\Mf{x̱}\Ff{s}\If{i}.ee.} @ {} @ {} @ {} @ {} @ {} @ {} @ {} //
	\glb	\Qf{a}- \Rf{u}- \Af{∅} \Mf{g̱}- \Ff{s}- \If{i}- \rt[¹]{.i} -μμL //
	\glc	\Qf{\xx{arg}}- \Rf{\xx{irr}}- \Af{\xx{zcnj}}\· \Mf{\xx{mod}}- \Ff{\xx{csv}}- \If{\xx{stv}}- \rt[¹]{cook} -\xx{var} //
	\gld	\rlap{3>3.\xx{pot}.make.cooked} {} {} {} {} {} {} //
	\glft	‘S/he/it can cook him/her/it.’
		//
\endgl
\a\label{ex:zero-irrealis+modal-forms-pot+past}%
\exrtcmt{past potential}%
\begingl
	\gla	\rlap{\Qf{O}\Rf{o}\Mf{x̱}\Ff{s}\Ef{a}.eeyín.} @ {} @ {} @ {} @ {} @ {} @ {} @ {} @ {} //
	\glb	\Qf{a}- \Rf{u}- \Af{∅} \Mf{g̱}- \Ff{s}- \phantom{\If{i}-} \rt[¹]{.i} -μμL -ín //
	\glc	\Qf{\xx{arg}}- \Rf{\xx{irr}}- \Af{\xx{zcnj}}\· \Mf{\xx{mod}}- \Ff{\xx{csv}}- \phantom{\If{\xx{stv}}-} \rt[¹]{cook} -\xx{var} -\xx{past} //
	\gld	\rlap{3>3.\xx{pot}.make.cooked.\xx{past}} {} {} {} {} {} {} {} //
	\glft	‘S/he/it could/woud have cooked him/her/it.’
		//
\endgl
\xe
\end{multicols}

\clearpage
%% Zero, Irrealis, Modal, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Rf{u}-\Mf{g̱}-	&—		&\Rf{u}-\Mf{g̱}-			&\Mf{g̱}\Rf{w}\Ef{a}\Df{d}\Ff{z}\If{i}	&\Mf{g̱}\Rf{w}\Ef{a}\Df{d}\If{i}		&\Mf{g̱}\Rf{w}\Ef{a}\Ff{s}\If{i}		&\Mf{g̱}\Rf{w}\Ef{a}\Df{d}\Ef{a}		&\Mf{g̱}\Rf{w}\Ef{a}\df{\Ff{s}}		&\Mf{g̱}\Rf{w}\Ef{a}\Ff{s}\Ef{a}		&\Mf{g̱}\Rf{w}\Ef{a}\If{a}		&\Mf{g̱}\Rf{w}\Ef{a}\\
\Qf{a}- arg./expl.	&\Rf{u}-\Mf{g̱}-	&—		&\Qf{a}-\Rf{u}-\Mf{g̱}-		&\Qf{o}\Rf{o}\Mf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{o}\Rf{o}\Mf{x̱}\Df{d}\If{i}		&\Qf{o}\Rf{o}\Mf{x̱}\Ff{s}\If{i}		&\Qf{o}\Rf{o}\Mf{x̱}\Df{d}\Ef{a}		&\Qf{o}\Rf{o}\Mf{g̱}\Ef{a}\df{\Ff{s}}	&\Qf{o}\Rf{o}\Mf{x̱}\Ff{s}\Ef{a}		&\Qf{o}\Rf{o}\Mf{g̱}\Ef{a}\If{a}		&\Qf{o}\Rf{o}\Mf{g̱}\Ef{a}\\
			&		&		&				&\Qf{a}\Mf{x̱}\Rf{w}\Df{d}\Ff{z}\If{i}	&\Qf{a}\Mf{x̱}\Rf{w}\Df{d}\If{i}		&\Qf{a}\Mf{x̱}\Rf{w}\Ff{s}\If{i}		&\Qf{a}\Mf{x̱}\Rf{w}\Df{d}\Ef{a}		&\Qf{a}\Mf{g̱}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{a}\Mf{x̱}\Rf{w}\Ff{s}\Ef{a}		&\Qf{a}\Mf{g̱}\Rf{w}\Ef{a}\If{a}		&\Qf{a}\Mf{g̱}\Rf{w}\Ef{a}\\
\Qf{ka}- qualifier	&\Rf{u}-\Mf{g̱}-	&—		&\Qf{ka}-\Rf{u}-\Mf{g̱}-		&\Qf{ko}\Rf{o}\Mf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{ko}\Rf{o}\Mf{x̱}\Df{d}\If{i}	&\Qf{ko}\Rf{o}\Mf{x̱}\Ff{s}\If{i}	&\Qf{ko}\Rf{o}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{ko}\Rf{o}\Mf{g̱}\Ef{a}\df{\Ff{s}}	&\Qf{ko}\Rf{o}\Mf{x̱}\Ff{s}\Ef{a}	&\Qf{ko}\Rf{o}\Mf{g̱}\Ef{a}\If{a}	&\Qf{ko}\Rf{o}\Mf{g̱}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{u}-\Mf{g̱}-	&—		&\Qf{x̱ʼe}-\Rf{u}-\Mf{g̱}-	&\Qf{x̱ʼe}\Rf{i}\Mf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼe}\Rf{i}\Mf{x̱}\Df{d}\If{i}	&\Qf{x̱ʼe}\Rf{i}\Mf{x̱}\Ff{s}\If{i}	&\Qf{x̱ʼe}\Rf{i}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{x̱ʼe}\Rf{i}\Mf{g̱}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼe}\Rf{i}\Mf{x̱}\Ff{s}\Ef{a}	&\Qf{x̱ʼe}\Rf{i}\Mf{g̱}\Ef{a}\If{a}	&\Qf{x̱ʼe}\Rf{i}\Mf{g̱}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Rf{u}-\Mf{g̱}-	&—		&\Qf{ji}-\Rf{u}-\Mf{g̱}-		&\Qf{je}\Rf{e}\Mf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{je}\Rf{e}\Mf{x̱}\Df{d}\If{i}	&\Qf{je}\Rf{e}\Mf{x̱}\Ff{s}\If{i}	&\Qf{je}\Rf{e}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{je}\Rf{e}\Mf{g̱}\Ef{a}\df{\Ff{s}}	&\Qf{je}\Rf{e}\Mf{x̱}\Ff{s}\Ef{a}	&\Qf{je}\Rf{e}\Mf{g̱}\Ef{a}\If{a}	&\Qf{je}\Rf{e}\Mf{g̱}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Rf{u}-\Mf{g̱}-	&—		&\Qf{tu}-\Rf{u}-\Mf{g̱}-		&\Qf{to}\Rf{o}\Mf{x̱}\Df{d}\Ff{z}\If{i}	&\Qf{to}\Rf{o}\Mf{x̱}\Df{d}\If{i}	&\Qf{to}\Rf{o}\Mf{x̱}\Ff{s}\If{i}	&\Qf{to}\Rf{o}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{to}\Rf{o}\Mf{g̱}\Ef{a}\df{\Ff{s}}	&\Qf{to}\Rf{o}\Mf{x̱}\Ff{s}\Ef{a}	&\Qf{to}\Rf{o}\Mf{g̱}\Ef{a}\If{a}	&\Qf{to}\Rf{o}\Mf{g̱}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with ireralis \textit{u-} and modal \textit{g̱-}, unmarked subject (third person or no subject)}
\end{table}

%% Zero, Irrealis, Modal, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}					&\Df{t}-\If{i}\rlap{-}					&\Ff{s}-\If{i}\rlap{-}					&\Df{t}-						&\Df{t}-\Ff{s}\rlap{-}					&\Ff{s}-						&\If{i}-					&—\\
\midrule
—			&\Rf{u}-\Mf{q}-	&—		&\Rf{u}-\Mf{q}-			&\Mf{q}\Rf{ʷ}\Ef{a}.\Df{t}\Ff{s}\If{i}				&\Mf{q}\Rf{ʷ}\Ef{a}.\Df{t}\If{i}			&\Mf{q}\Rf{ʷ}\Ef{a}.\Ff{s}\If{i}			&\Mf{q}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}			&\Mf{q}\Rf{ʷ}\Ef{a}\df{\Ff{s}}				&\Mf{q}\Rf{ʷ}\Ef{a}.\Ff{s}\Ef{a}			&\Mf{q}\Rf{ʷ}\Ef{a}\If{a}			&\Mf{q}\Rf{ʷ}\Ef{a}\\
\Qf{ʔa}- arg./expl.	&\Rf{u}-\Mf{q}-	&—		&\Qf{ʔa}-\Rf{u}-\Mf{q}-		&\Qf{ʔu}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}			&\Qf{ʔu}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Df{t}\If{i}			&\Qf{ʔu}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Ff{s}\If{i}			&\Qf{ʔu}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}			&\Qf{ʔu}\Rf{ː}.\Mf{q}\Ef{a}\df{\Ff{s}}			&\Qf{ʔu}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}			&\Qf{ʔu}\Rf{ː}.\Mf{q}\Ef{a}\If{a}		&\Qf{ʔu}\Rf{ː}.\Mf{q}\Ef{a}\\
			&		&		&				&\Qf{ʔa}\Mf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}				&\Qf{ʔa}\Mf{χ}\Rf{ʷ}.\Df{t}\If{i}			&\Qf{ʔa}\Mf{χ}\Rf{ʷ}.\Ff{s}\If{i}			&\Qf{ʔa}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}			&\Qf{ʔa}.\Mf{q}\Rf{ʷ}\Ef{a}\df{\Ff{s}}			&\Qf{ʔa}\Mf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}			&\Qf{ʔa}.\Mf{q}\Rf{ʷ}\Ef{a}\If{a}		&\Qf{ʔa}.\Mf{q}\Rf{ʷ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Rf{u}-\Mf{q}-	&—		&\Qf{kʰa}-\Rf{u}-\Mf{q}-	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Df{t}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Ff{s}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Ef{a}\df{\Ff{s}}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}\Mf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Ef{a}\If{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Rf{u}-\Mf{q}-	&—		&\Qf{χʼe}-\Rf{u}-\Mf{q}-	&\Qf{χʼe}\Rf{ː}\Mf{χ}.\Df{t}\Ff{s}\If{i}			&\Qf{χʼe}\Rf{ː}\Mf{χ}.\Df{t}\If{i}			&\Qf{χʼe}\Rf{ː}\Mf{χ}.\Ff{s}\If{i}			&\Qf{χʼe}\Rf{ː}\Mf{χ}.\Df{t}\Ef{a}			&\Qf{χʼe}\Rf{ː}.\Mf{q}\Ef{a}\df{\Ff{s}}			&\Qf{χʼe}\Rf{ː}\Mf{χ}.\Ff{s}\Ef{a}			&\Qf{χʼe}\Rf{ː}.\Mf{q}\Ef{a}\If{a}		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Rf{u}-\Mf{q}-	&—		&\Qf{tʃi}-\Rf{u}-\Mf{q}-	&\Qf{tʃi}\Rf{ː}\Mf{χ}.\Df{t}\Ff{s}\If{i}			&\Qf{tʃi}\Rf{ː}\Mf{χ}.\Df{t}\If{i}			&\Qf{tʃi}\Rf{ː}\Mf{χ}.\Ff{s}\If{i}			&\Qf{tʃi}\Rf{ː}\Mf{χ}.\Df{t}\Ef{a}			&\Qf{tʃi}\Rf{ː}.\Mf{q}\Ef{a}\df{\Ff{s}}			&\Qf{tʃi}\Rf{ː}\Mf{χ}.\Ff{s}\Ef{a}			&\Qf{tʃi}\Rf{ː}.\Mf{q}\Ef{a}\If{a}		&\Qf{tʃi}\Rf{ː}.\Mf{q}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Rf{u}-\Mf{q}-	&—		&\Qf{tʰu}-\Rf{u}-\Mf{q}-	&\Qf{tʰu}\Rf{ː}\Mf{χ}\rf{\Qf{ʷ}}.\Df{t}\Ff{s}\If{i}		&\Qf{tʰu}\Rf{ː}\Mf{χ}\rf{\Qf{ʷ}}.\Df{t}\If{i}		&\Qf{tʰu}\Rf{ː}\Mf{χ}\rf{\Qf{ʷ}}.\Ff{s}\If{i}		&\Qf{tʰu}\Rf{ː}\Mf{χ}\rf{\Qf{ʷ}}.\Df{t}\Ef{a}		&\Qf{tʰu}\Rf{ː}.\Mf{q}\Ef{a}\df{\Ff{s}}			&\Qf{tʰu}\Rf{ː}\Mf{χ}\rf{\Qf{ʷ}}.\Ff{s}\Ef{a}		&\Qf{tʰu}\Rf{ː}.\Mf{q}\Ef{a}\If{a}		&\Qf{tʰu}\Rf{ː}.\Mf{q}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis /{u-}/ and modal /{q-}/, unmarked subject (third person or no subject), IPA}
\end{table}

\clearpage
%% Zero, Irrealis, Modal, 1SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}					&\Df{d}-\If{i}\rlap{-}					&\Ff{s}-\If{i}\rlap{-}					&\Df{d}-						&\Df{d}-\Ff{s}\rlap{-}					&\Ff{s}-						&\If{i}-					&—\\
\midrule
—			&\Rf{u}-\Mf{g̱}-	&\Sf{x̱}-	&\Rf{u}-\Mf{g̱}-\Sf{x̱}-		&\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ff{z}\If{i}			&\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\If{i}			&\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\If{i}			&\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}			&\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}			&\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}			&\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\If{a}			&\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
\Qf{a}- expletive	&\Rf{u}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{a}-\Rf{u}-\Mf{g̱}-\Sf{x̱}-	&\Qf{o}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?		&\Qf{o}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}		&\Qf{o}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\Qf{o}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}\?		&\Qf{o}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}\?		&\Qf{o}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}\?		&\Qf{o}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\If{a}		&\Qf{o}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\\
\Qf{ka}- qualifier	&\Rf{u}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{ka}-\Rf{u}-\Mf{g̱}-\Sf{x̱}-	&\Qf{ko}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}		&\Qf{ko}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}		&\Qf{ko}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}		&\Qf{ko}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}		&\Qf{ko}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}		&\Qf{ko}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}		&\Qf{ko}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\If{a}		&\Qf{ko}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{u}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{x̱ʼe}-\Rf{u}-\Mf{g̱}-\Sf{x̱}-	&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?		&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}\?		&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}\?		&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}\?		&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}\?		&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Ef{a}\If{a}		&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Ef{a}\?\\
			&		&		&				&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\If{i}\?	&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\If{i}\?	&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}\?	&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}\?	&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}\?	&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\If{a}	&\Qf{x̱ʼe}\Rf{i}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
			&		&		&				&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ff{z}\If{i}\?		&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\If{i}\?		&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\If{i}\?		&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}		&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}\?		&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}\?		&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\If{a}		&\Qf{x̱ʼa}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Rf{u}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{ji}-\Rf{u}-\Mf{g̱}-\Sf{x̱}-	&\Qf{je}\Rf{e}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?		&\Qf{je}\Rf{e}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}\?		&\Qf{je}\Rf{e}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\Qf{je}\Rf{e}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}		&\Qf{je}\Rf{e}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}		&\Qf{je}\Rf{e}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}		&\Qf{je}\Rf{e}\mf{\Sf{ḵ}}\Ef{a}			&\Qf{je}\Rf{e}\mf{\Sf{ḵ}}\Ef{a}\\
			&		&		&				&\Qf{ji}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ff{z}\If{i}\?		&\Qf{ji}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\If{i}\?		&\Qf{ji}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\If{i}		&\Qf{ji}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}\?		&\Qf{ji}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}\?		&\Qf{ji}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}\?		&\Qf{ji}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\?		&\Qf{ji}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\?\\
\Qf{tu}- ‘inside’	&\Rf{u}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{tu}-\Rf{u}-\Mf{g̱}-\Sf{x̱}-	&\Qf{to}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?		&\Qf{to}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}		&\Qf{to}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\Qf{to}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}		&\Qf{to}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}\?		&\Qf{to}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}\?		&\Qf{to}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\If{a}\?		&\Qf{to}\Rf{o}\mf{\Sf{ḵ}}\Ef{a}\?\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis \textit{u-} and modal \textit{g̱-}, first person singular subject \textit{x̱-}}
\end{table}

%% Zero, Irrealis, Modal, 1SG, IPA
\begin{table}
\centerfloat
\setlength{\tabcolsep}{0.875ex}
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}						&\Df{t}-\If{i}\rlap{-}						&\Ff{s}-\If{i}\rlap{-}						&\Df{t}-							&\Df{t}-\Ff{s}\rlap{-}						&\Ff{s}-							&\If{i}-						&—\\
\midrule
—			&\Rf{u}-\Mf{q}-	&\Sf{χ}-	&\Rf{u}-\Mf{q}-\Sf{χ}-		&\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ff{s}\If{i}				&\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\If{i}				&\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Ff{s}\If{i}				&\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}				&\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}				&\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Ff{s}\Ef{a}				&\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\If{a}				&\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
\Qf{ʔa}- expletive	&\Rf{u}-\Mf{q}-	&\Sf{χ}-	&\Qf{ʔa}-\Rf{u}-\Mf{q}-\Sf{χ}-	&\Qf{ʔu}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?			&\Qf{ʔu}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}			&\Qf{ʔu}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?		&\Qf{ʔu}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}\?		&\Qf{ʔu}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}\?			&\Qf{ʔu}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}\?		&\Qf{ʔu}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\If{a}			&\Qf{ʔu}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Rf{u}-\Mf{q}-	&\Sf{χ}-	&\Qf{kʰa}-\Rf{u}-\Mf{q}-\Sf{χ}-	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\If{a}	&\Qf{kʰ}\Rf{ʷ}\Qf{u}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Rf{u}-\Mf{q}-	&\Sf{χ}-	&\Qf{χʼe}-\Rf{u}-\Mf{q}-\Sf{χ}-	&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?			&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}\?			&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\If{a}		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\?\\
			&		&		&				&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\If{i}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Ff{s}\If{i}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Ff{s}\Ef{a}\?		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\If{a}		&\Qf{χʼe}\Rf{ː}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
			&		&		&				&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?			&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\If{i}\?		&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Ff{s}\If{i}\?		&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}			&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}\?			&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Ff{s}\Ef{a}\?		&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\If{a}		&\Qf{χʼa}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Rf{u}-\Mf{q}-	&\Sf{χ}-	&\Qf{tʃi}-\Rf{u}-\Mf{q}-\Sf{χ}-	&\Qf{tʃi}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?			&\Qf{tʃi}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}\?		&\Qf{tʃi}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?		&\Qf{tʃi}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}			&\Qf{tʃi}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}			&\Qf{tʃi}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}			&\Qf{tʃi}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}			&\Qf{tʃi}\Rf{ː}.\Mf{q}\Sf{ʰ}\Ef{a}\\
			&		&		&				&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?			&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\If{i}\?		&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Ff{s}\If{i}			&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}\?		&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}\?			&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Ff{s}\Ef{a}\?		&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\?			&\Qf{tʃi}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\?\\
\bottomrule
\end{tabular}
\caption{Unmarked aspect with irrealis /{u-}/ and modal /{q-}/, first person singular subject /{χ-}/, IPA}
\end{table}

%%%
%%% N-conjugation
%%%
\clearpage
\section{\textit{N}-conjugation prefix \textit{n-}}\label{sec:nconj}

\begin{multicols}{2}
\noindent
The \fm{n-} conjugation prefix is the marker of membership in the \fm{n}-conjugation class.
As such, forms with \fm{n-} occur for any \fm{n}-conjugation verb when a conjugation prefix is selected.
The \fm{n-} conjugation prefix also has a dedicated use in progressive aspect forms, similar to how the \fm{g-} conjugation prefix is used for prospective aspect.
\end{multicols}

\clearpage
%% N-conjugation, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Af{n}-	&—		&\Af{n}-		&\Af{n}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Af{n}\Ef{a}\Df{d}\If{i}	&\Af{n}\Ef{a}\Ff{s}\If{i}		&\Af{n}\Ef{a}\Df{d}\Ef{a}	&\Af{n}\Ef{a}\df{\Ff{s}}		&\Af{n}\Ef{a}\Ff{s}		&\Af{n}\Ef{a}\If{a}		&\Af{n}\Ef{a}\\
\Qf{a}- arg./expl.	&\Af{n}-	&—		&\Qf{a}-\Af{n}-		&\Qf{a}\Af{n}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{n}\Df{d}\If{i}\?	&\Qf{a}\Af{n}\Ef{a}\Ff{s}\If{i}\?	&\Qf{a}\Af{n}\Df{d}\Ef{a}	&\Qf{a}\Af{n}\Ef{a}\df{\Ff{s}}		&\Qf{a}\Af{n}\Ef{a}\Ff{s}	&\Qf{a}\Af{n}\Ef{a}\If{a}	&\Qf{a}\Af{n}\Ef{a}\\
\Qf{ka}- qualifier	&\Af{n}-	&—		&\Qf{ka}-\Af{n}-	&\Qf{ka}\Af{n}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{n}\Df{d}\If{i}	&\Qf{ka}\Af{n}\Ef{a}\Ff{s}\If{i}\?	&\Qf{ka}\Af{n}\Df{d}\Ef{a}	&\Qf{ka}\Af{n}\Ef{a}\df{\Ff{s}}		&\Qf{ka}\Af{n}\Ef{a}\Ff{s}	&\Qf{ka}\Af{n}\Ef{a}\If{a}	&\Qf{ka}\Af{n}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{n}-	&—		&\Qf{x̱ʼe}-\Af{n}-	&\Qf{x̱ʼa}\Af{n}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Ff{s}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\If{a}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Af{n}-	&—		&\Qf{ji}-\Af{n}-	&\Qf{ji}\Af{n}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{n}\Df{d}\If{i}\?	&\Qf{ji}\Af{n}\Ef{a}\Ff{s}\If{i}\?	&\Qf{ji}\Af{n}\Df{d}\Ef{a}	&\Qf{ji}\Af{n}\Ef{a}\df{\Ff{s}}		&\Qf{ji}\Af{n}\Ef{a}\Ff{s}	&\Qf{ji}\Af{n}\Ef{a}\If{a}	&\Qf{ji}\Af{n}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Af{n}-	&—		&\Qf{tu}-\Af{n}-	&\Qf{tu}\Af{n}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{n}\Df{d}\If{i}\?	&\Qf{tu}\Af{n}\Ef{a}\Ff{s}\If{i}	&\Qf{tu}\Af{n}\Df{d}\Ef{a}	&\Qf{tu}\Af{n}\Ef{a}\df{\Ff{s}}		&\Qf{tu}\Af{n}\Ef{a}\Ff{s}	&\Qf{tu}\Af{n}\Ef{a}\If{a}	&\Qf{tu}\Af{n}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation \textit{n-}, unmarked subject (third person or no subject)}
\end{table}

%% N-conjugation, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-			&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Af{n}-	&—		&\Af{n}-		&\Af{n}\Ef{a}.\Df{t}\Ff{s}\If{i}\?	&\Af{n}\Ef{a}.\Df{t}\If{i}	&\Af{n}\Ef{a}.\Ff{s}\If{i}		&\Af{n}\Ef{a}.\Df{t}\Ef{a}	&\Af{n}\Ef{a}\df{\Ff{s}}		&\Af{n}\Ef{a}\Ff{s}		&\Af{n}\Ef{a}\If{ː}		&\Af{n}\Ef{a}\\
\Qf{ʔa}- arg./expl.	&\Af{n}-	&—		&\Qf{ʔa}-\Af{n}-	&\Qf{ʔa}\Af{n}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}\Af{n}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{n}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{ʔa}\Af{n}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{n}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}.\Af{n}\Ef{a}\Ff{s}	&\Qf{ʔa}.\Af{n}\Ef{a}\If{ː}	&\Qf{ʔa}.\Af{n}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Af{n}-	&—		&\Qf{kʰa}-\Af{n}-	&\Qf{kʰa}\Af{n}.\Df{t}\Ff{s}\If{i}\?	&\Qf{kʰa}\Af{n}.\Df{t}\If{i}	&\Qf{kʰa}.\Af{n}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{kʰa}\Af{n}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{n}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}.\Af{n}\Ef{a}\Ff{s}	&\Qf{kʰa}.\Af{n}\Ef{a}\If{ː}	&\Qf{kʰa}.\Af{n}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Af{n}-	&—		&\Qf{χʼe}-\Af{n}-	&\Qf{χʼa}\Af{n}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}\Af{n}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{n}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{χʼa}\Af{n}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{n}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}.\Af{n}\Ef{a}\Ff{s}	&\Qf{χʼa}.\Af{n}\Ef{a}\If{ː}	&\Qf{χʼa}.\Af{n}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Af{n}-	&—		&\Qf{tʃi}-\Af{n}-	&\Qf{tʃi}\Af{n}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʃi}\Af{n}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{n}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{tʃi}\Af{n}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{n}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}.\Af{n}\Ef{a}\Ff{s}	&\Qf{tʃi}.\Af{n}\Ef{a}\If{ː}	&\Qf{tʃi}.\Af{n}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Af{n}-	&—		&\Qf{tʰu}-\Af{n}-	&\Qf{tʰu}\Af{n}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{n}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{n}\Ef{a}.\Ff{s}\If{i}	&\Qf{tʰu}\Af{n}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{n}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}.\Af{n}\Ef{a}\Ff{s}	&\Qf{tʰu}.\Af{n}\Ef{a}\If{ː}	&\Qf{tʰu}.\Af{n}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation /{n-}/, unmarked subject (third person or no subject), IPA}
\end{table}

\clearpage
%% N-conjugation, 1SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}				&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{x̱}-	&\Af{n}-\Sf{x̱}-			&\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?		&\Af{n}\Ef{a}\Sf{x̱}\Df{d}\If{i}			&\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\If{i}			&\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}		&\Af{n}\Ef{a}\Sf{x̱}\Ef{a}\df{\Ff{s}}		&\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}		&\Af{n}\Ef{a}\Sf{x̱}\Ef{a}\If{a}		&\Af{n}\Ef{a}\Sf{x̱}\Ef{a}\\
\Qf{a}- expletive	&\Af{n}-	&\Sf{x̱}-	&\Qf{a}-\Af{n}-\Sf{x̱}-		&\Qf{a}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?		&\Qf{a}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?		&\Qf{a}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{a}\Af{n}\Ef{a}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{a}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{a}\Af{n}\Sf{x̱}\Ef{a}\If{a}		&\Qf{a}\Af{n}\Sf{x̱}\Ef{a}\\
\Qf{ka}- qualifier	&\Af{n}-	&\Sf{x̱}-	&\Qf{ka}-\Af{n}-\Sf{x̱}-		&\Qf{ka}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\If{i}		&\Qf{ka}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{ka}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{ka}\Af{n}\Ef{a}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{ka}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{ka}\Af{n}\Sf{x̱}\Ef{a}\If{a}	&\Qf{ka}\Af{n}\Sf{x̱}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{n}-	&\Sf{x̱}-	&\Qf{x̱ʼe}-\Af{n}-\Sf{x̱}-	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Sf{x̱}\Ef{a}\If{a}	&\Qf{x̱ʼa}\Af{n}\Sf{x̱}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Af{n}-	&\Sf{x̱}-	&\Qf{ji}-\Af{n}-\Sf{x̱}-		&\Qf{ji}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{ji}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{ji}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{ji}\Af{n}\Ef{a}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{ji}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{ji}\Af{n}\Sf{x̱}\Ef{a}\If{a}	&\Qf{ji}\Af{n}\Sf{x̱}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Af{n}-	&\Sf{x̱}-	&\Qf{tu}-\Af{n}-\Sf{x̱}-		&\Qf{tu}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{tu}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\If{i}		&\Qf{tu}\Af{n}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{tu}\Af{n}\Ef{a}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{tu}\Af{n}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{tu}\Af{n}\Sf{x̱}\Ef{a}\If{a}	&\Qf{tu}\Af{n}\Sf{x̱}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation \textit{n-}, first person singular subject \textit{x̱-}}
\end{table}

%% N-conjugation, 1SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{χ}-	&\Af{n}-\Sf{χ}-			&\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?		&\Af{n}\Ef{a}\Sf{χ}.\Df{t}\If{i}		&\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\If{i}		&\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}		&\Af{n}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}		&\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}		&\Af{n}\Ef{a}.\Sf{χ}\Ef{a}\If{ː}	&\Af{n}\Ef{a}.\Sf{χ}\Ef{a}\\
\Qf{ʔa}- expletive	&\Af{n}-	&\Sf{χ}-	&\Qf{ʔa}-\Af{n}-\Sf{χ}-		&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{n}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{ʔa}\Af{n}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{ʔa}\Af{n}.\Sf{χ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Af{n}-	&\Sf{χ}-	&\Qf{kʰa}-\Af{n}-\Sf{χ}-	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\If{i}	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{n}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{kʰa}\Af{n}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{kʰa}\Af{n}.\Sf{χ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Af{n}-	&\Sf{χ}-	&\Qf{χʼe}-\Af{n}-\Sf{χ}-	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{n}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{χʼa}\Af{n}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{χʼa}\Af{n}.\Sf{χ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Af{n}-	&\Sf{χ}-	&\Qf{tʃi}-\Af{n}-\Sf{χ}-	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{n}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{tʃi}\Af{n}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{tʃi}\Af{n}.\Sf{χ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Af{n}-	&\Sf{χ}-	&\Qf{tʰu}-\Af{n}-\Sf{χ}-	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\If{i}	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{n}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{tʰu}\Af{n}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{tʰu}\Af{n}.\Sf{χ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation /{n-}/, first person singular subject /{χ-}/, IPA}
\end{table}

\clearpage
%% N-conjugation, 1PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{tu}-	&\Af{n}-\Sf{tu}-		&\Af{n}\Ef{a}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Af{n}\Ef{a}\Sf{tu}\Df{d}\If{i}	&\Af{n}\Ef{a}\Sf{tu}\Ff{s}\If{i}	&\Af{n}\Ef{a}\Sf{tu}\Df{d}\Ef{a}	&\Af{n}\Ef{a}\Sf{too}\df{\Ff{s}}	&\Af{n}\Ef{a}\Sf{tu}\Ff{s}\Ef{a}	&\Af{n}\Ef{a}\Sf{tu}\If{w}\Ef{a}	&\Af{n}\Ef{a}\Sf{too}\\
\Qf{a}- expletive	&\Af{n}-	&\Sf{tu}-	&\Qf{a}-\Af{n}-\Sf{tu}-		&\Qf{a}\Af{n}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{n}\Sf{tu}\Df{d}\If{i}\?	&\Qf{a}\Af{n}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{a}\Af{n}\Sf{tu}\Df{d}\Ef{a}	&\Qf{a}\Af{n}\Sf{too}\df{\Ff{s}}	&\Qf{a}\Af{n}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{a}\Af{n}\Sf{tu}\If{w}\Ef{a}	&\Qf{a}\Af{n}\Sf{too}\\
\Qf{ka}- qualifier	&\Af{n}-	&\Sf{tu}-	&\Qf{ka}-\Af{n}-\Sf{tu}-	&\Qf{ka}\Af{n}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{n}\Sf{tu}\Df{d}\If{i}	&\Qf{ka}\Af{n}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{ka}\Af{n}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ka}\Af{n}\Sf{too}\df{\Ff{s}}	&\Qf{ka}\Af{n}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ka}\Af{n}\Sf{tu}\If{w}\Ef{a}	&\Qf{ka}\Af{n}\Sf{too}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{n}-	&\Sf{tu}-	&\Qf{x̱ʼe}-\Af{n}-\Sf{tu}-	&\Qf{x̱ʼa}\Af{n}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Sf{tu}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Sf{tu}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Sf{too}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{n}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Sf{tu}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Sf{too}\\
\Qf{ji}- ‘hand’		&\Af{n}-	&\Sf{tu}-	&\Qf{ji}-\Af{n}-\Sf{tu}-	&\Qf{ji}\Af{n}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{n}\Sf{tu}\Df{d}\If{i}\?	&\Qf{ji}\Af{n}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{ji}\Af{n}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ji}\Af{n}\Sf{too}\df{\Ff{s}}	&\Qf{ji}\Af{n}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ji}\Af{n}\Sf{tu}\If{w}\Ef{a}	&\Qf{ji}\Af{n}\Sf{too}\\
\Qf{tu}- ‘inside’	&\Af{n}-	&\Sf{tu}-	&\Qf{tu}-\Af{n}-\Sf{tu}-	&\Qf{tu}\Af{n}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{n}\Sf{tu}\Df{d}\If{i}\?	&\Qf{tu}\Af{n}\Sf{tu}\Ff{s}\If{i}	&\Qf{tu}\Af{n}\Sf{tu}\Df{d}\Ef{a}	&\Qf{tu}\Af{n}\Sf{too}\df{\Ff{s}}	&\Qf{tu}\Af{n}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{tu}\Af{n}\Sf{tu}\If{w}\Ef{a}	&\Qf{tu}\Af{n}\Sf{too}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation \textit{n-}, first person plural subject \textit{tu-}}
\end{table}

%% N-conjugation, 1PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{tʰu}-	&\Af{n}-\Sf{tʰu}-		&\Af{n}\Ef{a}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Af{n}\Ef{a}.\Sf{tʰu}.\Df{t}\If{i}	&\Af{n}\Ef{a}.\Sf{tʰu}.\Ff{s}\If{i}	&\Af{n}\Ef{a}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Af{n}\Ef{a}.\Sf{tʰuː}\df{\Ff{s}}	&\Af{n}\Ef{a}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Af{n}\Ef{a}.\Sf{tʰu}.\If{w}\Ef{a}	&\Af{n}\Ef{a}.\Sf{tʰuː}\\
\Qf{ʔa}- expletive	&\Af{n}-	&\Sf{tʰu}-	&\Qf{ʔa}-\Af{n}-\Sf{tʰu}-	&\Qf{ʔa}\Af{n}\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}\Af{n}.\Sf{tʰu}.\Df{t}\If{i}\?	&\Qf{ʔa}\Af{n}.\Sf{tʰu}.\Ff{s}\If{i}\?	&\Qf{ʔa}\Af{n}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{ʔa}\Af{n}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{ʔa}\Af{n}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{ʔa}\Af{n}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{ʔa}\Af{n}.\Sf{tʰuː}\\
\Qf{kʰa}- qualifier	&\Af{n}-	&\Sf{tʰu}-	&\Qf{kʰa}-\Af{n}-\Sf{tʰu}-	&\Qf{kʰa}\Af{n}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{kʰa}\Af{n}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{kʰa}\Af{n}.\Sf{tʰu}.\Ff{s}\If{i}\?	&\Qf{kʰa}\Af{n}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{kʰa}\Af{n}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{kʰa}\Af{n}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{kʰa}\Af{n}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{kʰa}\Af{n}.\Sf{tʰuː}\\
\Qf{χʼe}- ‘mouth’	&\Af{n}-	&\Sf{tʰu}-	&\Qf{χʼe}-\Af{n}-\Sf{tʰu}-	&\Qf{χʼa}\Af{n}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}\Af{n}.\Sf{tʰu}.\Df{t}\If{i}\?	&\Qf{χʼa}\Af{n}.\Sf{tʰu}.\Ff{s}\If{i}\?	&\Qf{χʼa}\Af{n}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{χʼa}\Af{n}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{χʼa}\Af{n}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{χʼa}\Af{n}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{χʼa}\Af{n}.\Sf{tʰuː}\\
\Qf{tʃi}- ‘hand’	&\Af{n}-	&\Sf{tʰu}-	&\Qf{tʃi}-\Af{n}-\Sf{tʰu}-	&\Qf{tʃi}\Af{n}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʃi}\Af{n}.\Sf{tʰu}.\Df{t}\If{i}\?	&\Qf{tʃi}\Af{n}.\Sf{tʰu}.\Ff{s}\If{i}\?	&\Qf{tʃi}\Af{n}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʃi}\Af{n}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʃi}\Af{n}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʃi}\Af{n}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʃi}\Af{n}.\Sf{tʰuː}\\
\Qf{tʰu}- ‘inside’	&\Af{n}-	&\Sf{tʰu}-	&\Qf{tʰu}-\Af{n}-\Sf{tʰu}-	&\Qf{tʰu}\Af{n}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{n}.\Sf{tʰu}.\Df{t}\If{i}\?	&\Qf{tʰu}\Af{n}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{tʰu}\Af{n}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}\Af{n}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʰu}\Af{n}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʰu}\Af{n}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʰu}\Af{n}.\Sf{tʰuː}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation /{n-}/, first person plural subject /{tʰu-}/, IPA}
\end{table}

\clearpage
%% N-conjugation, 2SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{i}-	&\Af{n}-\Sf{i}-			&\Af{n}\Sf{i}\Df{d}\Ff{z}\If{i}\?		&\Af{n}\Sf{i}\Df{d}\If{i}\?		&\Af{n}\Sf{i}\Ff{s}\If{i}\?		&\Af{n}\Sf{i}\Df{d}\Ef{a}		&\Af{n}\Sf{ee}\df{\Ff{s}}		&\Af{n}\Sf{i}\Ff{s}\Ef{a}		&\Af{n}\Sf{i}\If{y}\Ef{a}\?		&\Af{n}\Sf{ee}\\
\Qf{a}- expletive	&\Af{n}-	&\Sf{i}-	&\Qf{a}-\Af{n}-\Sf{i}-		&\Qf{a}\Af{n}\Sf{i}\Df{d}\Ff{z}\If{i}\?		&\Qf{a}\Af{n}\Sf{i}\Df{d}\If{i}\?	&\Qf{a}\Af{n}\Sf{i}\Ff{s}\If{i}\?	&\Qf{a}\Af{n}\Sf{i}\Df{d}\Ef{a}		&\Qf{a}\Af{n}\Sf{ee}\df{\Ff{s}}		&\Qf{a}\Af{n}\Sf{i}\Ff{s}\Ef{a}		&\Qf{a}\Af{n}\Sf{i}\If{y}\Ef{a}\?	&\Qf{a}\Af{n}\Sf{ee}\\
\Qf{ka}- qualifier	&\Af{n}-	&\Sf{i}-	&\Qf{ka}-\Af{n}-\Sf{i}-		&\Qf{ka}\Af{n}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{n}\Sf{i}\Df{d}\If{i}\?	&\Qf{ka}\Af{n}\Sf{i}\Ff{s}\If{i}\?	&\Qf{ka}\Af{n}\Sf{i}\Df{d}\Ef{a}	&\Qf{ka}\Af{n}\Sf{ee}\df{\Ff{s}}	&\Qf{ka}\Af{n}\Sf{i}\Ff{s}\Ef{a}	&\Qf{ka}\Af{n}\Sf{i}\If{y}\Ef{a}\?	&\Qf{ka}\Af{n}\Sf{ee}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{n}-	&\Sf{i}-	&\Qf{x̱ʼe}-\Af{n}-\Sf{i}-	&\Qf{x̱ʼa}\Af{n}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Sf{i}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Sf{i}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Sf{i}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Sf{ee}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{n}\Sf{i}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Sf{i}\If{y}\Ef{a}\?	&\Qf{x̱ʼa}\Af{n}\Sf{ee}\\
\Qf{ji}- ‘hand’		&\Af{n}-	&\Sf{i}-	&\Qf{ji}-\Af{n}-\Sf{i}-		&\Qf{ji}\Af{n}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{n}\Sf{i}\Df{d}\If{i}\?	&\Qf{ji}\Af{n}\Sf{i}\Ff{s}\If{i}\?	&\Qf{ji}\Af{n}\Sf{i}\Df{d}\Ef{a}	&\Qf{ji}\Af{n}\Sf{ee}\df{\Ff{s}}	&\Qf{ji}\Af{n}\Sf{i}\Ff{s}\Ef{a}	&\Qf{ji}\Af{n}\Sf{i}\If{y}\Ef{a}\?	&\Qf{ji}\Af{n}\Sf{ee}\\
\Qf{tu}- ‘inside’	&\Af{n}-	&\Sf{i}-	&\Qf{tu}-\Af{n}-\Sf{i}-		&\Qf{tu}\Af{n}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{n}\Sf{i}\Df{d}\If{i}\?	&\Qf{tu}\Af{n}\Sf{i}\Ff{s}\If{i}\?	&\Qf{tu}\Af{n}\Sf{i}\Df{d}\Ef{a}	&\Qf{tu}\Af{n}\Sf{ee}\df{\Ff{s}}	&\Qf{tu}\Af{n}\Sf{i}\Ff{s}\Ef{a}	&\Qf{tu}\Af{n}\Sf{i}\If{y}\Ef{a}\?	&\Qf{tu}\Af{n}\Sf{ee}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation \textit{n-}, second person singular subject \textit{i-}}
\end{table}

%% N-conjugation, 2SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{i}-	&\Af{n}-\Sf{i}-			&\Af{n}\Sf{i}.\Df{t}\Ff{s}\If{i}\?		&\Af{n}\Sf{i}.\Df{t}\If{i}\?		&\Af{n}\Sf{i}.\Ff{s}\If{i}\?		&\Af{n}\Sf{i}.\Df{t}\Ef{a}		&\Af{n}\Sf{iː}\df{\Ff{s}}		&\Af{n}\Sf{i}.\Ff{s}\Ef{a}		&\Af{n}\Sf{i}.\If{j}\Ef{a}\?		&\Af{n}\Sf{iː}\\
\Qf{ʔa}- expletive	&\Af{n}-	&\Sf{i}-	&\Qf{ʔa}-\Af{n}-\Sf{i}-		&\Qf{ʔa}.\Af{n}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{n}\Sf{i}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{n}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{n}\Sf{i}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{n}\Sf{iː}\df{\Ff{s}}	&\Qf{ʔa}.\Af{n}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Af{n}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{ʔa}.\Af{n}\Sf{iː}\\
\Qf{kʰa}- qualifier	&\Af{n}-	&\Sf{i}-	&\Qf{kʰa}-\Af{n}-\Sf{i}-	&\Qf{kʰa}.\Af{n}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{n}\Sf{i}.\Df{t}\If{i}\?	&\Qf{kʰa}.\Af{n}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{n}\Sf{i}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{n}\Sf{iː}\df{\Ff{s}}	&\Qf{kʰa}.\Af{n}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Af{n}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{kʰa}.\Af{n}\Sf{iː}\\
\Qf{χʼe}- ‘mouth’	&\Af{n}-	&\Sf{i}-	&\Qf{χʼe}-\Af{n}-\Sf{i}-	&\Qf{χʼa}.\Af{n}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{n}\Sf{i}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{n}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{n}\Sf{i}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{n}\Sf{iː}\df{\Ff{s}}	&\Qf{χʼa}.\Af{n}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Af{n}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{χʼa}.\Af{n}\Sf{iː}\\
\Qf{tʃi}- ‘hand’	&\Af{n}-	&\Sf{i}-	&\Qf{tʃi}-\Af{n}-\Sf{i}-	&\Qf{tʃi}.\Af{n}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{n}\Sf{i}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{n}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{n}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{n}\Sf{iː}\df{\Ff{s}}	&\Qf{tʃi}.\Af{n}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Af{n}\Sf{i}.\If{j}Ef{a}\?	&\Qf{tʃi}.\Af{n}\Sf{iː}\\
\Qf{tʰu}- ‘inside’	&\Af{n}-	&\Sf{i}-	&\Qf{tʰu}-\Af{n}-\Sf{i}-	&\Qf{tʰu}.\Af{n}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{n}\Sf{i}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{n}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{n}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{n}\Sf{iː}\df{\Ff{s}}	&\Qf{tʰu}.\Af{n}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{n}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{tʰu}.\Af{n}\Sf{iː}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation /{n-}/, second person singular subject /{i-}/, IPA}
\end{table}

\clearpage
%% N-conjugation, 2PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}				&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}				&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{yi}-	&\Af{n}-\Sf{yi}-		&\Af{n}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?		&\Af{n}\Ef{a}\Sf{y}\Df{d}\If{i}\?		&\Af{n}\Ef{a}\Sf{y}\Ff{s}\If{i}\?		&\Af{n}\Ef{a}\Sf{y}\Df{d}\Ef{a}		&\Af{n}\Ef{a}\Sf{yi}\df{\Ff{s}}		&\Af{n}\Ef{a}\Sf{y}\Ff{s}\Ef{a}		&\Af{n}\Ef{a}\Sf{yee}\If{y}\?		&\Af{n}\Ef{a}\Sf{y}\\
\Qf{a}- expletive	&\Af{n}-	&\Sf{yi}-	&\Qf{a}-\Af{n}-\Sf{yi}-		&\Qf{a}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{n}\Ef{a}\Sf{y}\Df{d}\If{i}\?		&\Qf{a}\Af{n}\Ef{a}\Sf{y}\Ff{s}\If{i}\?		&\Qf{a}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{a}\Af{n}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{a}\Af{n}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{a}\Af{n}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{a}\Af{n}\Ef{a}\Sf{y}\\
\Qf{ka}- qualifier	&\Af{n}-	&\Sf{yi}-	&\Qf{ka}-\Af{n}-\Sf{yi}-	&\Qf{ka}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{n}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Qf{ka}\Af{n}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Qf{ka}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{ka}\Af{n}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{ka}\Af{n}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{ka}\Af{n}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{ka}\Af{n}\Ef{a}\Sf{y}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{n}-	&\Sf{yi}-	&\Qf{x̱ʼe}-\Af{n}-\Sf{yi}-	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{x̱ʼa}\Af{n}\Ef{a}\Sf{y}\\
\Qf{ji}- ‘hand’		&\Af{n}-	&\Sf{yi}-	&\Qf{ji}-\Af{n}-\Sf{yi}-	&\Qf{ji}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{n}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Qf{ji}\Af{n}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Qf{ji}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{ji}\Af{n}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{ji}\Af{n}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{ji}\Af{n}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{ji}\Af{n}\Ef{a}\Sf{y}\\
\Qf{tu}- ‘inside’	&\Af{n}-	&\Sf{yi}-	&\Qf{tu}-\Af{n}-\Sf{yi}-	&\Qf{tu}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{n}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Qf{tu}\Af{n}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Qf{tu}\Af{n}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{tu}\Af{n}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{tu}\Af{n}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{tu}\Af{n}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{tu}\Af{n}\Ef{a}\Sf{y}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation \textit{n-}, second person plural subject \textit{yi-}}
\end{table}

%% N-conjugation, 2PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{ji}-	&\Af{n}-\Sf{ji}-		&\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?		&\Af{n}\Ef{a}\Sf{j}.\Df{t}\If{i}\?		&\Af{n}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?		&\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ef{a}		&\Af{n}\Ef{a}.\Sf{ji}\df{\Ff{s}}		&\Af{n}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}		&\Af{n}\Ef{a}.\Sf{jiː}\If{j}\?		&\Af{n}\Ef{a}\Sf{j}\\
\Qf{ʔa}- expletive	&\Af{n}-	&\Sf{ji}-	&\Qf{ʔa}-\Af{n}-\Sf{ji}-	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{n}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Af{n}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{ʔa}.\Af{n}\Ef{a}\Sf{j}\\
\Qf{kʰa}- qualifier	&\Af{n}-	&\Sf{ji}-	&\Qf{kʰa}-\Af{n}-\Sf{ji}-	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{n}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Af{n}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{kʰa}.\Af{n}\Ef{a}\Sf{j}\\
\Qf{χʼe}- ‘mouth’	&\Af{n}-	&\Sf{ji}-	&\Qf{χʼe}-\Af{n}-\Sf{ji}-	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{n}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Af{n}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{χʼa}.\Af{n}\Ef{a}\Sf{j}\\
\Qf{tʃi}- ‘hand’	&\Af{n}-	&\Sf{ji}-	&\Qf{tʃi}-\Af{n}-\Sf{ji}-	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{n}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Af{n}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{tʃi}.\Af{n}\Ef{a}\Sf{j}\\
\Qf{tʰu}- ‘inside’	&\Af{n}-	&\Sf{ji}-	&\Qf{tʰu}-\Af{n}-\Sf{ji}-	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{n}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{n}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{tʰu}.\Af{n}\Ef{a}\Sf{j}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation /{n-}/, second person plural subject /{ji-}/, IPA}
\end{table}

\clearpage
%% N-conjugation, 4H
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-	&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-	&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{du}-	&\Af{n}-\Sf{du}-		&\Af{n}\Ef{a}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Af{n}\Ef{a}\Sf{du}\df{\Ff{s}}		&⁎		&\Af{n}\Ef{a}\Sf{du}\If{w}\Ef{a}\?	&\Af{n}\Ef{a}\Sf{du}\\
\Qf{a}- expletive	&\Af{n}-	&\Sf{du}-	&\Qf{a}-\Af{n}-\Sf{du}-		&\Qf{a}\Af{n}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{a}\Af{n}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{a}\Af{n}\Sf{du}\If{w}\Ef{a}\?	&\Qf{a}\Af{n}\Sf{du}\\
\Qf{ka}- qualifier	&\Af{n}-	&\Sf{du}-	&\Qf{ka}-\Af{n}-\Sf{du}-	&\Qf{ka}\Af{n}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{ka}\Af{n}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ka}\Af{n}\Sf{du}\If{w}\Ef{a}\?	&\Qf{ka}\Af{n}\Sf{du}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{n}-	&\Sf{du}-	&\Qf{x̱ʼe}-\Af{n}-\Sf{du}-	&\Qf{x̱ʼa}\Af{n}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{x̱ʼa}\Af{n}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{x̱ʼa}\Af{n}\Sf{du}\If{w}\Ef{a}\?	&\Qf{x̱ʼa}\Af{n}\Sf{du}\\
\Qf{ji}- ‘hand’		&\Af{n}-	&\Sf{du}-	&\Qf{ji}-\Af{n}-\Sf{du}-	&\Qf{ji}\Af{n}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{ji}\Af{n}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ji}\Af{n}\Sf{du}\If{w}\Ef{a}\?	&\Qf{ji}\Af{n}\Sf{du}\\
\Qf{tu}- ‘inside’	&\Af{n}-	&\Sf{du}-	&\Qf{tu}-\Af{n}-\Sf{du}-	&\Qf{tu}\Af{n}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{tu}\Af{n}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{tu}\Af{n}\Sf{du}\If{w}\Ef{a}\?	&\Qf{tu}\Af{n}\Sf{du}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation \textit{n-}, fourth person (indefinite) human subject \textit{du-}}
\end{table}

%% N-conjugation, 4H, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-	&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-	&\If{i}-				&—\\
\midrule
—			&\Af{n}-	&\Sf{tu}-	&\Af{n}-\Sf{tu}-		&\Af{n}\Ef{a}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Af{n}\Ef{a}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Af{n}\Ef{a}.\Sf{tu}.\If{w}\Ef{a}\?	&\Af{n}\Ef{a}.\Sf{tu}\\
\Qf{ʔa}- expletive	&\Af{n}-	&\Sf{tu}-	&\Qf{ʔa}-\Af{n}-\Sf{tu}-	&\Qf{ʔa}\Af{n}\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{ʔa}\Af{n}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{ʔa}\Af{n}.\Sf{tu}.\If{w}\Ef{a}\?	&\Qf{ʔa}\Af{n}.\Sf{tu}\\
\Qf{kʰa}- qualifier	&\Af{n}-	&\Sf{tu}-	&\Qf{kʰa}-\Af{n}-\Sf{tu}-	&\Qf{kʰa}\Af{n}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{kʰa}\Af{n}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{kʰa}\Af{n}.\Sf{tu}.\If{w}\Ef{a}\?	&\Qf{kʰa}\Af{n}.\Sf{tu}\\
\Qf{χʼe}- ‘mouth’	&\Af{n}-	&\Sf{tu}-	&\Qf{χʼe}-\Af{n}-\Sf{tu}-	&\Qf{χʼa}\Af{n}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{χʼa}\Af{n}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{χʼa}\Af{n}.\Sf{tu}.\If{w}\Ef{a}\?	&\Qf{χʼa}\Af{n}.\Sf{tu}\\
\Qf{tʃi}- ‘hand’	&\Af{n}-	&\Sf{tu}-	&\Qf{tʃi}-\Af{n}-\Sf{tu}-	&\Qf{tʃi}\Af{n}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{tʃi}\Af{n}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{tʃi}\Af{n}.\Sf{tu}.\If{w}\Ef{a}\?	&\Qf{tʃi}\Af{n}.\Sf{tu}\\
\Qf{tʰu}- ‘inside’	&\Af{n}-	&\Sf{tu}-	&\Qf{tʰu}-\Af{n}-\Sf{tu}-	&\Qf{tʰu}\Af{n}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{tʰu}\Af{n}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{tʰu}\Af{n}.\Sf{tu}.\If{w}\Ef{a}\?	&\Qf{tʰu}\Af{n}.\Sf{tu}\\
\bottomrule
\end{tabular}
\caption{\textit{N}-conjugation /{n-}/, fourth person (indefinite) human subject /{tu-}/, IPA}
\end{table}

%%%
%%% N-conjugation with irrealis 
%%%
\clearpage
\subsection{\textit{N}-conjugation prefix \textit{n-} with irrealis \textit{u-}}\label{sec:nconj-irrealis}

%%%
%%% N-conjugation with modal
%%%
\subsection{\textit{N}-conjugation prefix \textit{n-} with modal \textit{g̱-}}\label{sec:nconj-modal}

%%%
%%% N-conjugation with irrealis and modal
%%%
\subsection{\textit{N}-conjugation prefix \textit{n-} with irrealis \textit{u-} and modal \textit{g̱-}}\label{sec:nconj-irrealis+modal}

\clearpage
%%%
%%% G̱-conjugation
%%%
\section{\textit{G̱}-conjugation prefix \textit{g̱-}}\label{sec:ghconj}

\clearpage
%% G̱-conjugation, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Af{g̱}-	&—		&\Af{g̱}-		&\Af{g̱}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Af{g̱}\Ef{a}\Df{d}\If{i}\?	&\Af{g̱}\Ef{a}\Ff{s}\If{i}	&\Af{g̱}\Ef{a}\Df{d}\Ef{a}	&\Af{g̱}\Ef{a}\df{\Ff{s}}		&\Af{g̱}\Ef{a}\Ff{s}\Ef{a}	&\Af{g̱}\Ef{a}\If{a}		&\Af{g̱}\Ef{a}\\
			&		&		&			&					&				&				&				&					&\#\Af{g̱}\Ef{a}\Ff{s}		&				&\\
\Qf{a}- arg./expl.	&\Af{g̱}-	&—		&\Qf{a}-\Af{g̱}-		&\Qf{a}\Af{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{x̱}\Df{d}\If{i}\?	&\Qf{a}\Af{x̱}\Ff{s}\If{i}\?	&\Qf{a}\Af{x̱}\Df{d}\Ef{a}	&\Qf{a}\Af{g̱}\Ef{a}\df{\Ff{s}}		&\Qf{a}\Af{x̱}\Ff{s}\Ef{a}	&\Qf{a}\Af{g̱}\Ef{a}\If{a}	&\Qf{a}\Af{g̱}\Ef{a}\\
\Qf{ka}- qualifier	&\Af{g̱}-	&—		&\Qf{ka}-\Af{g̱}-	&\Qf{ka}\Af{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{x̱}\Df{d}\If{i}\?	&\Qf{ka}\Af{x̱}\Ff{s}\If{i}\?	&\Qf{ka}\Af{x̱}\Df{d}\Ef{a}	&\Qf{ka}\Af{g̱}\Ef{a}\df{\Ff{s}}		&\Qf{ka}\Af{x̱}\Ff{s}\Ef{a}	&\Qf{ka}\Af{g̱}\Ef{a}\If{a}	&\Qf{ka}\Af{g̱}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g̱}-	&—		&\Qf{x̱ʼe}-\Af{g̱}-	&\Qf{x̱ʼa}\Af{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{g̱}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{x̱}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{g̱}\Ef{a}\If{a}	&\Qf{x̱ʼa}\Af{g̱}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Af{g̱}-	&—		&\Qf{ji}-\Af{g̱}-	&\Qf{ji}\Af{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{x̱}\Df{d}\If{i}\?	&\Qf{ji}\Af{x̱}\Ff{s}\If{i}\?	&\Qf{ji}\Af{x̱}\Df{d}\Ef{a}	&\Qf{ji}\Af{g̱}\Ef{a}\df{\Ff{s}}		&\Qf{ji}\Af{x̱}\Ff{s}\Ef{a}	&\Qf{ji}\Af{g̱}\Ef{a}\If{a}	&\Qf{ji}\Af{g̱}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Af{g̱}-	&—		&\Qf{tu}-\Af{g̱}-	&\Qf{tu}\Af{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{x̱}\Df{d}\If{i}\?	&\Qf{tu}\Af{x̱}\Ff{s}\If{i}\?	&\Qf{tu}\Af{x̱}\Df{d}\Ef{a}	&\Qf{tu}\Af{g̱}\Ef{a}\df{\Ff{s}}		&\Qf{tu}\Af{x̱}\Ff{s}\Ef{a}	&\Qf{tu}\Af{g̱}\Ef{a}\If{a}	&\Qf{tu}\Af{g̱}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation \textit{g̱-}, unmarked subject (third person or no subject)}
\end{table}

%% G̱-conjugation, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-			&—\\
\midrule
—			&\Af{q}-	&—		&\Af{q}-		&\Af{q}\Ef{a}.\Df{t}\Ff{s}\If{i}\?		&\Af{q}\Ef{a}.\Df{t}\If{i}\?		&\Af{q}\Ef{a}.\Ff{s}\If{i}		&\Af{q}\Ef{a}.\Df{t}\Ef{a}		&\Af{q}\Ef{a}\df{\Ff{s}}		&\Af{q}\Ef{a}.\Ff{s}\Ef{a}		&\Af{q}\Ef{a}\If{ː}		&\Af{q}\Ef{a}\\
			&		&		&			&						&					&					&					&					&\#\Af{q}\Ef{a}\Ff{s}			&				&\\
\Qf{ʔa}- arg./expl.	&\Af{q}-	&—		&\Qf{ʔa}-\Af{q}-	&\Qf{ʔa}\Af{χ}.\Df{t}\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Df{t}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Df{t}\Ef{a}		&\Qf{ʔa}.\Af{q}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}\Af{χ}.\Ff{s}\Ef{a}		&\Qf{ʔa}.\Af{q}\Ef{a}\If{ː}	&\Qf{ʔa}.\Af{q}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Af{q}-	&—		&\Qf{kʰa}-\Af{q}-	&\Qf{kʰa}\Af{χ}.\Df{t}\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Df{t}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Df{t}\Ef{a}		&\Qf{kʰa}.\Af{q}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}\Af{χ}.\Ff{s}\Ef{a}		&\Qf{kʰa}.\Af{q}\Ef{a}\If{ː}	&\Qf{kʰa}.\Af{q}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Af{q}-	&—		&\Qf{χʼe}-\Af{q}-	&\Qf{χʼa}\Af{χ}.\Df{t}\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Df{t}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Df{t}\Ef{a}		&\Qf{χʼa}.\Af{q}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}\Af{χ}.\Ff{s}\Ef{a}		&\Qf{χʼa}.\Af{q}\Ef{a}\If{ː}	&\Qf{χʼa}.\Af{q}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Af{q}-	&—		&\Qf{tʃi}-\Af{q}-	&\Qf{tʃi}\Af{χ}.\Df{t}\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Df{t}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Df{t}\Ef{a}		&\Qf{tʃi}.\Af{q}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}\Af{χ}.\Ff{s}\Ef{a}		&\Qf{tʃi}.\Af{q}\Ef{a}\If{ː}	&\Qf{tʃi}.\Af{q}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Af{q}-	&—		&\Qf{tʰu}-\Af{q}-	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Df{t}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{q}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{q}\Ef{a}\If{ː}	&\Qf{tʰu}.\Af{q}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation /{q-}/, unmarked subject (third person or no subject), IPA}
\end{table}

\clearpage
%% G̱-conjugation, 1SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{g̱}-	&\Sf{x̱}-	&\Af{g̱}-\Sf{x̱}-			&\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?		&\af{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}\?		&\af{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}		&\af{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}		&\af{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}		&\af{\Sf{ḵ}}\Ef{a}\If{a}		&\af{\Sf{ḵ}}\Ef{a}\\
\Qf{a}- expletive	&\Af{g̱}-	&\Sf{x̱}-	&\Qf{a}-\Af{g̱}-\Sf{x̱}-		&\Qf{a}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\af{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}\?		&\Qf{a}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\Qf{a}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{a}\af{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{a}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&\Qf{a}\af{\Sf{ḵ}}\Ef{a}\If{a}		&\Qf{a}\af{\Sf{ḵ}}\Ef{a}\\
\Qf{ka}- qualifier	&\Af{g̱}-	&\Sf{x̱}-	&\Qf{ka}-\Af{g̱}-\Sf{x̱}-		&\Qf{ka}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\af{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}\?		&\Qf{ka}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\Qf{ka}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{ka}\af{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{ka}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&\Qf{ka}\af{\Sf{ḵ}}\Ef{a}\If{a}		&\Qf{ka}\af{\Sf{ḵ}}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g̱}-	&\Sf{x̱}-	&\Qf{x̱ʼe}-\Af{g̱}-\Sf{x̱}-	&\Qf{x̱ʼa}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\af{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\af{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\af{\Sf{ḵ}}\Ef{a}\If{a}	&\Qf{x̱ʼa}\af{\Sf{ḵ}}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Af{g̱}-	&\Sf{x̱}-	&\Qf{ji}-\Af{g̱}-\Sf{x̱}-		&\Qf{ji}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\af{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}\?		&\Qf{ji}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\Qf{ji}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{ji}\af{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{ji}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&\Qf{ji}\af{\Sf{ḵ}}\Ef{a}\If{a}		&\Qf{ji}\af{\Sf{ḵ}}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Af{g̱}-	&\Sf{x̱}-	&\Qf{tu}-\Af{g̱}-\Sf{x̱}-		&\Qf{tu}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\af{\Sf{ḵ}}\Ef{a}\Df{d}\If{i}\?		&\Qf{tu}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\If{i}\?		&\Qf{tu}\af{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}	&\Qf{tu}\af{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}	&\Qf{tu}\af{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}	&\Qf{tu}\af{\Sf{ḵ}}\Ef{a}\If{a}		&\Qf{tu}\af{\Sf{ḵ}}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation \textit{g̱-}, first person singular subject \textit{x̱-}}
\end{table}

%% G̱-conjugation, 1SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-					&\If{i}-				&—\\
\midrule
—			&\Af{q}-	&\Sf{χ}-	&\Af{q}-\Sf{χ}-			&\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?		&\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}\?		&\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?		&\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}		&\Af{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}		&\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}		&\Af{q}\Sf{ʰ}\Ef{a}\If{ː}		&\Af{q}\Sf{ʰ}\Ef{a}\\
\Qf{ʔa}- expletive	&\Af{q}-	&\Sf{χ}-	&\Qf{ʔa}-\Af{q}-\Sf{χ}-		&\Qf{ʔa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Af{q}\Sf{ʰ}\Ef{a}\If{ː}	&\Qf{ʔa}.\Af{q}\Sf{ʰ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Af{q}-	&\Sf{χ}-	&\Qf{kʰa}-\Af{q}-\Sf{χ}-	&\Qf{kʰa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}\?	&\Qf{kʰa}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Af{q}\Sf{ʰ}\Ef{a}\If{ː}	&\Qf{kʰa}.\Af{q}\Sf{ʰ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Af{q}-	&\Sf{χ}-	&\Qf{χʼe}-\Af{q}-\Sf{χ}-	&\Qf{χʼa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Af{q}\Sf{ʰ}\Ef{a}\If{ː}	&\Qf{χʼa}.\Af{q}\Sf{ʰ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Af{q}-	&\Sf{χ}-	&\Qf{tʃi}-\Af{q}-\Sf{χ}-	&\Qf{tʃi}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Af{q}\Sf{ʰ}\Ef{a}\If{ː}	&\Qf{tʃi}.\Af{q}\Sf{ʰ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Af{q}-	&\Sf{χ}-	&\Qf{tʰu}-\Af{q}-\Sf{χ}-	&\Qf{tʰu}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}.\Af{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{q}\Sf{ʰ}\Ef{a}\If{ː}	&\Qf{tʰu}.\Af{q}\Sf{ʰ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation /{q-}/, first person singular subject /{χ-}/, IPA}
\end{table}

\clearpage
%% G̱-conjugation, 1PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{g̱}-	&\Sf{tu}-	&\Af{g̱}-\Sf{tu}-		&\Af{g̱}\Ef{a}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Af{g̱}\Ef{a}\Sf{tu}\Df{d}\If{i}\?	&\Af{g̱}\Ef{a}\Sf{tu}\Ff{s}\If{i}\?	&\Af{g̱}\Ef{a}\Sf{tu}\Df{d}\Ef{a}	&\Af{g̱}\Ef{a}\Sf{too}\df{\Ff{s}}	&\Af{g̱}\Ef{a}\Sf{tu}\Ff{s}\Ef{a}	&\Af{g̱}\Ef{a}\Sf{tu}\If{w}\Ef{a}	&\Af{g̱}\Ef{a}\Sf{too}\\
\Qf{a}- expletive	&\Af{g̱}-	&\Sf{tu}-	&\Qf{a}-\Af{g̱}-\Sf{tu}-		&\Qf{a}\Af{x̱}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{x̱}\Sf{tu}\Df{d}\If{i}\?	&\Qf{a}\Af{x̱}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{a}\Af{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{a}\Af{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{a}\Af{x̱}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{a}\Af{x̱}\Sf{tu}\If{w}\Ef{a}	&\Qf{a}\Af{x̱}\Sf{too}\\
\Qf{ka}- qualifier	&\Af{g̱}-	&\Sf{tu}-	&\Qf{ka}-\Af{g̱}-\Sf{tu}-	&\Qf{ka}\Af{x̱}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{x̱}\Sf{tu}\Df{d}\If{i}\?	&\Qf{ka}\Af{x̱}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{ka}\Af{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ka}\Af{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{ka}\Af{x̱}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ka}\Af{x̱}\Sf{tu}\If{w}\Ef{a}	&\Qf{ka}\Af{x̱}\Sf{too}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g̱}-	&\Sf{tu}-	&\Qf{x̱ʼe}-\Af{g̱}-\Sf{tu}-	&\Qf{x̱ʼa}\Af{x̱}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Sf{tu}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{x̱}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{x̱}\Sf{tu}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Af{x̱}\Sf{too}\\
\Qf{ji}- ‘hand’		&\Af{g̱}-	&\Sf{tu}-	&\Qf{ji}-\Af{g̱}-\Sf{tu}-	&\Qf{ji}\Af{x̱}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{x̱}\Sf{tu}\Df{d}\If{i}\?	&\Qf{ji}\Af{x̱}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{ji}\Af{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ji}\Af{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{ji}\Af{x̱}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ji}\Af{x̱}\Sf{tu}\If{w}\Ef{a}	&\Qf{ji}\Af{x̱}\Sf{too}\\
\Qf{tu}- ‘inside’	&\Af{g̱}-	&\Sf{tu}-	&\Qf{tu}-\Af{g̱}-\Sf{tu}-	&\Qf{tu}\Af{x̱}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{x̱}\Sf{tu}\Df{d}\If{i}\?	&\Qf{tu}\Af{x̱}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{tu}\Af{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{tu}\Af{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{tu}\Af{x̱}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{tu}\Af{x̱}\Sf{tu}\If{w}\Ef{a}	&\Qf{tu}\Af{x̱}\Sf{too}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation \textit{g̱-}, first person plural subject \textit{tu-}}
\end{table}

%% G̱-conjugation, 1PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-					&—\\
\midrule
—			&\Af{q}-	&\Sf{tʰu}-	&\Af{q}-\Sf{tʰu}-		&\Af{q}\Ef{a}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Af{q}\Ef{a}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Af{q}\Ef{a}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Af{q}\Ef{a}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Af{q}\Ef{a}.\Sf{tʰuː}\df{\Ff{s}}		&\Af{q}\Ef{a}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Af{q}\Ef{a}.\Sf{tʰu}.\If{w}\Ef{a}		&\Af{q}\Ef{a}.\Sf{tʰuː}\\
\Qf{ʔa}- expletive	&\Af{q}-	&\Sf{tʰu}-	&\Qf{ʔa}-\Af{q}-\Sf{tʰu}-	&\Qf{ʔa}\Af{χ}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{ʔa}\Af{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{ʔa}\Af{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Qf{ʔa}\Af{χ}.\Sf{tʰu}.\If{w}\Ef{a}		&\Qf{ʔa}\Af{χ}.\Sf{tʰuː}\\
\Qf{kʰa}- qualifier	&\Af{q}-	&\Sf{tʰu}-	&\Qf{kʰa}-\Af{q}-\Sf{tʰu}-	&\Qf{kʰa}\Af{χ}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{kʰa}\Af{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{kʰa}\Af{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Qf{kʰa}\Af{χ}.\Sf{tʰu}.\If{w}\Ef{a}		&\Qf{kʰa}\Af{χ}.\Sf{tʰuː}\\
\Qf{χʼe}- ‘mouth’	&\Af{q}-	&\Sf{tʰu}-	&\Qf{χʼe}-\Af{q}-\Sf{tʰu}-	&\Qf{χʼa}\Af{χ}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{χʼa}\Af{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{χʼa}\Af{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Qf{χʼa}\Af{χ}.\Sf{tʰu}.\If{w}\Ef{a}		&\Qf{χʼa}\Af{χ}.\Sf{tʰuː}\\
\Qf{tʃi}- ‘hand’	&\Af{q}-	&\Sf{tʰu}-	&\Qf{tʃi}-\Af{q}-\Sf{tʰu}-	&\Qf{tʃi}\Af{χ}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{tʃi}\Af{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{tʃi}\Af{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Qf{tʃi}\Af{χ}.\Sf{tʰu}.\If{w}\Ef{a}		&\Qf{tʃi}\Af{χ}.\Sf{tʰuː}\\
\Qf{tʰu}- ‘inside’	&\Af{q}-	&\Sf{tʰu}-	&\Qf{tʰu}-\Af{q}-\Sf{tʰu}-	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tʰu}.\Df{t}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tʰu}.\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tʰuː}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation /{q-}/, first person plural subject /{tʰu-}/, IPA}
\end{table}

\clearpage
%% G̱-conjugation, 2SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{g̱}-	&\Sf{i}-	&\Af{g̱}-\Sf{i}-			&\Af{g̱}\Sf{i}\Df{d}\Ff{z}\If{i}\?		&\Af{g̱}\Sf{i}\Df{d}\If{i}\?		&\Af{g̱}\Sf{i}\Ff{s}\If{i}\?		&\Af{g̱}\Sf{i}\Df{d}\Ef{a}		&\Af{g̱}\Sf{ee}\df{\Ff{s}}		&\Af{g̱}\Sf{i}\Ff{s}\Ef{a}		&\Af{g̱}\Sf{i}\If{y}\Ef{a}\?		&\Af{g̱}\Sf{ee}\\
\Qf{a}- expletive	&\Af{g̱}-	&\Sf{i}-	&\Qf{a}-\Af{g̱}-\Sf{i}-		&\Qf{a}\Af{g̱}\Sf{i}\Df{d}\Ff{z}\If{i}\?		&\Qf{a}\Af{g̱}\Sf{i}\Df{d}\If{i}\?	&\Qf{a}\Af{g̱}\Sf{i}\Ff{s}\If{i}\?	&\Qf{a}\Af{g̱}\Sf{i}\Df{d}\Ef{a}		&\Qf{a}\Af{g̱}\Sf{ee}\df{\Ff{s}}		&\Qf{a}\Af{g̱}\Sf{i}\Ff{s}\Ef{a}		&\Qf{a}\Af{g̱}\Sf{i}\If{y}\Ef{a}\?	&\Qf{a}\Af{g̱}\Sf{ee}\\
\Qf{ka}- qualifier	&\Af{g̱}-	&\Sf{i}-	&\Qf{ka}-\Af{g̱}-\Sf{i}-		&\Qf{ka}\Af{g̱}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{g̱}\Sf{i}\Df{d}\If{i}\?	&\Qf{ka}\Af{g̱}\Sf{i}\Ff{s}\If{i}\?	&\Qf{ka}\Af{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{ka}\Af{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{ka}\Af{g̱}\Sf{i}\Ff{s}\Ef{a}	&\Qf{ka}\Af{g̱}\Sf{i}\If{y}\Ef{a}\?	&\Qf{ka}\Af{g̱}\Sf{ee}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g̱}-	&\Sf{i}-	&\Qf{x̱ʼe}-\Af{g̱}-\Sf{i}-	&\Qf{x̱ʼa}\Af{g̱}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{g̱}\Sf{i}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{g̱}\Sf{i}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{g̱}\Sf{i}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{g̱}\Sf{i}\If{y}\Ef{a}\?	&\Qf{x̱ʼa}\Af{g̱}\Sf{ee}\\
\Qf{ji}- ‘hand’		&\Af{g̱}-	&\Sf{i}-	&\Qf{ji}-\Af{g̱}-\Sf{i}-		&\Qf{ji}\Af{g̱}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{g̱}\Sf{i}\Df{d}\If{i}\?	&\Qf{ji}\Af{g̱}\Sf{i}\Ff{s}\If{i}\?	&\Qf{ji}\Af{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{ji}\Af{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{ji}\Af{g̱}\Sf{i}\Ff{s}\Ef{a}	&\Qf{ji}\Af{g̱}\Sf{i}\If{y}\Ef{a}\?	&\Qf{ji}\Af{g̱}\Sf{ee}\\
\Qf{tu}- ‘inside’	&\Af{g̱}-	&\Sf{i}-	&\Qf{tu}-\Af{g̱}-\Sf{i}-		&\Qf{tu}\Af{g̱}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{g̱}\Sf{i}\Df{d}\If{i}\?	&\Qf{tu}\Af{g̱}\Sf{i}\Ff{s}\If{i}\?	&\Qf{tu}\Af{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{tu}\Af{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{tu}\Af{g̱}\Sf{i}\Ff{s}\Ef{a}	&\Qf{tu}\Af{g̱}\Sf{i}\If{y}\Ef{a}\?	&\Qf{tu}\Af{g̱}\Sf{ee}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation \textit{g̱-}, second person singular subject \textit{i-}}
\end{table}

%% G̱-conjugation, 2SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{q}-	&\Sf{i}-	&\Af{q}-\Sf{i}-			&\Af{q}\Sf{i}.\Df{t}\Ff{s}\If{i}\?		&\Af{q}\Sf{i}.\Df{t}\If{i}\?		&\Af{q}\Sf{i}.\Ff{s}\If{i}\?		&\Af{q}\Sf{i}.\Df{t}\Ef{a}		&\Af{q}\Sf{iː}\df{\Ff{s}}		&\Af{q}\Sf{i}.\Ff{s}\Ef{a}		&\Af{q}\Sf{i}.\If{j}\Ef{a}\?		&\Af{q}\Sf{iː}\\
\Qf{ʔa}- expletive	&\Af{q}-	&\Sf{i}-	&\Qf{ʔa}-\Af{q}-\Sf{i}-		&\Qf{ʔa}.\Af{q}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{q}\Sf{i}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{q}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{q}\Sf{iː}\df{\Ff{s}}	&\Qf{ʔa}.\Af{q}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Af{q}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{ʔa}.\Af{q}\Sf{iː}\\
\Qf{kʰa}- qualifier	&\Af{q}-	&\Sf{i}-	&\Qf{kʰa}-\Af{q}-\Sf{i}-	&\Qf{kʰa}.\Af{q}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{q}\Sf{i}.\Df{t}\If{i}\?	&\Qf{kʰa}.\Af{q}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{q}\Sf{iː}\df{\Ff{s}}	&\Qf{kʰa}.\Af{q}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Af{q}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{kʰa}.\Af{q}\Sf{iː}\\
\Qf{χʼe}- ‘mouth’	&\Af{q}-	&\Sf{i}-	&\Qf{χʼe}-\Af{q}-\Sf{i}-	&\Qf{χʼa}.\Af{q}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{q}\Sf{i}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{q}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{q}\Sf{iː}\df{\Ff{s}}	&\Qf{χʼa}.\Af{q}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Af{q}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{χʼa}.\Af{q}\Sf{iː}\\
\Qf{tʃi}- ‘hand’	&\Af{q}-	&\Sf{i}-	&\Qf{tʃi}-\Af{q}-\Sf{i}-	&\Qf{tʃi}.\Af{q}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{q}\Sf{i}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{q}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{q}\Sf{iː}\df{\Ff{s}}	&\Qf{tʃi}.\Af{q}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Af{q}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{tʃi}.\Af{q}\Sf{iː}\\
\Qf{tʰu}- ‘inside’	&\Af{q}-	&\Sf{i}-	&\Qf{tʰu}-\Af{q}-\Sf{i}-	&\Qf{tʰu}.\Af{q}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{q}\Sf{i}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{q}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{q}\Sf{iː}\df{\Ff{s}}	&\Qf{tʰu}.\Af{q}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{q}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{tʰu}.\Af{q}\Sf{iː}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation /{q-}/, second person singular subject /{i-}/, IPA}
\end{table}

\clearpage
%% G̱-conjugation, 2PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-			&—\\
\midrule
—			&\Af{g̱}-	&\Sf{yi}-	&\Af{g̱}-\Sf{yi}-		&\Af{g̱}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?		&\Af{g̱}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Af{g̱}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Af{g̱}\Ef{a}\Sf{y}\Df{d}\Ef{a}		&\Af{g̱}\Ef{a}\Sf{yi}\df{\Ff{s}}		&\Af{g̱}\Ef{a}\Sf{y}\Ff{s}\Ef{a}		&\Af{g̱}\Ef{a}\Sf{ye}\If{ey}	&\Af{g̱}\Ef{a}\Sf{yi}\\
\Qf{a}- expletive	&\Af{g̱}-	&\Sf{yi}-	&\Qf{a}-\Af{g̱}-\Sf{yi}-		&\Qf{a}\Af{x̱}\Sf{yi}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{x̱}\Sf{yi}\Df{d}\If{i}\?	&\Qf{a}\Af{x̱}\Sf{yi}\Ff{s}\If{i}\?	&\Qf{a}\Af{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{a}\Af{x̱}\Sf{yi}\df{\Ff{s}}		&\Qf{a}\Af{x̱}\Sf{yi}\Ff{s}\Ef{a}	&\Qf{a}\Af{x̱}\Sf{ye}\If{ey}	&\Qf{a}\Af{x̱}\Sf{yi}\\
\Qf{ka}- qualifier	&\Af{g̱}-	&\Sf{yi}-	&\Qf{ka}-\Af{g̱}-\Sf{yi}-	&\Qf{ka}\Af{x̱}\Sf{yi}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{x̱}\Sf{yi}\Df{d}\If{i}\?	&\Qf{ka}\Af{x̱}\Sf{yi}\Ff{s}\If{i}\?	&\Qf{ka}\Af{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{ka}\Af{x̱}\Sf{yi}\df{\Ff{s}}	&\Qf{ka}\Af{x̱}\Sf{yi}\Ff{s}\Ef{a}	&\Qf{ka}\Af{x̱}\Sf{ye}\If{ey}	&\Qf{ka}\Af{x̱}\Sf{yi}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g̱}-	&\Sf{yi}-	&\Qf{x̱ʼe}-\Af{g̱}-\Sf{yi}-	&\Qf{x̱ʼa}\Af{x̱}\Sf{yi}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Sf{yi}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Sf{yi}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{x̱}\Sf{yi}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{x̱}\Sf{yi}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{x̱}\Sf{ye}\If{ey}	&\Qf{x̱ʼa}\Af{x̱}\Sf{yi}\\
\Qf{ji}- ‘hand’		&\Af{g̱}-	&\Sf{yi}-	&\Qf{ji}-\Af{g̱}-\Sf{yi}-	&\Qf{ji}\Af{x̱}\Sf{yi}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{x̱}\Sf{yi}\Df{d}\If{i}\?	&\Qf{ji}\Af{x̱}\Sf{yi}\Ff{s}\If{i}\?	&\Qf{ji}\Af{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{ji}\Af{x̱}\Sf{yi}\df{\Ff{s}}	&\Qf{ji}\Af{x̱}\Sf{yi}\Ff{s}\Ef{a}	&\Qf{ji}\Af{x̱}\Sf{ye}\If{ey}	&\Qf{ji}\Af{x̱}\Sf{yi}\\
\Qf{tu}- ‘inside’	&\Af{g̱}-	&\Sf{yi}-	&\Qf{tu}-\Af{g̱}-\Sf{yi}-	&\Qf{tu}\Af{x̱}\Sf{yi}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{x̱}\Sf{yi}\Df{d}\If{i}\?	&\Qf{tu}\Af{x̱}\Sf{yi}\Ff{s}\If{i}\?	&\Qf{tu}\Af{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{tu}\Af{x̱}\Sf{yi}\df{\Ff{s}}	&\Qf{tu}\Af{x̱}\Sf{yi}\Ff{s}\Ef{a}	&\Qf{tu}\Af{x̱}\Sf{ye}\If{ey}	&\Qf{tu}\Af{x̱}\Sf{yi}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation \textit{g̱-}, second person plural subject \textit{yi-}}
\end{table}

%% G̱-conjugation, 2PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-				&—\\
\midrule
—			&\Af{q}-	&\Sf{ji}-	&\Af{q}-\Sf{ji}-		&\Af{q}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?		&\Af{q}\Ef{a}\Sf{j}.\Df{t}\If{i}\?		&\Af{q}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?		&\Af{q}\Ef{a}\Sf{j}.\Df{t}\Ef{a}		&\Af{q}\Ef{a}\Sf{ji}\df{\Ff{s}}			&\Af{q}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}		&\Af{q}\Ef{a}.\Sf{ji}\If{ːj}		&\Af{q}\Ef{a}.\Sf{ji}\\
\Qf{ʔa}- expletive	&\Af{q}-	&\Sf{ji}-	&\Qf{ʔa}-\Af{q}-\Sf{ji}-	&\Qf{ʔa}\Af{χ}.\Sf{ji}.\Df{t}\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Sf{ji}.\Df{t}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Sf{ji}.\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{χ}.\Sf{ji}.\Df{t}\Ef{a}		&\Qf{ʔa}\Af{χ}.\Sf{ji}\df{\Ff{s}}		&\Qf{ʔa}\Af{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&\Qf{ʔa}\Af{χ}.\Sf{ji}\If{ːj}		&\Qf{ʔa}\Af{χ}.\Sf{ji}\\
\Qf{kʰa}- qualifier	&\Af{q}-	&\Sf{ji}-	&\Qf{kʰa}-\Af{q}-\Sf{ji}-	&\Qf{kʰa}\Af{χ}.\Sf{ji}.\Df{t}\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Sf{ji}.\Df{t}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Sf{ji}.\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{χ}.\Sf{ji}.\Df{t}\Ef{a}		&\Qf{kʰa}\Af{χ}.\Sf{ji}\df{\Ff{s}}		&\Qf{kʰa}\Af{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&\Qf{kʰa}\Af{χ}.\Sf{ji}\If{ːj}		&\Qf{kʰa}\Af{χ}.\Sf{ji}\\
\Qf{χʼe}- ‘mouth’	&\Af{q}-	&\Sf{ji}-	&\Qf{χʼe}-\Af{q}-\Sf{ji}-	&\Qf{χʼa}\Af{χ}.\Sf{ji}.\Df{t}\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Sf{ji}.\Df{t}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Sf{ji}.\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{χ}.\Sf{ji}.\Df{t}\Ef{a}		&\Qf{χʼa}\Af{χ}.\Sf{ji}\df{\Ff{s}}		&\Qf{χʼa}\Af{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&\Qf{χʼa}\Af{χ}.\Sf{ji}\If{ːj}		&\Qf{χʼa}\Af{χ}.\Sf{ji}\\
\Qf{tʃi}- ‘hand’	&\Af{q}-	&\Sf{ji}-	&\Qf{tʃi}-\Af{q}-\Sf{ji}-	&\Qf{tʃi}\Af{χ}.\Sf{ji}.\Df{t}\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Sf{ji}.\Df{t}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Sf{ji}.\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{χ}.\Sf{ji}.\Df{t}\Ef{a}		&\Qf{tʃi}\Af{χ}.\Sf{ji}\df{\Ff{s}}		&\Qf{tʃi}\Af{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&\Qf{tʃi}\Af{χ}.\Sf{ji}\If{ːj}		&\Qf{tʃi}\Af{χ}.\Sf{ji}\\
\Qf{tʰu}- ‘inside’	&\Af{q}-	&\Sf{ji}-	&\Qf{tʰu}-\Af{q}-\Sf{ji}-	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{ji}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{ji}.\Df{t}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{ji}.\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{ji}.\Df{t}\Ef{a}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{ji}.\Ff{s}\Ef{a}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{ji}\If{ːj}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{ji}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation /{q-}/, second person plural subject /{ji-}/, IPA}
\end{table}

\clearpage
%% G̱-conjugation, 4H
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-	&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-	&\If{i}-				&—\\
\midrule
—			&\Af{g̱}-	&\Sf{du}-	&\Af{g̱}-\Sf{du}-		&\Af{g̱}\Ef{a}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Af{g̱}\Ef{a}\Sf{du}\df{\Ff{s}}		&⁎		&\Af{g̱}\Ef{a}\Sf{du}\If{w}\Ef{a}	&\Af{g̱}\Ef{a}\Sf{du}\\
\Qf{a}- expletive	&\Af{g̱}-	&\Sf{du}-	&\Qf{a}-\Af{g̱}-\Sf{du}-		&\Qf{a}\Af{x̱}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{a}\Af{x̱}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{a}\Af{x̱}\Sf{du}\If{w}\Ef{a}	&\Qf{a}\Af{x̱}\Sf{du}\\
\Qf{ka}- qualifier	&\Af{g̱}-	&\Sf{du}-	&\Qf{ka}-\Af{g̱}-\Sf{du}-	&\Qf{ka}\Af{x̱}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{ka}\Af{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ka}\Af{x̱}\Sf{du}\If{w}\Ef{a}	&\Qf{ka}\Af{x̱}\Sf{du}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g̱}-	&\Sf{du}-	&\Qf{x̱ʼe}-\Af{g̱}-\Sf{du}-	&\Qf{x̱ʼa}\Af{x̱}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{x̱ʼa}\Af{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{x̱ʼa}\Af{x̱}\Sf{du}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Af{x̱}\Sf{du}\\
\Qf{ji}- ‘hand’		&\Af{g̱}-	&\Sf{du}-	&\Qf{ji}-\Af{g̱}-\Sf{du}-	&\Qf{ji}\Af{x̱}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{ji}\Af{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ji}\Af{x̱}\Sf{du}\If{w}\Ef{a}	&\Qf{ji}\Af{x̱}\Sf{du}\\
\Qf{tu}- ‘inside’	&\Af{g̱}-	&\Sf{du}-	&\Qf{tu}-\Af{g̱}-\Sf{du}-	&\Qf{tu}\Af{x̱}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{tu}\Af{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{tu}\Af{x̱}\Sf{du}\If{w}\Ef{a}	&\Qf{tu}\Af{x̱}\Sf{du}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation \textit{g̱-}, fourth person (indefinite) human subject \textit{du-}}
\end{table}

%% G̱-conjugation, 4H, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-	&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-	&\If{i}-					&—\\
\midrule
—			&\Af{q}-	&\Sf{tu}-	&\Af{q}-\Sf{tu}-		&\Af{q}\Ef{a}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Af{q}\Ef{a}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Af{q}\Ef{a}.\Sf{tu}.\If{w}\Ef{a}		&\Af{q}\Ef{a}.\Sf{tu}\\
\Qf{ʔa}- expletive	&\Af{q}-	&\Sf{tu}-	&\Qf{ʔa}-\Af{q}-\Sf{tu}-	&\Qf{ʔa}\Af{χ}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{ʔa}\Af{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{ʔa}\Af{χ}.\Sf{tu}.\If{w}\Ef{a}		&\Qf{ʔa}\Af{χ}.\Sf{tu}\\
\Qf{kʰa}- qualifier	&\Af{q}-	&\Sf{tu}-	&\Qf{kʰa}-\Af{q}-\Sf{tu}-	&\Qf{kʰa}\Af{χ}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{kʰa}\Af{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{kʰa}\Af{χ}.\Sf{tu}.\If{w}\Ef{a}		&\Qf{kʰa}\Af{χ}.\Sf{tu}\\
\Qf{χʼe}- ‘mouth’	&\Af{q}-	&\Sf{tu}-	&\Qf{χʼe}-\Af{q}-\Sf{tu}-	&\Qf{χʼa}\Af{χ}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{χʼa}\Af{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{χʼa}\Af{χ}.\Sf{tu}.\If{w}\Ef{a}		&\Qf{χʼa}\Af{χ}.\Sf{tu}\\
\Qf{tʃi}- ‘hand’	&\Af{q}-	&\Sf{tu}-	&\Qf{tʃi}-\Af{q}-\Sf{tu}-	&\Qf{tʃi}\Af{χ}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{tʃi}\Af{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{tʃi}\Af{χ}.\Sf{tu}.\If{w}\Ef{a}		&\Qf{tʃi}\Af{χ}.\Sf{tu}\\
\Qf{tʰu}- ‘inside’	&\Af{q}-	&\Sf{tu}-	&\Qf{tʰu}-\Af{q}-\Sf{tu}-	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{tʰu}\Af{χ}\Qf{ʷ}.\Sf{tu}\\
\bottomrule
\end{tabular}
\caption{\textit{G̱}-conjugation /{q-}/, fourth person (indefinite) human subject /{tu-}/, IPA}
\end{table}

\clearpage
%%%
%%% G̱-conjugation with irrealis 
%%%
\subsection{\textit{G̱}-conjugation prefix \textit{g̱-} with irrealis \textit{u-}}\label{sec:ghconj-irrealis}

%%%
%%% G̱-conjugation with modal
%%%
\subsection{\textit{G̱}-conjugation prefix \textit{g̱-} with modal \textit{g̱-}}\label{sec:ghconj-modal}

%%%
%%% G̱-conjugation with irrealis and modal
%%%
\subsection{\textit{G̱}-conjugation prefix \textit{g̱-} with irrealis \textit{u-} and modal \textit{g̱-}}\label{sec:ghconj-irrealis+modal}

\clearpage
%%%
%%% G-conjugation
%%%
\section{\textit{G}-conjugation prefix \textit{g-}}\label{sec:gconj}

\clearpage
%% G-conjugation, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-			&\If{i}-			&—\\
\midrule
—			&\Af{g}-	&—		&\Af{g}-		&\Af{g}\Ef{a}\Df{d}\Ff{z}\If{i}\?	&\Af{g}\Ef{a}\Df{d}\If{i}	&\Af{g}\Ef{a}\Ff{s}\If{i}	&\Af{g}\Ef{a}\Df{d}\Ef{a}	&\Af{g}\Ef{a}\df{\Ff{s}}		&\Af{g}\Ef{a}\Ff{s}\Ef{a}	&\Af{g}\Ef{a}\If{a}		&\Af{g}\Ef{a}\\
\Qf{a}- arg./expl.	&\Af{g}-	&—		&\Qf{a}-\Af{g}-		&\Qf{a}\Af{k}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{k}\Df{d}\If{i}\?	&\Qf{a}\Af{k}\Ff{s}\If{i}\?	&\Qf{a}\Af{k}\Df{d}\Ef{a}	&\Qf{a}\Af{g}\Ef{a}\df{\Ff{s}}		&\Qf{a}\Af{k}\Ff{s}\Ef{a}	&\Qf{a}\Af{g}\Ef{a}\If{a}	&\Qf{a}\Af{g}\Ef{a}\\
			&		&		&			&\Qf{a}\Af{x}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{x}\Df{d}\If{i}\?	&				&\Qf{a}\Af{x}\Df{d}\Ef{a}\?	&					&				&				&\\
\Qf{ka}- qualifier	&\Af{g}-	&—		&\Qf{ka}-\Af{g}-	&\Qf{ka}\Af{k}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{k}\Df{d}\If{i}	&\Qf{ka}\Af{k}\Ff{s}\If{i}\?	&\Qf{ka}\Af{k}\Df{d}\Ef{a}	&\Qf{ka}\Af{g}\Ef{a}\df{\Ff{s}}		&\Qf{ka}\Af{k}\Ff{s}\Ef{a}	&\Qf{ka}\Af{g}\Ef{a}\If{a}	&\Qf{ka}\Af{g}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g}-	&—		&\Qf{x̱ʼe}-\Af{g}-	&\Qf{x̱ʼa}\Af{k}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{k}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{k}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{k}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{k}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\If{a}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Af{g}-	&—		&\Qf{ji}-\Af{g}-	&\Qf{ji}\Af{k}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{k}\Df{d}\If{i}\?	&\Qf{ji}\Af{k}\Ff{s}\If{i}\?	&\Qf{ji}\Af{k}\Df{d}\Ef{a}	&\Qf{ji}\Af{g}\Ef{a}\df{\Ff{s}}		&\Qf{ji}\Af{k}\Ff{s}\Ef{a}	&\Qf{ji}\Af{g}\Ef{a}\If{a}	&\Qf{ji}\Af{g}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Af{g}-	&—		&\Qf{tu}-\Af{g}-	&\Qf{tu}\Af{k}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{k}\Df{d}\If{i}\?	&\Qf{tu}\Af{k}\Ff{s}\If{i}	&\Qf{tu}\Af{k}\Df{d}\Ef{a}	&\Qf{tu}\Af{g}\Ef{a}\df{\Ff{s}}		&\Qf{tu}\Af{k}\Ff{s}\Ef{a}	&\Qf{tu}\Af{g}\Ef{a}\If{a}	&\Qf{tu}\Af{g}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation \textit{g-}, unmarked subject (third person or no subject)}
\end{table}

%% G-conjugation, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&			&\multicolumn{8}{c}{Classifier prefixes}\\
										\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes		&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-			&—\\
\midrule
—			&\Af{k}-	&—		&\Af{k}-		&\Af{k}\Ef{a}.\Df{t}\Ff{s}\If{i}\?		&\Af{k}\Ef{a}.\Df{t}\If{i}		&\Af{k}\Ef{a}.\Ff{s}\If{i}		&\Af{k}\Ef{a}.\Df{t}\Ef{a}		&\Af{k}\Ef{a}\df{\Ff{s}}		&\Af{k}\Ef{a}.\Ff{s}\Ef{a}		&\Af{k}\Ef{a}\If{ː}		&\Af{k}\Ef{a}\\
\Qf{ʔa}- arg./expl.	&\Af{k}-	&—		&\Qf{ʔa}-\Af{k}-	&\Qf{ʔa}\Af{k}.\Df{t}\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{k}.\Df{t}\If{i}\?		&\Qf{ʔa}.\Af{k}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{ʔa}\Af{k}.\Df{t}\Ef{a}		&\Qf{ʔa}.\Af{k}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}\Af{k}.\Ff{s}\Ef{a}		&\Qf{ʔa}.\Af{k}\Ef{a}\If{ː}	&\Qf{ʔa}.\Af{k}\Ef{a}\\
			&		&		&			&\Qf{ʔa}\Af{x}.\Df{t}\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{x}.\Df{t}\If{i}\?		&					&\Qf{ʔa}\Af{x}.\Df{t}\Ef{a}\?		&					&					&				&\\
\Qf{kʰa}- qualifier	&\Af{k}-	&—		&\Qf{kʰa}-\Af{k}-	&\Qf{kʰa}\Af{k}.\Df{t}\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{k}.\Df{t}\If{i}		&\Qf{kʰa}.\Af{k}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{kʰa}\Af{k}.\Df{t}\Ef{a}		&\Qf{kʰa}.\Af{k}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}\Af{k}.\Ff{s}\Ef{a}		&\Qf{kʰa}.\Af{k}\Ef{a}\If{ː}	&\Qf{kʰa}.\Af{k}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Af{k}-	&—		&\Qf{χʼe}-\Af{k}-	&\Qf{χʼa}\Af{k}.\Df{t}\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{k}.\Df{t}\If{i}\?		&\Qf{χʼa}.\Af{k}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{χʼa}\Af{k}.\Df{t}\Ef{a}		&\Qf{χʼa}.\Af{k}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}\Af{k}.\Ff{s}\Ef{a}		&\Qf{χʼa}.\Af{k}\Ef{a}\If{ː}	&\Qf{χʼa}.\Af{k}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Af{k}-	&—		&\Qf{tʃi}-\Af{k}-	&\Qf{tʃi}\Af{k}.\Df{t}\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{k}.\Df{t}\If{i}\?		&\Qf{tʃi}.\Af{k}\Ef{a}.\Ff{s}\If{i}\?	&\Qf{tʃi}\Af{k}.\Df{t}\Ef{a}		&\Qf{tʃi}.\Af{k}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}\Af{k}.\Ff{s}\Ef{a}		&\Qf{tʃi}.\Af{k}\Ef{a}\If{ː}	&\Qf{tʃi}.\Af{k}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Af{k}-	&—		&\Qf{tʰu}-\Af{k}-	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{k}\Ef{a}.\Ff{s}\If{i}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{k}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{k}\Ef{a}\If{ː}	&\Qf{tʰu}.\Af{k}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation /{k-}/, unmarked subject (third person or no subject), IPA}
\end{table}

\clearpage
%% G-conjugation, 1SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{g}-	&\Sf{x̱}-	&\Af{g}-\Sf{x̱}-			&\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?		&\Af{g}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?		&\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?		&\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}		&\Af{g}\Ef{a}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}		&\Af{g}\Ef{a}\Sf{x̱}\Ef{a}\If{a}		&\Af{g}\Ef{a}\Sf{x̱}\Ef{a}\\
\Qf{a}- expletive	&\Af{g}-	&\Sf{x̱}-	&\Qf{a}-\Af{g}-\Sf{x̱}-		&\Qf{a}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?		&\Qf{a}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?		&\Qf{a}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{a}\Af{k}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{a}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{a}\Af{k}\Sf{x̱}\Ef{a}\If{a}		&\Qf{a}\Af{k}\Sf{x̱}\Ef{a}\\
\Qf{ka}- qualifier	&\Af{g}-	&\Sf{x̱}-	&\Qf{ka}-\Af{g}-\Sf{x̱}-		&\Qf{ka}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{ka}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{ka}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{ka}\Af{k}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{ka}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{ka}\Af{k}\Sf{x̱}\Ef{a}\If{a}	&\Qf{ka}\Af{k}\Sf{x̱}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g}-	&\Sf{x̱}-	&\Qf{x̱ʼe}-\Af{g}-\Sf{x̱}-	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{k}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{k}\Sf{x̱}\Ef{a}\If{a}	&\Qf{x̱ʼa}\Af{k}\Sf{x̱}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Af{g}-	&\Sf{x̱}-	&\Qf{ji}-\Af{g}-\Sf{x̱}-		&\Qf{ji}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{ji}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{ji}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{ji}\Af{k}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{ji}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{ji}\Af{k}\Sf{x̱}\Ef{a}\If{a}	&\Qf{ji}\Af{k}\Sf{x̱}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Af{g}-	&\Sf{x̱}-	&\Qf{tu}-\Af{g}-\Sf{x̱}-		&\Qf{tu}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\If{i}\?	&\Qf{tu}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\If{i}\?	&\Qf{tu}\Af{g}\Ef{a}\Sf{x̱}\Df{d}\Ef{a}	&\Qf{tu}\Af{k}\Sf{x̱}\Ef{a}\df{\Ff{s}}	&\Qf{tu}\Af{g}\Ef{a}\Sf{x̱}\Ff{s}\Ef{a}	&\Qf{tu}\Af{k}\Sf{x̱}\Ef{a}\If{a}	&\Qf{tu}\Af{k}\Sf{x̱}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation \textit{g-}, first person singular subject \textit{x̱-}}
\end{table}

%% G-conjugation, 1SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-					&—\\
\midrule
—			&\Af{k}-	&\Sf{χ}-	&\Af{k}-\Sf{χ}-			&\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?		&\Af{k}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?		&\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?		&\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}		&\Af{k}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}		&\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}		&\Af{k}\Ef{a}.\Sf{χ}\Ef{a}\If{ː}		&\Af{k}\Ef{a}.\Sf{χ}\Ef{a}\\
\Qf{ʔa}- expletive	&\Af{k}-	&\Sf{χ}-	&\Qf{ʔa}-\Af{k}-\Sf{χ}-		&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{k}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{ʔa}\Af{k}.\Sf{χ}\Ef{a}\If{ː}		&\Qf{ʔa}\Af{k}.\Sf{χ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Af{k}-	&\Sf{χ}-	&\Qf{kʰa}-\Af{k}-\Sf{χ}-	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{k}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{kʰa}\Af{k}.\Sf{χ}\Ef{a}\If{ː}		&\Qf{kʰa}\Af{k}.\Sf{χ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Af{k}-	&\Sf{χ}-	&\Qf{χʼe}-\Af{k}-\Sf{χ}-	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{χʼa}\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{k}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{χʼa}\Af{k}.\Sf{χ}\Ef{a}\If{ː}		&\Qf{χʼa}\Af{k}.\Sf{χ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Af{k}-	&\Sf{χ}-	&\Qf{tʃi}-\Af{k}-\Sf{χ}-	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{k}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{tʃi}\Af{k}.\Sf{χ}\Ef{a}\If{ː}		&\Qf{tʃi}\Af{k}.\Sf{χ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Af{k}-	&\Sf{χ}-	&\Qf{tʰu}-\Af{k}-\Sf{χ}-	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ff{z}\If{i}\?	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{χ}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{k}\Ef{a}.\Sf{χ}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{χ}.\Ff{s}\Ef{a}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{χ}\Ef{a}\If{ː}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{χ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation /{k-}/, first person singular subject /{χ-}/, IPA}
\end{table}

\clearpage
%% G-conjugation, 1PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{g}-	&\Sf{tu}-	&\Af{g}-\Sf{tu}-		&\Af{g}\Ef{a}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Af{g}\Ef{a}\Sf{tu}\Df{d}\If{i}\?	&\Af{g}\Ef{a}\Sf{tu}\Ff{s}\If{i}\?	&\Af{g}\Ef{a}\Sf{tu}\Df{d}\Ef{a}	&\Af{g}\Ef{a}\Sf{too}\df{\Ff{s}}	&\Af{g}\Ef{a}\Sf{tu}\Ff{s}\Ef{a}	&\Af{g}\Ef{a}\Sf{tu}\If{w}\Ef{a}	&\Af{g}\Ef{a}\Sf{too}\\
\Qf{a}- expletive	&\Af{g}-	&\Sf{tu}-	&\Qf{a}-\Af{g}-\Sf{tu}-		&\Qf{a}\Af{k}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{k}\Sf{tu}\Df{d}\If{i}\?	&\Qf{a}\Af{k}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{a}\Af{k}\Sf{tu}\Df{d}\Ef{a}	&\Qf{a}\Af{k}\Sf{too}\df{\Ff{s}}	&\Qf{a}\Af{k}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{a}\Af{k}\Sf{tu}\If{w}\Ef{a}	&\Qf{a}\Af{k}\Sf{too}\\
\Qf{ka}- qualifier	&\Af{g}-	&\Sf{tu}-	&\Qf{ka}-\Af{g}-\Sf{tu}-	&\Qf{ka}\Af{k}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{k}\Sf{tu}\Df{d}\If{i}\?	&\Qf{ka}\Af{k}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{ka}\Af{k}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ka}\Af{k}\Sf{too}\df{\Ff{s}}	&\Qf{ka}\Af{k}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ka}\Af{k}\Sf{tu}\If{w}\Ef{a}	&\Qf{ka}\Af{k}\Sf{too}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g}-	&\Sf{tu}-	&\Qf{x̱ʼe}-\Af{g}-\Sf{tu}-	&\Qf{x̱ʼa}\Af{k}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{k}\Sf{tu}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{k}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{k}\Sf{tu}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{k}\Sf{too}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{k}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{k}\Sf{tu}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Af{k}\Sf{too}\\
\Qf{ji}- ‘hand’		&\Af{g}-	&\Sf{tu}-	&\Qf{ji}-\Af{g}-\Sf{tu}-	&\Qf{ji}\Af{k}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{k}\Sf{tu}\Df{d}\If{i}\?	&\Qf{ji}\Af{k}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{ji}\Af{k}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ji}\Af{k}\Sf{too}\df{\Ff{s}}	&\Qf{ji}\Af{k}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ji}\Af{k}\Sf{tu}\If{w}\Ef{a}	&\Qf{ji}\Af{k}\Sf{too}\\
\Qf{tu}- ‘inside’	&\Af{g}-	&\Sf{tu}-	&\Qf{tu}-\Af{g}-\Sf{tu}-	&\Qf{tu}\Af{k}\Sf{tu}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{k}\Sf{tu}\Df{d}\If{i}\?	&\Qf{tu}\Af{k}\Sf{tu}\Ff{s}\If{i}\?	&\Qf{tu}\Af{k}\Sf{tu}\Df{d}\Ef{a}	&\Qf{tu}\Af{k}\Sf{too}\df{\Ff{s}}	&\Qf{tu}\Af{k}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{tu}\Af{k}\Sf{tu}\If{w}\Ef{a}	&\Qf{tu}\Af{k}\Sf{too}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation \textit{g-}, first person plural subject \textit{tu-}}
\end{table}

%% G-conjugation, 1PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-					&—\\
\midrule
—			&\Af{k}-	&\Sf{tʰu}-	&\Af{k}-\Sf{tʰu}-		&\Af{k}\Ef{a}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Af{k}\Ef{a}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Af{k}\Ef{a}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Af{k}\Ef{a}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Af{k}\Ef{a}.\Sf{tʰuː}\df{\Ff{s}}		&\Af{k}\Ef{a}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Af{k}\Ef{a}.\Sf{tʰu}.\If{w}\Ef{a}		&\Af{k}\Ef{a}.\Sf{tʰuː}\\
\Qf{ʔa}- expletive	&\Af{k}-	&\Sf{tʰu}-	&\Qf{ʔa}-\Af{k}-\Sf{tʰu}-	&\Qf{ʔa}\Af{k}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{k}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Qf{ʔa}\Af{k}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Qf{ʔa}\Af{k}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{ʔa}\Af{k}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{ʔa}\Af{k}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Qf{ʔa}\Af{k}.\Sf{tʰu}.\If{w}\Ef{a}		&\Qf{ʔa}\Af{k}.\Sf{tʰuː}\\
\Qf{kʰa}- qualifier	&\Af{k}-	&\Sf{tʰu}-	&\Qf{kʰa}-\Af{k}-\Sf{tʰu}-	&\Qf{kʰa}\Af{k}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{k}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Qf{kʰa}\Af{k}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Qf{kʰa}\Af{k}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{kʰa}\Af{k}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{kʰa}\Af{k}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Qf{kʰa}\Af{k}.\Sf{tʰu}.\If{w}\Ef{a}		&\Qf{kʰa}\Af{k}.\Sf{tʰuː}\\
\Qf{χʼe}- ‘mouth’	&\Af{k}-	&\Sf{tʰu}-	&\Qf{χʼe}-\Af{k}-\Sf{tʰu}-	&\Qf{χʼa}\Af{k}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{k}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Qf{χʼa}\Af{k}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Qf{χʼa}\Af{k}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{χʼa}\Af{k}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{χʼa}\Af{k}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Qf{χʼa}\Af{k}.\Sf{tʰu}.\If{w}\Ef{a}		&\Qf{χʼa}\Af{k}.\Sf{tʰuː}\\
\Qf{tʃi}- ‘hand’	&\Af{k}-	&\Sf{tʰu}-	&\Qf{tʃi}-\Af{k}-\Sf{tʰu}-	&\Qf{tʃi}\Af{k}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{k}.\Sf{tʰu}.\Df{t}\If{i}\?		&\Qf{tʃi}\Af{k}.\Sf{tʰu}.\Ff{s}\If{i}\?		&\Qf{tʃi}\Af{k}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Qf{tʃi}\Af{k}.\Sf{tʰuː}\df{\Ff{s}}		&\Qf{tʃi}\Af{k}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Qf{tʃi}\Af{k}.\Sf{tʰu}.\If{w}\Ef{a}		&\Qf{tʃi}\Af{k}.\Sf{tʰuː}\\
\Qf{tʰu}- ‘inside’	&\Af{k}-	&\Sf{tʰu}-	&\Qf{tʰu}-\Af{k}-\Sf{tʰu}-	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tʰu}.\Df{t}\If{i}\?	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tʰu}.\Ff{s}\If{i}\?	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tʰuː}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation /{k-}/, first person plural subject /{tʰu-}/, IPA}
\end{table}

\clearpage
%% G-conjugation, 2SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{g}-	&\Sf{i}-	&\Af{g}-\Sf{i}-			&\Af{g}\Sf{i}\Df{d}\Ff{z}\If{i}\?		&\Af{g}\Sf{i}\Df{d}\If{i}\?		&\Af{g}\Sf{i}\Ff{s}\If{i}\?		&\Af{g}\Sf{i}\Df{d}\Ef{a}		&\Af{g}\Sf{ee}\df{\Ff{s}}		&\Af{g}\Sf{i}\Ff{s}\Ef{a}		&\Af{g}\Sf{i}\If{y}\Ef{a}\?		&\Af{g}\Sf{ee}\\
\Qf{a}- expletive	&\Af{g}-	&\Sf{i}-	&\Qf{a}-\Af{g}-\Sf{i}-		&\Qf{a}\Af{g}\Sf{i}\Df{d}\Ff{z}\If{i}\?		&\Qf{a}\Af{g}\Sf{i}\Df{d}\If{i}\?	&\Qf{a}\Af{g}\Sf{i}\Ff{s}\If{i}\?	&\Qf{a}\Af{g}\Sf{i}\Df{d}\Ef{a}		&\Qf{a}\Af{g}\Sf{ee}\df{\Ff{s}}		&\Qf{a}\Af{g}\Sf{i}\Ff{s}\Ef{a}		&\Qf{a}\Af{g}\Sf{i}\If{y}\Ef{a}\?	&\Qf{a}\Af{g}\Sf{ee}\\
\Qf{ka}- qualifier	&\Af{g}-	&\Sf{i}-	&\Qf{ka}-\Af{g}-\Sf{i}-		&\Qf{ka}\Af{g}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{g}\Sf{i}\Df{d}\If{i}\?	&\Qf{ka}\Af{g}\Sf{i}\Ff{s}\If{i}\?	&\Qf{ka}\Af{g}\Sf{i}\Df{d}\Ef{a}	&\Qf{ka}\Af{g}\Sf{ee}\df{\Ff{s}}	&\Qf{ka}\Af{g}\Sf{i}\Ff{s}\Ef{a}	&\Qf{ka}\Af{g}\Sf{i}\If{y}\Ef{a}\?	&\Qf{ka}\Af{g}\Sf{ee}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g}-	&\Sf{i}-	&\Qf{x̱ʼe}-\Af{g}-\Sf{i}-	&\Qf{x̱ʼa}\Af{g}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Sf{i}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Sf{i}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Sf{i}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{g}\Sf{ee}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{g}\Sf{i}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{g}\Sf{i}\If{y}\Ef{a}\?	&\Qf{x̱ʼa}\Af{g}\Sf{ee}\\
\Qf{ji}- ‘hand’		&\Af{g}-	&\Sf{i}-	&\Qf{ji}-\Af{g}-\Sf{i}-		&\Qf{ji}\Af{g}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{g}\Sf{i}\Df{d}\If{i}\?	&\Qf{ji}\Af{g}\Sf{i}\Ff{s}\If{i}\?	&\Qf{ji}\Af{g}\Sf{i}\Df{d}\Ef{a}	&\Qf{ji}\Af{g}\Sf{ee}\df{\Ff{s}}	&\Qf{ji}\Af{g}\Sf{i}\Ff{s}\Ef{a}	&\Qf{ji}\Af{g}\Sf{i}\If{y}\Ef{a}\?	&\Qf{ji}\Af{g}\Sf{ee}\\
\Qf{tu}- ‘inside’	&\Af{g}-	&\Sf{i}-	&\Qf{tu}-\Af{g}-\Sf{i}-		&\Qf{tu}\Af{g}\Sf{i}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{g}\Sf{i}\Df{d}\If{i}\?	&\Qf{tu}\Af{g}\Sf{i}\Ff{s}\If{i}\?	&\Qf{tu}\Af{g}\Sf{i}\Df{d}\Ef{a}	&\Qf{tu}\Af{g}\Sf{ee}\df{\Ff{s}}	&\Qf{tu}\Af{g}\Sf{i}\Ff{s}\Ef{a}	&\Qf{tu}\Af{g}\Sf{i}\If{y}\Ef{a}\?	&\Qf{tu}\Af{g}\Sf{ee}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation \textit{g-}, second person singular subject \textit{i-}}
\end{table}

%% G-conjugation, 2SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{k}-	&\Sf{i}-	&\Af{k}-\Sf{i}-			&\Af{k}\Sf{i}.\Df{t}\Ff{s}\If{i}\?		&\Af{k}\Sf{i}.\Df{t}\If{i}\?		&\Af{k}\Sf{i}.\Ff{s}\If{i}\?		&\Af{k}\Sf{i}.\Df{t}\Ef{a}		&\Af{k}\Sf{iː}\df{\Ff{s}}		&\Af{k}\Sf{i}.\Ff{s}\Ef{a}		&\Af{k}\Sf{i}.\If{j}\Ef{a}\?		&\Af{k}\Sf{iː}\\
\Qf{ʔa}- expletive	&\Af{k}-	&\Sf{i}-	&\Qf{ʔa}-\Af{k}-\Sf{i}-		&\Qf{ʔa}.\Af{k}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{k}\Sf{i}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{k}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{k}\Sf{i}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{k}\Sf{iː}\df{\Ff{s}}	&\Qf{ʔa}.\Af{k}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Af{k}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{ʔa}.\Af{k}\Sf{iː}\\
\Qf{kʰa}- qualifier	&\Af{k}-	&\Sf{i}-	&\Qf{kʰa}-\Af{k}-\Sf{i}-	&\Qf{kʰa}.\Af{k}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{k}\Sf{i}.\Df{t}\If{i}\?	&\Qf{kʰa}.\Af{k}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{k}\Sf{i}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{k}\Sf{iː}\df{\Ff{s}}	&\Qf{kʰa}.\Af{k}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Af{k}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{kʰa}.\Af{k}\Sf{iː}\\
\Qf{χʼe}- ‘mouth’	&\Af{k}-	&\Sf{i}-	&\Qf{χʼe}-\Af{k}-\Sf{i}-	&\Qf{χʼa}.\Af{k}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{k}\Sf{i}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{k}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{k}\Sf{i}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{k}\Sf{iː}\df{\Ff{s}}	&\Qf{χʼa}.\Af{k}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Af{k}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{χʼa}.\Af{k}\Sf{iː}\\
\Qf{tʃi}- ‘hand’	&\Af{k}-	&\Sf{i}-	&\Qf{tʃi}-\Af{k}-\Sf{i}-	&\Qf{tʃi}.\Af{k}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{k}\Sf{i}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{k}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{k}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{k}\Sf{iː}\df{\Ff{s}}	&\Qf{tʃi}.\Af{k}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Af{k}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{tʃi}.\Af{k}\Sf{iː}\\
\Qf{tʰu}- ‘inside’	&\Af{k}-	&\Sf{i}-	&\Qf{tʰu}-\Af{k}-\Sf{i}-	&\Qf{tʰu}.\Af{k}\Sf{i}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{k}\Sf{i}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{k}\Sf{i}.\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{k}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{k}\Sf{iː}\df{\Ff{s}}	&\Qf{tʰu}.\Af{k}\Sf{i}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{k}\Sf{i}.\If{j}\Ef{a}\?	&\Qf{tʰu}.\Af{k}\Sf{iː}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation /{k-}/, second person singular subject /{i-}/, IPA}
\end{table}

\clearpage
%% G-conjugation, 2PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{g}-	&\Sf{yi}-	&\Af{g}-\Sf{yi}-		&\Af{g}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?		&\Af{g}\Ef{a}\Sf{y}\Df{d}\If{i}\?		&\Af{g}\Ef{a}\Sf{y}\Ff{s}\If{i}\?		&\Af{g}\Ef{a}\Sf{y}\Df{d}\Ef{a}		&\Af{g}\Ef{a}\Sf{yi}\df{\Ff{s}}		&\Af{g}\Ef{a}\Sf{y}\Ff{s}\Ef{a}		&\Af{g}\Ef{a}\Sf{yee}\If{y}\?		&\Af{g}\Ef{a}\Sf{y}\\
\Qf{a}- expletive	&\Af{g}-	&\Sf{yi}-	&\Qf{a}-\Af{g}-\Sf{yi}-		&\Qf{a}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{a}\Af{g}\Ef{a}\Sf{y}\Df{d}\If{i}\?		&\Qf{a}\Af{g}\Ef{a}\Sf{y}\Ff{s}\If{i}\?		&\Qf{a}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{a}\Af{g}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{a}\Af{g}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{a}\Af{g}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{a}\Af{g}\Ef{a}\Sf{y}\\
\Qf{ka}- qualifier	&\Af{g}-	&\Sf{yi}-	&\Qf{ka}-\Af{g}-\Sf{yi}-	&\Qf{ka}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{ka}\Af{g}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Qf{ka}\Af{g}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Qf{ka}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{ka}\Af{g}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{ka}\Af{g}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{ka}\Af{g}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{ka}\Af{g}\Ef{a}\Sf{y}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g}-	&\Sf{yi}-	&\Qf{x̱ʼe}-\Af{g}-\Sf{yi}-	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Sf{y}\\
\Qf{ji}- ‘hand’		&\Af{g}-	&\Sf{yi}-	&\Qf{ji}-\Af{g}-\Sf{yi}-	&\Qf{ji}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{ji}\Af{g}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Qf{ji}\Af{g}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Qf{ji}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{ji}\Af{g}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{ji}\Af{g}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{ji}\Af{g}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{ji}\Af{g}\Ef{a}\Sf{y}\\
\Qf{tu}- ‘inside’	&\Af{g}-	&\Sf{yi}-	&\Qf{tu}-\Af{g}-\Sf{yi}-	&\Qf{tu}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ff{z}\If{i}\?	&\Qf{tu}\Af{g}\Ef{a}\Sf{y}\Df{d}\If{i}\?	&\Qf{tu}\Af{g}\Ef{a}\Sf{y}\Ff{s}\If{i}\?	&\Qf{tu}\Af{g}\Ef{a}\Sf{y}\Df{d}\Ef{a}	&\Qf{tu}\Af{g}\Ef{a}\Sf{yi}\df{\Ff{s}}	&\Qf{tu}\Af{g}\Ef{a}\Sf{y}\Ff{s}\Ef{a}	&\Qf{tu}\Af{g}\Ef{a}\Sf{yee}\If{y}\?	&\Qf{tu}\Af{g}\Ef{a}\Sf{y}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation \textit{g-}, second person plural subject \textit{yi-}}
\end{table}

%% G-conjugation, 2PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}				&\Ff{s}-\If{i}\rlap{-}				&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-				&—\\
\midrule
—			&\Af{k}-	&\Sf{ji}-	&\Af{k}-\Sf{ji}-		&\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?		&\Af{k}\Ef{a}\Sf{j}.\Df{t}\If{i}\?		&\Af{k}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?		&\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ef{a}		&\Af{k}\Ef{a}.\Sf{ji}\df{\Ff{s}}		&\Af{k}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}		&\Af{k}\Ef{a}.\Sf{jiː}\If{j}\?		&\Af{k}\Ef{a}\Sf{j}\\
\Qf{ʔa}- expletive	&\Af{k}-	&\Sf{ji}-	&\Qf{ʔa}-\Af{k}-\Sf{ji}-	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{k}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Af{k}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{ʔa}.\Af{k}\Ef{a}\Sf{j}\\
\Qf{kʰa}- qualifier	&\Af{k}-	&\Sf{ji}-	&\Qf{kʰa}-\Af{k}-\Sf{ji}-	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{k}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Af{k}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{kʰa}.\Af{k}\Ef{a}\Sf{j}\\
\Qf{χʼe}- ‘mouth’	&\Af{k}-	&\Sf{ji}-	&\Qf{χʼe}-\Af{k}-\Sf{ji}-	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{k}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Af{k}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{χʼa}.\Af{k}\Ef{a}\Sf{j}\\
\Qf{tʃi}- ‘hand’	&\Af{k}-	&\Sf{ji}-	&\Qf{tʃi}-\Af{k}-\Sf{ji}-	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{k}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Af{k}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{tʃi}.\Af{k}\Ef{a}\Sf{j}\\
\Qf{tʰu}- ‘inside’	&\Af{k}-	&\Sf{ji}-	&\Qf{tʰu}-\Af{k}-\Sf{ji}-	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\If{i}\?	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\If{i}\?	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{j}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{k}\Ef{a}.\Sf{ji}\df{\Ff{s}}	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{j}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{k}\Ef{a}.\Sf{jiː}\If{j}\?	&\Qf{tʰu}.\Af{k}\Ef{a}\Sf{j}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation /{k-}/, second person plural subject /{ji-}/, IPA}
\end{table}

\clearpage
%% G-conjugation, 4H
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-	&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-	&\If{i}-				&—\\
\midrule
—			&\Af{g}-	&\Sf{du}-	&\Af{g}-\Sf{du}-		&\Af{g}\Ef{a}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Af{g}\Ef{a}\Sf{du}\df{\Ff{s}}		&⁎		&\Af{g}\Ef{a}\Sf{du}\If{w}\Ef{a}\?	&\Af{g}\Ef{a}\Sf{du}\\
\Qf{a}- expletive	&\Af{g}-	&\Sf{du}-	&\Qf{a}-\Af{g}-\Sf{du}-		&\Qf{a}\Af{k}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{a}\Af{k}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{a}\Af{k}\Sf{du}\If{w}\Ef{a}\?	&\Qf{a}\Af{k}\Sf{du}\\
\Qf{ka}- qualifier	&\Af{g}-	&\Sf{du}-	&\Qf{ka}-\Af{g}-\Sf{du}-	&\Qf{ka}\Af{k}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{ka}\Af{k}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ka}\Af{k}\Sf{du}\If{w}\Ef{a}\?	&\Qf{ka}\Af{k}\Sf{du}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{g}-	&\Sf{du}-	&\Qf{x̱ʼe}-\Af{g}-\Sf{du}-	&\Qf{x̱ʼa}\Af{k}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{x̱ʼa}\Af{k}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{x̱ʼa}\Af{k}\Sf{du}\If{w}\Ef{a}\?	&\Qf{x̱ʼa}\Af{k}\Sf{du}\\
\Qf{ji}- ‘hand’		&\Af{g}-	&\Sf{du}-	&\Qf{ji}-\Af{g}-\Sf{du}-	&\Qf{ji}\Af{k}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{ji}\Af{k}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ji}\Af{k}\Sf{du}\If{w}\Ef{a}\?	&\Qf{ji}\Af{k}\Sf{du}\\
\Qf{tu}- ‘inside’	&\Af{g}-	&\Sf{du}-	&\Qf{tu}-\Af{g}-\Sf{du}-	&\Qf{tu}\Af{k}\Sf{du}\Df{d}\Ff{z}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{tu}\Af{k}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{tu}\Af{k}\Sf{du}\If{w}\Ef{a}\?	&\Qf{tu}\Af{k}\Sf{du}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation \textit{g-}, fourth person (indefinite) human subject \textit{du-}}
\end{table}

%% G-conjugation, 4H, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}				&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-	&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-	&\If{i}-					&—\\
\midrule
—			&\Af{k}-	&\Sf{tu}-	&\Af{k}-\Sf{tu}-		&\Af{k}\Ef{a}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Af{k}\Ef{a}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Af{k}\Ef{a}.\Sf{tu}.\If{w}\Ef{a}\?		&\Af{k}\Ef{a}.\Sf{tu}\\
\Qf{ʔa}- expletive	&\Af{k}-	&\Sf{tu}-	&\Qf{ʔa}-\Af{k}-\Sf{tu}-	&\Qf{ʔa}\Af{k}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{ʔa}\Af{k}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{ʔa}\Af{k}.\Sf{tu}.\If{w}\Ef{a}\?		&\Qf{ʔa}\Af{k}.\Sf{tu}\\
\Qf{kʰa}- qualifier	&\Af{k}-	&\Sf{tu}-	&\Qf{kʰa}-\Af{k}-\Sf{tu}-	&\Qf{kʰa}\Af{k}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{kʰa}\Af{k}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{kʰa}\Af{k}.\Sf{tu}.\If{w}\Ef{a}\?		&\Qf{kʰa}\Af{k}.\Sf{tu}\\
\Qf{χʼe}- ‘mouth’	&\Af{k}-	&\Sf{tu}-	&\Qf{χʼe}-\Af{k}-\Sf{tu}-	&\Qf{χʼa}\Af{k}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{χʼa}\Af{k}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{χʼa}\Af{k}.\Sf{tu}.\If{w}\Ef{a}\?		&\Qf{χʼa}\Af{k}.\Sf{tu}\\
\Qf{tʃi}- ‘hand’	&\Af{k}-	&\Sf{tu}-	&\Qf{tʃi}-\Af{k}-\Sf{tu}-	&\Qf{tʃi}\Af{k}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?		&⁎			&⁎			&⁎		&\Qf{tʃi}\Af{k}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Qf{tʃi}\Af{k}.\Sf{tu}.\If{w}\Ef{a}\?		&\Qf{tʃi}\Af{k}.\Sf{tu}\\
\Qf{tʰu}- ‘inside’	&\Af{k}-	&\Sf{tu}-	&\Qf{tʰu}-\Af{k}-\Sf{tu}-	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tu}.\Df{t}\Ff{s}\If{i}\?	&⁎			&⁎			&⁎		&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tu}.\If{w}\Ef{a}\?	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Sf{tu}\\
\bottomrule
\end{tabular}
\caption{\textit{G}-conjugation /{k-}/, fourth person (indefinite) human subject /{tu-}/, IPA}
\end{table}

\clearpage
%%%
%%% G-conjugation with irrealis 
%%%
\subsection{\textit{G}-conjugation prefix \textit{g-} with irrealis \textit{u-}}\label{sec:gconj-irrealis}

%%%
%%% G-conjugation with modal
%%%
\subsection{\textit{G}-conjugation prefix \textit{g-} with modal \textit{g̱-}}\label{sec:gconj-modal}

%%%
%%% G-conjugation with irrealis and modal
%%%
\subsection{\textit{G}-conjugation prefix \textit{g-} with irrealis \textit{u-} and modal \textit{g̱-}}\label{sec:gconj-irrealis+modal}

\clearpage
%%%
%%% Perfective
%%%

\section{Perfective prefixes \textit{wu-} and \textit{u-}}\label{sec:pfv}

\begin{multicols}{2}
\end{multicols}

\clearpage
%% Perfective, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}		&\Df{d}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{d}-			&\Df{d}-\Ff{s}\rlap{-}		&\Ff{s}-		&\If{i}-			&—\\
\midrule
—			&\Af{wu}-	&—		&\Af{wu}-			&\Af{wu}\Df{d}\Ff{z}\If{i}		&\Af{wu}\Df{d}\If{i}		&\Af{wu}\Ff{s}\If{i}		&\Af{wu}\Df{d}\Ef{a}		&\Af{wu}\df{\Ff{s}}		&\Af{wu}\Ff{s}		&\Af{wo}\If{o}			&\Af{wu}\\
—			&\Af{u}-	&—		&\Af{u}-			&					&				&				&\Af{u}\Df{d}\Ef{a}		&\Af{u}\df{\Ff{s}}		&\Af{u}\Ff{s}		&\Af{u}\If{w}\Ef{a}		&\Af{u}\\
\Qf{a}- arg./expl.	&\Af{wu}-	&—		&\Qf{a}-\Af{wu}-		&\Qf{a}\Af{w}\Df{d}\Ff{z}\If{i}		&\Qf{a}\Af{w}\Df{d}\If{i}	&\Qf{a}\Af{w}\Ff{s}\If{i}	&\Qf{a}\Af{w}\Df{d}\Ef{a}	&\Qf{a}\Af{wu}\df{\Ff{s}}	&\Qf{a}\Af{wu}\Ff{s}	&\Qf{a}\Af{a}\If{w}\Ef{a}	&\Qf{a}\Af{wu}\\
\Qf{a}- arg./expl.	&\Af{u}-	&—		&\Qf{a}-\Af{u}-			&					&				&				&\Qf{o}\Af{o}\Df{d}\Ef{a}\?	&\Qf{o}\Af{o}\df{\Ff{s}}\?	&\Qf{o}\Af{o}\Ff{s}	&\Qf{o}\Af{o}\If{w}\Ef{a}\?	&\Qf{o}\Af{o}\\
\Qf{ka}- qualifier	&\Af{wu}-	&—		&\Qf{ka}-\Af{wu}-		&\Qf{ka}\Af{w}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\Af{w}\Df{d}\If{i}	&\Qf{ka}\Af{w}\Ff{s}\If{i}	&\Qf{ka}\Af{w}\Df{d}\Ef{a}	&\Qf{ka}\Af{wu}\df{\Ff{s}}	&\Qf{ka}\Af{wu}\Ff{s}	&\Qf{ka}\Af{a}\If{w}\Ef{a}	&\Qf{ka}\Af{wu}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{wu}-	&—		&\Qf{x̱ʼe}-\Af{wu}-		&\Qf{x̱ʼa}\Af{w}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Af{w}\Df{d}\If{i}	&\Qf{x̱ʼa}\Af{w}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Af{w}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{wu}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{wu}\Ff{s}	&\Qf{x̱ʼe}\Af{i}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Af{wu}\\
\Qf{ji}- ‘hand’		&\Af{wu}-	&—		&\Qf{ji}-\Af{wu}-		&\Qf{ji}\Af{w}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\Af{w}\Df{d}\If{i}	&\Qf{ji}\Af{w}\Ff{s}\If{i}	&\Qf{ji}\Af{w}\Df{d}\Ef{a}	&\Qf{ji}\Af{wu}\df{\Ff{s}}	&\Qf{ji}\Af{wu}\Ff{s}	&\Qf{je}\Af{e}\If{w}\Ef{a}	&\Qf{ji}\Af{wu}\\
\Qf{tu}- ‘inside’	&\Af{wu}-	&—		&\Qf{tu}-\Af{wu}-		&\Qf{tu}\Af{w}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\Af{w}\Df{d}\If{i}	&\Qf{tu}\Af{w}\Ff{s}\If{i}	&\Qf{tu}\Af{w}\Df{d}\Ef{a}	&\Qf{tu}\Af{wu}\df{\Ff{s}}	&\Qf{tu}\Af{wu}\Ff{s}	&\Qf{to}\Af{o}\If{w}\Ef{a}	&\Qf{tu}\Af{wu}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect \textit{wu-} or \textit{u-} (incl.\ \textit{∅}-conj.\ habitual), unmarked subject (third person or no subject)}
\end{table}

%% Perfective, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}		&\Df{t}-\If{i}\rlap{-}		&\Ff{s}-\If{i}\rlap{-}		&\Df{t}-			&\Df{t}-\Ff{s}\rlap{-}		&\Ff{s}-		&\If{i}-			&—\\
\midrule
—			&\Af{wu}-	&—		&\Af{wu}-			&\Af{wu}.\Df{t}\Ff{s}\If{i}		&\Af{wu}.\Df{t}\If{i}		&\Af{wu}.\Ff{s}\If{i}		&\Af{wu}.\Df{t}\Ef{a}		&\Af{wu}\df{\Ff{s}}		&\Af{wu}\Ff{s}		&\Af{wu}\If{ː}			&\Af{wu}\\
—			&\Af{u}-	&—		&\Af{u}-			&					&				&				&\Af{ʔu}.\Df{t}\Ef{a}		&\Af{ʔu}\df{\Ff{s}}		&\Af{ʔu}\Ff{s}		&\Af{ʔu}.\If{w}\Ef{a}		&\Af{ʔu}\\
\Qf{ʔa}- arg./expl.	&\Af{wu}-	&—		&\Qf{ʔa}-\Af{wu}-		&\Qf{ʔa}\Af{w}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔa}\Af{w}.\Df{t}\If{i}	&\Qf{ʔa}\Af{w}.\Ff{s}\If{i}	&\Qf{ʔa}\Af{w}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{wu}\df{\Ff{s}}	&\Qf{ʔa}.\Af{wu}\Ff{s}	&\Qf{ʔa}\Af{ː}.\If{w}\Ef{a}	&\Qf{ʔa}.\Af{wu}\\
\Qf{ʔa}- arg./expl.	&\Af{u}-	&—		&\Qf{ʔa}-\Af{u}-		&					&				&				&\Qf{ʔu}\Af{ː}.\Df{t}\Ef{a}\?	&\Qf{ʔu}\Af{ː}\df{\Ff{s}}\?	&\Qf{ʔu}\Af{ː}\Ff{s}	&\Qf{ʔu}\Af{ː}.\If{w}\Ef{a}\?	&\Qf{ʔu}\Af{ː}\\
\Qf{kʰa}- qualifier	&\Af{wu}-	&—		&\Qf{kʰa}-\Af{wu}-		&\Qf{kʰa}\Af{w}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}\Af{w}.\Df{t}\If{i}	&\Qf{kʰa}\Af{w}.\Ff{s}\If{i}	&\Qf{kʰa}\Af{w}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{wu}\df{\Ff{s}}	&\Qf{kʰa}.\Af{wu}\Ff{s}	&\Qf{kʰa}\Af{ː}.\If{w}\Ef{a}	&\Qf{kʰa}.\Af{wu}\\
\Qf{χʼe}- ‘mouth’	&\Af{wu}-	&—		&\Qf{χʼe}-\Af{wu}-		&\Qf{χʼa}\Af{w}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}\Af{w}.\Df{t}\If{i}	&\Qf{χʼa}\Af{w}.\Ff{s}\If{i}	&\Qf{χʼa}\Af{w}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{wu}\df{\Ff{s}}	&\Qf{χʼa}.\Af{wu}\Ff{s}	&\Qf{χʼe}\Af{ː}.\If{w}\Ef{a}	&\Qf{χʼa}.\Af{wu}\\
\Qf{tʃi}- ‘hand’	&\Af{wu}-	&—		&\Qf{tʃi}-\Af{wu}-		&\Qf{tʃi}\Af{w}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}\Af{w}.\Df{t}\If{i}	&\Qf{tʃi}\Af{w}.\Ff{s}\If{i}	&\Qf{tʃi}\Af{w}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{wu}\df{\Ff{s}}	&\Qf{tʃi}.\Af{wu}\Ff{s}	&\Qf{tʃi}\Af{ː}.\If{w}\Ef{a}	&\Qf{tʃi}.\Af{wu}\\
\Qf{tʰu}- ‘inside’	&\Af{wu}-	&—		&\Qf{tʰu}-\Af{wu}-		&\Qf{tʰu}\Af{w}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}\Af{w}.\Df{t}\If{i}	&\Qf{tʰu}\Af{w}.\Ff{s}\If{i}	&\Qf{tʰu}\Af{w}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{wu}\df{\Ff{s}}	&\Qf{tʰu}.\Af{wu}\Ff{s}	&\Qf{tʰu}\Af{ː}.\If{w}\Ef{a}	&\Qf{tʰu}.\Af{wu}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect /{wu-}/ or /{u-}/ (incl.\ \textit{∅}-conj.\ habitual), unmarked subject (third person or no subject), IPA}
\end{table}

\clearpage
%% Perfective, 1SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{wu}-	&\Sf{x̱}-	&\Af{wu}-\Sf{x̱}-		&\Sf{x̱}\Af{w}\Ef{a}\Df{d}\Ff{z}\If{i}		&\Sf{x̱}\Af{w}\Ef{a}\Df{d}\If{i}		&\Sf{x̱}\Af{w}\Ef{a}\Ff{s}\If{i}		&\Sf{x̱}\Af{w}\Ef{a}\Df{d}\Ef{a}		&\Sf{x̱}\Af{w}\Ef{a}\df{\Ff{s}}		&\Sf{x̱}\Af{w}\Ef{a}\Ff{s}\Ef{a}		&\Sf{x̱}\Af{w}\Ef{a}\If{a}		&\Sf{x̱}\Af{w}\Ef{a}\\
\Qf{a}- arg/expl.	&\Af{wu}-	&\Sf{x̱}-	&\Qf{a}-\Af{wu}-\Sf{x̱}-		&\Qf{a}\Sf{x̱}\Af{w}\Df{d}\Ff{z}\If{i}		&\Qf{a}\Sf{x̱}\Af{w}\Df{d}\If{i}		&\Qf{a}\Sf{x̱}\Af{w}\Ff{s}\If{i}		&\Qf{a}\Sf{x̱}\Af{w}\Df{d}\Ef{a}		&\Qf{a}\Sf{x̱}\Af{w}\Ef{a}\df{\Ff{s}}	&\Qf{a}\Sf{x̱}\Af{w}\Ff{s}\Ef{a}		&\Qf{a}\Sf{x̱}\Af{w}\Ef{a}\If{a}		&\Qf{a}\Sf{x̱}\Af{w}\Ef{a}\\
\Qf{ka}- qualifier	&\Af{wu}-	&\Sf{x̱}-	&\Qf{ka}-\Af{wu}-\Sf{x̱}-	&\Qf{ka}\Sf{x̱}\Af{w}\Df{d}\Ff{z}\If{i}		&\Qf{ka}\Sf{x̱}\Af{w}\Df{d}\If{i}	&\Qf{ka}\Sf{x̱}\Af{w}\Ff{s}\If{i}	&\Qf{ka}\Sf{x̱}\Af{w}\Df{d}\Ef{a}	&\Qf{ka}\Sf{x̱}\Af{w}\Ef{a}\df{\Ff{s}}	&\Qf{ka}\Sf{x̱}\Af{w}\Ff{s}\Ef{a}	&\Qf{ka}\Sf{x̱}\Af{w}\Ef{a}\If{a}	&\Qf{ka}\Sf{x̱}\Af{w}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{wu}-	&\Sf{x̱}-	&\Qf{x̱ʼe}-\Af{wu}-\Sf{x̱}-	&\Qf{x̱ʼa}\Sf{x̱}\Af{w}\Df{d}\Ff{z}\If{i}		&\Qf{x̱ʼa}\Sf{x̱}\Af{w}\Df{d}\If{i}	&\Qf{x̱ʼa}\Sf{x̱}\Af{w}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Sf{x̱}\Af{w}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Sf{x̱}\Af{w}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Sf{x̱}\Af{w}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Sf{x̱}\Af{w}\Ef{a}\If{a}	&\Qf{x̱ʼa}\Sf{x̱}\Af{w}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Af{wu}-	&\Sf{x̱}-	&\Qf{ji}-\Af{wu}-\Sf{x̱}-	&\Qf{ji}\Sf{x̱}\Af{w}\Df{d}\Ff{z}\If{i}		&\Qf{ji}\Sf{x̱}\Af{w}\Df{d}\If{i}	&\Qf{ji}\Sf{x̱}\Af{w}\Ff{s}\If{i}	&\Qf{ji}\Sf{x̱}\Af{w}\Df{d}\Ef{a}	&\Qf{ji}\Sf{x̱}\Af{w}\Ef{a}\df{\Ff{s}}	&\Qf{ji}\Sf{x̱}\Af{w}\Ff{s}\Ef{a}	&\Qf{ji}\Sf{x̱}\Af{w}\Ef{a}\If{a}	&\Qf{ji}\Sf{x̱}\Af{w}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Af{wu}-	&\Sf{x̱}-	&\Qf{tu}-\Af{wu}-\Sf{x̱}-	&\Qf{tu}\Sf{x̱}\Af{w}\Df{d}\Ff{z}\If{i}		&\Qf{tu}\Sf{x̱}\Af{w}\Df{d}\If{i}	&\Qf{tu}\Sf{x̱}\Af{w}\Ff{s}\If{i}	&\Qf{tu}\Sf{x̱}\Af{w}\Df{d}\Ef{a}	&\Qf{tu}\Sf{x̱}\Af{w}\Ef{a}\df{\Ff{s}}	&\Qf{tu}\Sf{x̱}\Af{w}\Ff{s}\Ef{a}	&\Qf{tu}\Sf{x̱}\Af{w}\Ef{a}\If{a}	&\Qf{tu}\Sf{x̱}\Af{w}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect \textit{wu-} (incl.\ \textit{∅}-conj.\ habitual), first person singular subject \textit{x̱-}}
\end{table}

%% Perfective, 1SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule
—			&\Af{wu}-	&\Sf{χ}-	&\Af{wu}-\Sf{χ}-		&\Sf{χ}\Af{ʷ}\Ef{a}.\Df{t}\Ff{s}\If{i}		&\Sf{χ}\Af{ʷ}\Ef{a}.\Df{t}\If{i}	&\Sf{χ}\Af{ʷ}\Ef{a}.\Ff{s}\If{i}	&\Sf{χ}\Af{ʷ}\Ef{a}.\Df{t}\Ef{a}	&\Sf{χ}\Af{ʷ}\Ef{a}\df{\Ff{s}}		&\Sf{χ}\Af{ʷ}\Ef{a}.\Ff{s}\Ef{a}	&\Sf{χ}\Af{ʷ}\Ef{a}\If{ː}		&\Sf{χ}\Af{ʷ}\Ef{a}\\
\Qf{ʔa}- arg/expl.	&\Af{wu}-	&\Sf{χ}-	&\Qf{ʔa}-\Af{wu}-\Sf{χ}-	&\Qf{ʔa}\Sf{χ}\Af{ʷ}.\Df{t}\Ff{s}\If{i}		&\Qf{ʔa}\Sf{χ}\Af{ʷ}.\Df{t}\If{i}	&\Qf{ʔa}\Sf{χ}\Af{ʷ}.\Ff{s}\If{i}	&\Qf{ʔa}\Sf{χ}\Af{ʷ}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Sf{χ}\Af{ʷ}\Ef{a}\df{\Ff{s}}	&\Qf{ʔa}\Sf{χ}\Af{ʷ}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Sf{χ}\Af{ʷ}\Ef{a}\If{ː}	&\Qf{ʔa}.\Sf{χ}\Af{ʷ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Af{wu}-	&\Sf{χ}-	&\Qf{kʰa}-\Af{wu}-\Sf{χ}-	&\Qf{kʰa}\Sf{χ}\Af{ʷ}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}\Sf{χ}\Af{ʷ}.\Df{t}\If{i}	&\Qf{kʰa}\Sf{χ}\Af{ʷ}.\Ff{s}\If{i}	&\Qf{kʰa}\Sf{χ}\Af{ʷ}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Sf{χ}\Af{ʷ}\Ef{a}\df{\Ff{s}}	&\Qf{kʰa}\Sf{χ}\Af{ʷ}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Sf{χ}\Af{ʷ}\Ef{a}\If{ː}	&\Qf{kʰa}.\Sf{χ}\Af{ʷ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Af{wu}-	&\Sf{χ}-	&\Qf{χʼe}-\Af{wu}-\Sf{χ}-	&\Qf{χʼa}\Sf{χ}\Af{ʷ}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}\Sf{χ}\Af{ʷ}.\Df{t}\If{i}	&\Qf{χʼa}\Sf{χ}\Af{ʷ}.\Ff{s}\If{i}	&\Qf{χʼa}\Sf{χ}\Af{ʷ}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Sf{χ}\Af{ʷ}\Ef{a}\df{\Ff{s}}	&\Qf{χʼa}\Sf{χ}\Af{ʷ}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Sf{χ}\Af{ʷ}\Ef{a}\If{ː}	&\Qf{χʼa}.\Sf{χ}\Af{ʷ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Af{wu}-	&\Sf{χ}-	&\Qf{tʃi}-\Af{wu}-\Sf{χ}-	&\Qf{tʃi}\Sf{χ}\Af{ʷ}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}\Sf{χ}\Af{ʷ}.\Df{t}\If{i}	&\Qf{tʃi}\Sf{χ}\Af{ʷ}.\Ff{s}\If{i}	&\Qf{tʃi}\Sf{χ}\Af{ʷ}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Sf{χ}\Af{ʷ}\Ef{a}\df{\Ff{s}}	&\Qf{tʃi}\Sf{χ}\Af{ʷ}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Sf{χ}\Af{ʷ}\Ef{a}\If{ː}	&\Qf{tʃi}.\Sf{χ}\Af{ʷ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Af{wu}-	&\Sf{χ}-	&\Qf{tʰu}-\Af{wu}-\Sf{χ}-	&\Qf{tʰu}\Sf{χ}\Af{ʷ}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}\Sf{χ}\Af{ʷ}.\Df{t}\If{i}	&\Qf{tʰu}\Sf{χ}\Af{ʷ}.\Ff{s}\If{i}	&\Qf{tʰu}\Sf{χ}\Af{ʷ}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Sf{χ}\Af{ʷ}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}\Sf{χ}\Af{ʷ}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Sf{χ}\Af{ʷ}\Ef{a}\If{ː}	&\Qf{tʰu}.\Sf{χ}\Af{ʷ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect /{wu-}/ (incl.\ \textit{∅}-conj.\ habitual), first person singular subject /{χ-}/}
\end{table}

\clearpage
%% Perfective, 1PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule																															                                        
—			&\Af{wu}-	&\Sf{tu}-	&\Af{wu}-\Sf{tu}-		&\Af{wu}\Sf{tu}\Df{d}\Ff{z}\If{i}		&\Af{wu}\Sf{tu}\Df{d}\If{i}		&\Af{wu}\Sf{tu}\Ff{s}\If{i}		&\Af{wu}\Sf{tu}\Df{d}\Ef{a}		&\Af{wu}\Sf{too}\df{\Ff{s}}		&\Af{wu}\Sf{tu}\Ff{s}\Ef{a}		&\Af{wu}\Sf{tu}\If{w}\Ef{a}		&\Af{wu}\Sf{too}\\
\Qf{a}- expletive	&\Af{wu}-	&\Sf{tu}-	&\Qf{a}-\Af{wu}-\Sf{tu}-	&\Qf{a}\Af{w}\Sf{tu}\Df{d}\Ff{z}\If{i}		&\Qf{a}\Af{w}\Sf{tu}\Df{d}\If{i}	&\Qf{a}\Af{w}\Sf{tu}\Ff{s}\If{i}	&\Qf{a}\Af{w}\Sf{tu}\Df{d}\Ef{a}	&\Qf{a}\Af{w}\Sf{too}\df{\Ff{s}}	&\Qf{a}\Af{w}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{a}\Af{w}\Sf{tu}\If{w}\Ef{a}	&\Qf{a}\Af{w}\Sf{too}\\
\Qf{ka}- qualifier	&\Af{wu}-	&\Sf{tu}-	&\Qf{ka}-\Af{wu}-\Sf{tu}-	&\Qf{ka}\Af{w}\Sf{tu}\Df{d}\Ff{z}\If{i}		&\Qf{ka}\Af{w}\Sf{tu}\Df{d}\If{i}	&\Qf{ka}\Af{w}\Sf{tu}\Ff{s}\If{i}	&\Qf{ka}\Af{w}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ka}\Af{w}\Sf{too}\df{\Ff{s}}	&\Qf{ka}\Af{w}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ka}\Af{w}\Sf{tu}\If{w}\Ef{a}	&\Qf{ka}\Af{w}\Sf{too}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{wu}-	&\Sf{tu}-	&\Qf{x̱ʼe}-\Af{wu}-\Sf{tu}-	&\Qf{x̱ʼa}\Af{w}\Sf{tu}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Af{w}\Sf{tu}\Df{d}\If{i}	&\Qf{x̱ʼa}\Af{w}\Sf{tu}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Af{w}\Sf{tu}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{w}\Sf{too}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{w}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{w}\Sf{tu}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Af{w}\Sf{too}\\
\Qf{ji}- ‘hand’		&\Af{wu}-	&\Sf{tu}-	&\Qf{ji}-\Af{wu}-\Sf{tu}-	&\Qf{ji}\Af{w}\Sf{tu}\Df{d}\Ff{z}\If{i}		&\Qf{ji}\Af{w}\Sf{tu}\Df{d}\If{i}	&\Qf{ji}\Af{w}\Sf{tu}\Ff{s}\If{i}	&\Qf{ji}\Af{w}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ji}\Af{w}\Sf{too}\df{\Ff{s}}	&\Qf{ji}\Af{w}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{ji}\Af{w}\Sf{tu}\If{w}\Ef{a}	&\Qf{ji}\Af{w}\Sf{too}\\
\Qf{tu}- ‘inside’	&\Af{wu}-	&\Sf{tu}-	&\Qf{tu}-\Af{wu}-\Sf{tu}-	&\Qf{tu}\Af{w}\Sf{tu}\Df{d}\Ff{z}\If{i}		&\Qf{tu}\Af{w}\Sf{tu}\Df{d}\If{i}	&\Qf{tu}\Af{w}\Sf{tu}\Ff{s}\If{i}	&\Qf{tu}\Af{w}\Sf{tu}\Df{d}\Ef{a}	&\Qf{tu}\Af{w}\Sf{too}\df{\Ff{s}}	&\Qf{tu}\Af{w}\Sf{tu}\Ff{s}\Ef{a}	&\Qf{tu}\Af{w}\Sf{tu}\If{w}\Ef{a}	&\Qf{tu}\Af{w}\Sf{too}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect \textit{wu-} (incl.\ \textit{∅}-conj.\ habitual), first person plural subject \textit{tu-}}
\end{table}

%% Perfective, 1PL, IPA
\begin{table}
\centerfloat
\setlength{\tabcolsep}{0.75ex}
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{+}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule																															                                        
—			&\Af{wu}-	&\Sf{tʰu}-	&\Af{wu}-\Sf{tʰu}-		&\Af{wu}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}		&\Af{wu}.\Sf{tʰu}.\Df{t}\If{i}		&\Af{wu}.\Sf{tʰu}.\Ff{s}\If{i}		&\Af{wu}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Af{wu}.\Sf{tʰuː}\df{\Ff{s}}		&\Af{wu}.\Sf{tʰu}.\Ff{s}\Ef{a}		&\Af{wu}.\Sf{tʰu}.\If{w}\Ef{a}		&\Af{wu}.\Sf{tʰuː}\\
\Qf{ʔa}- expletive	&\Af{wu}-	&\Sf{tʰu}-	&\Qf{ʔa}-\Af{wu}-\Sf{tʰu}-	&\Qf{ʔa}\Af{w}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔa}\Af{w}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{ʔa}\Af{w}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{ʔa}\Af{w}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{ʔa}\Af{w}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{ʔa}\Af{w}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{ʔa}\Af{w}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{ʔa}\Af{w}.\Sf{tʰuː}\\
\Qf{kʰa}- qualifier	&\Af{wu}-	&\Sf{tʰu}-	&\Qf{kʰa}-\Af{wu}-\Sf{tʰu}-	&\Qf{kʰa}\Af{w}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}\Af{w}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{kʰa}\Af{w}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{kʰa}\Af{w}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{kʰa}\Af{w}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{kʰa}\Af{w}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{kʰa}\Af{w}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{kʰa}\Af{w}.\Sf{tʰuː}\\
\Qf{χʼe}- ‘mouth’	&\Af{wu}-	&\Sf{tʰu}-	&\Qf{χʼe}-\Af{wu}-\Sf{tʰu}-	&\Qf{χʼa}\Af{w}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}\Af{w}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{χʼa}\Af{w}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{χʼa}\Af{w}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{χʼa}\Af{w}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{χʼa}\Af{w}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{χʼa}\Af{w}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{χʼa}\Af{w}.\Sf{tʰuː}\\
\Qf{tʃi}- ‘hand’	&\Af{wu}-	&\Sf{tʰu}-	&\Qf{tʃi}-\Af{wu}-\Sf{tʰu}-	&\Qf{tʃi}\Af{w}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}\Af{w}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{tʃi}\Af{w}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{tʃi}\Af{w}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʃi}\Af{w}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʃi}\Af{w}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʃi}\Af{w}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʃi}\Af{w}.\Sf{tʰuː}\\
\Qf{tʰu}- ‘inside’	&\Af{wu}-	&\Sf{tʰu}-	&\Qf{tʰu}-\Af{wu}-\Sf{tʰu}-	&\Qf{tʰu}\Af{w}.\Sf{tʰu}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}\Af{w}.\Sf{tʰu}.\Df{t}\If{i}	&\Qf{tʰu}\Af{w}.\Sf{tʰu}.\Ff{s}\If{i}	&\Qf{tʰu}\Af{w}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}\Af{w}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʰu}\Af{w}.\Sf{tʰu}.\Ff{s}\Ef{a}	&\Qf{tʰu}\Af{w}.\Sf{tʰu}.\If{w}\Ef{a}	&\Qf{tʰu}\Af{w}.\Sf{tʰuː}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect /{wu-}/ (incl.\ \textit{∅}-conj.\ habitual), first person plural subject /{tʰu-}/}
\end{table}

\clearpage
%% Perfective, 2SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule																															                                        
—			&\Af{wu}-	&\Sf{i}-	&\Af{wu}-\Sf{i}-		&\Af{y}\Sf{i}\Df{d}\Ff{z}\If{i}			&\Af{y}\Sf{i}\Df{d}\If{i}		&\Af{y}\Sf{i}\Ff{s}\If{i}		&\Af{y}\Sf{i}\Df{d}\Ef{a}		&\Af{y}\Sf{i}\df{\Ff{s}}		&\Af{y}\Sf{i}\Ff{s}\Ef{a}		&\Af{y}\Sf{e}\If{e}			&\Af{y}\Sf{i}\\
—			&\Af{u}-	&\Sf{i}-	&\Qf{u}-\Sf{i}-			&						&					&					&					&					&					&\af{\Sf{i}}\If{y}\Ef{a}		&\\
			&		&		&				&						&					&					&					&					&					&\Af{e}\Sf{e}\If{y}\Ef{a}\?		&\\
\Qf{a}- expletive	&\Af{wu}-	&\Sf{i}-	&\Qf{a}-\Af{wu}-\Sf{i}-		&\Qf{a}\af{\Sf{y}\Sf{}}\Df{d}\Ff{z}\If{i}	&\Qf{a}\af{\Sf{y}\Sf{}}\Df{d}\If{i}	&\Qf{a}\af{\Sf{y}\Sf{}}\Ff{s}\If{i}	&\Qf{a}\af{\Sf{y}\Sf{}}\Df{d}\Ef{a}	&\Qf{a}\Af{y}\Sf{i}\df{\Ff{s}}		&\Qf{a}\af{\Sf{y}\Sf{}}\Ff{s}\Ef{a}	&\Qf{}\Af{e}\Sf{e}\If{y}\Ef{a}		&\Qf{a}\Af{y}\Sf{i}\\
\Qf{ka}- qualifier	&\Af{wu}-	&\Sf{i}-	&\Qf{ka}-\Af{wu}-\Sf{i}-	&\Qf{ka}\af{\Sf{y}\Sf{}}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\af{\Sf{y}\Sf{}}\Df{d}\If{i}	&\Qf{ka}\af{\Sf{y}\Sf{}}\Ff{s}\If{i}	&\Qf{ka}\af{\Sf{y}\Sf{}}\Df{d}\Ef{a}	&\Qf{ka}\Af{y}\Sf{i}\df{\Ff{s}}		&\Qf{ka}\af{\Sf{y}\Sf{}}\Ff{s}\Ef{a}	&\Qf{k}\Af{e}\Sf{e}\If{y}\Ef{a}		&\Qf{ka}\Af{y}\Sf{i}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{wu}-	&\Sf{i}-	&\Qf{x̱ʼe}-\Af{wu}-\Sf{i}-	&\Qf{x̱ʼa}\af{\Sf{y}\Sf{}}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\af{\Sf{y}\Sf{}}\Df{d}\If{i}	&\Qf{x̱ʼa}\af{\Sf{y}\Sf{}}\Ff{s}\If{i}	&\Qf{x̱ʼa}\af{\Sf{y}\Sf{}}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{y}\Sf{i}\df{\Ff{s}}	&\Qf{x̱ʼa}\af{\Sf{y}\Sf{}}\Ff{s}\Ef{a}	&\Qf{x̱ʼ}\Af{e}\Sf{e}\If{y}\Ef{a}	&\Qf{x̱ʼa}\Af{y}\Sf{i}\\
\Qf{ji}- ‘hand’		&\Af{wu}-	&\Sf{i}-	&\Qf{ji}-\Af{wu}-\Sf{i}-	&\Qf{ji}\af{\Sf{y}\Sf{}}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\af{\Sf{y}\Sf{}}\Df{d}\If{i}	&\Qf{ji}\af{\Sf{y}\Sf{}}\Ff{s}\If{i}	&\Qf{ji}\af{\Sf{y}\Sf{}}\Df{d}\Ef{a}	&\Qf{ji}\Af{y}\Sf{i}\df{\Ff{s}}		&\Qf{ji}\af{\Sf{y}\Sf{}}\Ff{s}\Ef{a}	&\Qf{j}\Af{e}\Sf{e}\If{y}\Ef{a}		&\Qf{ji}\Af{y}\Sf{i}\\
\Qf{tu}- ‘inside’	&\Af{wu}-	&\Sf{i}-	&\Qf{tu}-\Af{wu}-\Sf{i}-	&\Qf{tu}\af{\Sf{y}\Sf{}}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\af{\Sf{y}\Sf{}}\Df{d}\If{i}	&\Qf{tu}\af{\Sf{y}\Sf{}}\Ff{s}\If{i}	&\Qf{tu}\af{\Sf{y}\Sf{}}\Df{d}\Ef{a}	&\Qf{tu}\Af{y}\Sf{i}\df{\Ff{s}}		&\Qf{tu}\af{\Sf{y}\Sf{}}\Ff{s}\Ef{a}	&\Qf{t}\Af{e}\Sf{e}\If{y}\Ef{a}		&\Qf{tu}\Af{y}\Sf{i}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect \textit{wu-} (incl.\ \textit{∅}-conj.\ habitual), second person singular subject \textit{i-}}
\end{table}

%% Perfective, 2SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule																															                                        
—			&\Af{wu}-	&\Sf{i}-	&\Af{wu}-\Sf{i}-		&\Af{j}\Sf{i}.\Df{t}\Ff{s}\If{i}		&\Af{j}\Sf{i}.\Df{t}\If{i}		&\Af{j}\Sf{i}.\Ff{s}\If{i}		&\Af{j}\Sf{i}.\Df{t}\Ef{a}		&\Af{j}\Sf{i}\df{\Ff{s}}		&\Af{j}\Sf{i}.\Ff{s}\Ef{a}		&\Af{j}\Sf{i}\If{ː}			&\Af{j}\Sf{i}\\
—			&\Af{u}-	&\Sf{i}-	&\Qf{u}-\Sf{i}-			&						&					&					&					&					&					&\Ef{ʔ}\af{\Sf{i}}.\If{j}\Ef{a}		&\\
			&		&		&				&						&					&					&					&					&					&\Ef{ʔ}\Af{i}\Sf{ː}.\If{j}\Ef{a}\?	&\\
\Qf{ʔa}- expletive	&\Af{wu}-	&\Sf{i}-	&\Qf{ʔa}-\Af{wu}-\Sf{i}-	&\Qf{ʔa}\af{\Sf{j}\Sf{}}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔa}\af{\Sf{j}\Sf{}}.\Df{t}\If{i}	&\Qf{ʔa}\af{\Sf{j}\Sf{}}.\Ff{s}\If{i}	&\Qf{ʔa}\af{\Sf{j}\Sf{}}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{j}\Sf{i}\df{\Ff{s}}	&\Qf{ʔa}\af{\Sf{j}\Sf{}}.\Ff{s}\Ef{a}	&\Qf{ʔ}\Af{i}\Sf{ː}.\If{j}\Ef{a}	&\Qf{ʔa}.\Af{j}\Sf{i}\\
\Qf{kʰa}- qualifier	&\Af{wu}-	&\Sf{i}-	&\Qf{kʰa}-\Af{wu}-\Sf{i}-	&\Qf{kʰa}\af{\Sf{j}\Sf{}}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}\af{\Sf{j}\Sf{}}.\Df{t}\If{i}	&\Qf{kʰa}\af{\Sf{j}\Sf{}}.\Ff{s}\If{i}	&\Qf{kʰa}\af{\Sf{j}\Sf{}}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{j}\Sf{i}\df{\Ff{s}}	&\Qf{kʰa}\af{\Sf{j}\Sf{}}.\Ff{s}\Ef{a}	&\Qf{kʰ}\Af{i}\Sf{ː}.\If{j}\Ef{a}	&\Qf{kʰa}.\Af{j}\Sf{i}\\
\Qf{χʼe}- ‘mouth’	&\Af{wu}-	&\Sf{i}-	&\Qf{χʼe}-\Af{wu}-\Sf{i}-	&\Qf{χʼa}\af{\Sf{j}\Sf{}}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}\af{\Sf{j}\Sf{}}.\Df{t}\If{i}	&\Qf{χʼa}\af{\Sf{j}\Sf{}}.\Ff{s}\If{i}	&\Qf{χʼa}\af{\Sf{j}\Sf{}}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{j}\Sf{i}\df{\Ff{s}}	&\Qf{χʼa}\af{\Sf{j}\Sf{}}.\Ff{s}\Ef{a}	&\Qf{χʼ}\Af{i}\Sf{ː}.\If{j}\Ef{a}	&\Qf{χʼa}.\Af{j}\Sf{i}\\
\Qf{tʃi}- ‘hand’	&\Af{wu}-	&\Sf{i}-	&\Qf{tʃi}-\Af{wu}-\Sf{i}-	&\Qf{tʃi}\af{\Sf{j}\Sf{}}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}\af{\Sf{j}\Sf{}}.\Df{t}\If{i}	&\Qf{tʃi}\af{\Sf{j}\Sf{}}.\Ff{s}\If{i}	&\Qf{tʃi}\af{\Sf{j}\Sf{}}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{j}\Sf{i}\df{\Ff{s}}	&\Qf{tʃi}\af{\Sf{j}\Sf{}}.\Ff{s}\Ef{a}	&\Qf{tʃ}\Af{i}\Sf{ː}.\If{j}\Ef{a}	&\Qf{tʃi}.\Af{j}\Sf{i}\\
\Qf{tʰu}- ‘inside’	&\Af{wu}-	&\Sf{i}-	&\Qf{tʰu}-\Af{wu}-\Sf{i}-	&\Qf{tʰu}\af{\Sf{j}\Sf{}}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}\af{\Sf{j}\Sf{}}.\Df{t}\If{i}	&\Qf{tʰu}\af{\Sf{j}\Sf{}}.\Ff{s}\If{i}	&\Qf{tʰu}\af{\Sf{j}\Sf{}}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{j}\Sf{i}\df{\Ff{s}}	&\Qf{tʰu}\af{\Sf{j}\Sf{}}.\Ff{s}\Ef{a}	&\Qf{tʰ}\Af{i}\Sf{ː}.\If{j}\Ef{a}	&\Qf{tʰu}.\Af{j}\Sf{i}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect /{wu-}/ (incl.\ \textit{∅}-conj.\ habitual), second person singular subject /{i-}/, IPA}
\end{table}

\clearpage
%% Perfective, 2PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule																															                                        
—			&\Af{wu}-	&\Sf{yi}-	&\Af{wu}-\Sf{yi}-		&\Af{ye}\Sf{ey}\Df{d}\Ff{z}\If{i}		&\Af{ye}\Sf{ey}\Df{d}\If{i}		&\Af{ye}\Sf{ey}\Ff{s}\If{i}		&\Af{ye}\Sf{ey}\Df{d}\Ef{a}		&\Af{ye}\Sf{ey}\df{\Ff{s}}		&\Af{ye}\Sf{ey}\Ff{s}\Ef{a}		&\Af{ye}\Sf{e}\If{y}			&\Af{ye}\Sf{ey}\\
\Qf{a}- expletive	&\Af{wu}-	&\Sf{yi}-	&\Qf{a}-\Af{wu}-\Sf{yi}-	&\Qf{a}\Af{ye}\Sf{ey}\Df{d}\Ff{z}\If{i}		&\Qf{a}\Af{ye}\Sf{ey}\Df{d}\If{i}	&\Qf{a}\Af{ye}\Sf{ey}\Ff{s}\If{i}	&\Qf{a}\Af{ye}\Sf{ey}\Df{d}\Ef{a}	&\Qf{a}\Af{ye}\Sf{ey}\df{\Ff{s}}	&\Qf{a}\Af{ye}\Sf{ey}\Ff{s}\Ef{a}	&\Qf{a}\Af{ye}\Sf{e}\If{y}		&\Qf{a}\Af{ye}\Sf{ey}\\
\Qf{ka}- qualifier	&\Af{wu}-	&\Sf{yi}-	&\Qf{ka}-\Af{wu}-\Sf{yi}-	&\Qf{ka}\Af{ye}\Sf{ey}\Df{d}\Ff{z}\If{i}	&\Qf{ka}\Af{ye}\Sf{ey}\Df{d}\If{i}	&\Qf{ka}\Af{ye}\Sf{ey}\Ff{s}\If{i}	&\Qf{ka}\Af{ye}\Sf{ey}\Df{d}\Ef{a}	&\Qf{ka}\Af{ye}\Sf{ey}\df{\Ff{s}}	&\Qf{ka}\Af{ye}\Sf{ey}\Ff{s}\Ef{a}	&\Qf{ka}\Af{ye}\Sf{e}\If{y}		&\Qf{ka}\Af{ye}\Sf{ey}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{wu}-	&\Sf{yi}-	&\Qf{x̱ʼe}-\Af{wu}-\Sf{yi}-	&\Qf{x̱ʼa}\Af{ye}\Sf{ey}\Df{d}\Ff{z}\If{i}	&\Qf{x̱ʼa}\Af{ye}\Sf{ey}\Df{d}\If{i}	&\Qf{x̱ʼa}\Af{ye}\Sf{ey}\Ff{s}\If{i}	&\Qf{x̱ʼa}\Af{ye}\Sf{ey}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{ye}\Sf{ey}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{ye}\Sf{ey}\Ff{s}\Ef{a}	&\Qf{x̱ʼa}\Af{ye}\Sf{e}\If{y}		&\Qf{x̱ʼa}\Af{ye}\Sf{ey}\\
\Qf{ji}- ‘inside’	&\Af{wu}-	&\Sf{yi}-	&\Qf{ji}-\Af{wu}-\Sf{yi}-	&\Qf{ji}\Af{ye}\Sf{ey}\Df{d}\Ff{z}\If{i}	&\Qf{ji}\Af{ye}\Sf{ey}\Df{d}\If{i}	&\Qf{ji}\Af{ye}\Sf{ey}\Ff{s}\If{i}	&\Qf{ji}\Af{ye}\Sf{ey}\Df{d}\Ef{a}	&\Qf{ji}\Af{ye}\Sf{ey}\df{\Ff{s}}	&\Qf{ji}\Af{ye}\Sf{ey}\Ff{s}\Ef{a}	&\Qf{ji}\Af{ye}\Sf{e}\If{y}		&\Qf{ji}\Af{ye}\Sf{ey}\\
\Qf{tu}- ‘inside’	&\Af{wu}-	&\Sf{yi}-	&\Qf{tu}-\Af{wu}-\Sf{yi}-	&\Qf{tu}\Af{ye}\Sf{ey}\Df{d}\Ff{z}\If{i}	&\Qf{tu}\Af{ye}\Sf{ey}\Df{d}\If{i}	&\Qf{tu}\Af{ye}\Sf{ey}\Ff{s}\If{i}	&\Qf{tu}\Af{ye}\Sf{ey}\Df{d}\Ef{a}	&\Qf{tu}\Af{ye}\Sf{ey}\df{\Ff{s}}	&\Qf{tu}\Af{ye}\Sf{ey}\Ff{s}\Ef{a}	&\Qf{tu}\Af{ye}\Sf{e}\If{y}		&\Qf{tu}\Af{ye}\Sf{ey}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect \textit{wu-} (incl.\ \textit{∅}-conj.\ habitual), second person plural subject \textit{yi-}}
\end{table}

%% Perfective, 2PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rrrr
		rrrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}			&\Ff{s}-\If{i}\rlap{-}			&\Df{t}-				&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-				&—\\
\midrule																															                                        
—			&\Af{wu}-	&\Sf{ji}-	&\Af{wu}-\Sf{ji}-		&\Af{ji}\Sf{ːj}.\Df{t}\Ff{s}\If{i}		&\Af{ji}\Sf{ːj}.\Df{t}\If{i}		&\Af{ji}\Sf{ːj}.\Ff{s}\If{i}		&\Af{ji}\Sf{ːj}.\Df{t}\Ef{a}		&\Af{ji}\Sf{ːj}\df{\Ff{s}}		&\Af{ji}\Sf{ːj}.\Ff{s}\Ef{a}		&\Af{ji}\Sf{ː}\If{j}			&\Af{ji}\Sf{ːj}\\
\Qf{ʔa}- expletive	&\Af{wu}-	&\Sf{ji}-	&\Qf{ʔa}-\Af{wu}-\Sf{ji}-	&\Qf{ʔa}.\Af{ji}\Sf{ːj}.\Df{t}\Ff{s}\If{i}	&\Qf{ʔa}.\Af{ji}\Sf{ːj}.\Df{t}\If{i}	&\Qf{ʔa}.\Af{ji}\Sf{ːj}.\Ff{s}\If{i}	&\Qf{ʔa}.\Af{ji}\Sf{ːj}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{ji}\Sf{ːj}\df{\Ff{s}}	&\Qf{ʔa}.\Af{ji}\Sf{ːj}.\Ff{s}\Ef{a}	&\Qf{ʔa}.\Af{ji}\Sf{ː}\If{j}		&\Qf{ʔa}.\Af{ji}\Sf{ːj}\\
\Qf{kʰa}- qualifier	&\Af{wu}-	&\Sf{ji}-	&\Qf{kʰa}-\Af{wu}-\Sf{ji}-	&\Qf{kʰa}.\Af{ji}\Sf{ːj}.\Df{t}\Ff{s}\If{i}	&\Qf{kʰa}.\Af{ji}\Sf{ːj}.\Df{t}\If{i}	&\Qf{kʰa}.\Af{ji}\Sf{ːj}.\Ff{s}\If{i}	&\Qf{kʰa}.\Af{ji}\Sf{ːj}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{ji}\Sf{ːj}\df{\Ff{s}}	&\Qf{kʰa}.\Af{ji}\Sf{ːj}.\Ff{s}\Ef{a}	&\Qf{kʰa}.\Af{ji}\Sf{ː}\If{j}		&\Qf{kʰa}.\Af{ji}\Sf{ːj}\\
\Qf{χʼe}- ‘mouth’	&\Af{wu}-	&\Sf{ji}-	&\Qf{χʼe}-\Af{wu}-\Sf{ji}-	&\Qf{χʼa}.\Af{ji}\Sf{ːj}.\Df{t}\Ff{s}\If{i}	&\Qf{χʼa}.\Af{ji}\Sf{ːj}.\Df{t}\If{i}	&\Qf{χʼa}.\Af{ji}\Sf{ːj}.\Ff{s}\If{i}	&\Qf{χʼa}.\Af{ji}\Sf{ːj}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{ji}\Sf{ːj}\df{\Ff{s}}	&\Qf{χʼa}.\Af{ji}\Sf{ːj}.\Ff{s}\Ef{a}	&\Qf{χʼa}.\Af{ji}\Sf{ː}\If{j}		&\Qf{χʼa}.\Af{ji}\Sf{ːj}\\
\Qf{tʃi}- ‘inside’	&\Af{wu}-	&\Sf{ji}-	&\Qf{tʃi}-\Af{wu}-\Sf{ji}-	&\Qf{tʃi}.\Af{ji}\Sf{ːj}.\Df{t}\Ff{s}\If{i}	&\Qf{tʃi}.\Af{ji}\Sf{ːj}.\Df{t}\If{i}	&\Qf{tʃi}.\Af{ji}\Sf{ːj}.\Ff{s}\If{i}	&\Qf{tʃi}.\Af{ji}\Sf{ːj}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{ji}\Sf{ːj}\df{\Ff{s}}	&\Qf{tʃi}.\Af{ji}\Sf{ːj}.\Ff{s}\Ef{a}	&\Qf{tʃi}.\Af{ji}\Sf{ː}\If{j}		&\Qf{tʃi}.\Af{ji}\Sf{ːj}\\
\Qf{tʰu}- ‘inside’	&\Af{wu}-	&\Sf{ji}-	&\Qf{tʰu}-\Af{wu}-\Sf{ji}-	&\Qf{tʰu}.\Af{ji}\Sf{ːj}.\Df{t}\Ff{s}\If{i}	&\Qf{tʰu}.\Af{ji}\Sf{ːj}.\Df{t}\If{i}	&\Qf{tʰu}.\Af{ji}\Sf{ːj}.\Ff{s}\If{i}	&\Qf{tʰu}.\Af{ji}\Sf{ːj}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{ji}\Sf{ːj}\df{\Ff{s}}	&\Qf{tʰu}.\Af{ji}\Sf{ːj}.\Ff{s}\Ef{a}	&\Qf{tʰu}.\Af{ji}\Sf{ː}\If{j}		&\Qf{tʰu}.\Af{ji}\Sf{ːj}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect /{wu-}/ (incl.\ \textit{∅}-conj.\ habitual), second person plural subject /{ji-}/, IPA}
\end{table}

\clearpage
%% Perfective, 4H
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}			&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}\rlap{-}	&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}\rlap{-}	&\If{i}-				&—\\
\midrule
—			&\Af{wu}-	&\Sf{du}-	&\Af{wu}-\Sf{du}-		&\Af{wu}\Sf{du}\Df{d}\Ff{z}\If{i}		&⁎			&⁎			&⁎		&\Af{wu}\Sf{du}\df{\Ff{s}}		&⁎		&\Af{wu}\Sf{du}\If{w}\Ef{a}		&\Af{wu}\Sf{du}\\
\Qf{a}- expletive	&\Af{wu}-	&\Sf{du}-	&\Qf{a}-\Af{wu}-\Sf{du}-	&\Qf{a}\Af{w}\Sf{du}\Df{d}\Ff{z}\If{i}		&⁎			&⁎			&⁎		&\Qf{a}\Af{w}\Sf{du}\df{\Ff{s}}		&⁎		&\Qf{a}\Af{w}\Sf{du}\If{w}\Ef{a}	&\Qf{a}\Af{w}\Sf{du}\\
\Qf{ka}- qualifier	&\Af{wu}-	&\Sf{du}-	&\Qf{ka}-\Af{wu}-\Sf{du}-	&\Qf{ka}\Af{w}\Sf{du}\Df{d}\Ff{z}\If{i}		&⁎			&⁎			&⁎		&\Qf{ka}\Af{w}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ka}\Af{w}\Sf{du}\If{w}\Ef{a}	&\Qf{ka}\Af{w}\Sf{du}\\
\Qf{x̱ʼe}- ‘mouth’	&\Af{wu}-	&\Sf{du}-	&\Qf{x̱ʼe}-\Af{wu}-\Sf{du}-	&\Qf{x̱ʼa}\Af{w}\Sf{du}\Df{d}\Ff{z}\If{i}	&⁎			&⁎			&⁎		&\Qf{x̱ʼa}\Af{w}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{x̱ʼa}\Af{w}\Sf{du}\If{w}\Ef{a}	&\Qf{x̱ʼa}\Af{w}\Sf{du}\\
\Qf{ji}- ‘hand’		&\Af{wu}-	&\Sf{du}-	&\Qf{ji}-\Af{wu}-\Sf{du}-	&\Qf{ji}\Af{w}\Sf{du}\Df{d}\Ff{z}\If{i}		&⁎			&⁎			&⁎		&\Qf{ji}\Af{w}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{ji}\Af{w}\Sf{du}\If{w}\Ef{a}	&\Qf{ji}\Af{w}\Sf{du}\\
\Qf{tu}- ‘inside’	&\Af{wu}-	&\Sf{du}-	&\Qf{tu}-\Af{wu}-\Sf{du}-	&\Qf{tu}\Af{w}\Sf{du}\Df{d}\Ff{z}\If{i}		&⁎			&⁎			&⁎		&\Qf{tu}\Af{w}\Sf{du}\df{\Ff{s}}	&⁎		&\Qf{tu}\Af{w}\Sf{du}\If{w}\Ef{a}	&\Qf{tu}\Af{w}\Sf{du}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect \textit{wu-} (incl.\ \textit{∅}-conj.\ habitual), fourth person (indefinite) human subject \textit{du-}}
\end{table}

%% Perfective, 4H, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		rccc
		rcrr}
\toprule
(IPA)			&		&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
											\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}	& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}			&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-	&\Df{t}-\Ff{s}\rlap{-}			&\Ff{s}-	&\If{i}-				&—\\
\midrule
—			&\Af{wu}-	&\Sf{tu}-	&\Af{wu}-\Sf{tu}-		&\Af{wu}.\Sf{tu}.\Df{t}\Ff{s}\If{i}		&⁎			&⁎			&⁎		&\Af{wu}.\Sf{tu}\df{\Ff{s}}		&⁎		&\Af{wu}.\Sf{tu}.\If{w}\Ef{a}		&\Af{wu}.\Sf{tu}\\
\Qf{ʔa}- expletive	&\Af{wu}-	&\Sf{tu}-	&\Qf{ʔa}-\Af{wu}-\Sf{tu}-	&\Qf{ʔa}\Af{w}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{ʔa}\Af{w}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{ʔa}\Af{w}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{ʔa}\Af{w}.\Sf{tu}\\
\Qf{kʰa}- qualifier	&\Af{wu}-	&\Sf{tu}-	&\Qf{kʰa}-\Af{wu}-\Sf{tu}-	&\Qf{kʰa}\Af{w}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{kʰa}\Af{w}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{kʰa}\Af{w}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{kʰa}\Af{w}.\Sf{tu}\\
\Qf{χʼe}- ‘mouth’	&\Af{wu}-	&\Sf{tu}-	&\Qf{χʼe}-\Af{wu}-\Sf{tu}-	&\Qf{χʼa}\Af{w}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{χʼa}\Af{w}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{χʼa}\Af{w}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{χʼa}\Af{w}.\Sf{tu}\\
\Qf{tʃi}- ‘hand’	&\Af{wu}-	&\Sf{tu}-	&\Qf{tʃi}-\Af{wu}-\Sf{tu}-	&\Qf{tʃi}\Af{w}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{tʃi}\Af{w}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{tʃi}\Af{w}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{tʃi}\Af{w}.\Sf{tu}\\
\Qf{tʰu}- ‘inside’	&\Af{wu}-	&\Sf{tu}-	&\Qf{tʰu}-\Af{wu}-\Sf{tu}-	&\Qf{tʰu}\Af{w}.\Sf{tu}.\Df{t}\Ff{s}\If{i}	&⁎			&⁎			&⁎		&\Qf{tʰu}\Af{w}.\Sf{tu}\df{\Ff{s}}	&⁎		&\Qf{tʰu}\Af{w}.\Sf{tu}.\If{w}\Ef{a}	&\Qf{tʰu}\Af{w}.\Sf{tu}\\
\bottomrule
\end{tabular}
\caption{Perfective aspect /{wu-}/ (incl.\ \textit{∅}-conj.\ habitual), fourth person (indefinite) human subject /{tu-}/}
\end{table}

\clearpage
%%%
%%% Prospective aspect.
%%%

\section{Prospective aspect prefixes \textit{w-g-g̱-}}\label{sec:prosp}

\begin{multicols}{2}
\noindent
Prospective aspect – also inaccurately called ‘future tense’ by analogy with English – is expressed with three prefixes \fm{w-}, \fm{g-}, and \fm{g̱-}.
The \fm{w-} /\ipa{ʷ}/ irrealis prefix is an allomorph of the irrealis prefix that occurs with the prospective aspect and with comparatives.
The \fm{g-} /\ipa{k}/ conjugation prefix is identified as a conjugation prefix although it is used for the prospective aspect regardless of the verb’s conjugation class membership.
This is similar to the use of the \fm{n-} /\ipa{n}/ conjugation prefix for all prospective aspect forms regardless of the verb’s conjugation class.
The \fm{g̱-} /\ipa{q}/ modal prefix is associated with modality, being found also in the hortative mood and the potential modality.
The \fm{g̱-} modal prefix is homophonous with the \fm{g̱-} conjugation prefix but the two can occur together so they are not identical.
\end{multicols}

\clearpage
%% Prospective, 3
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
			&			&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
												\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes			&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}				&\Ff{s}-				&\If{i}-	&—\\
\midrule
—			&\Rf{w}-\Af{g}-\Mf{g̱}-	&—		&\Rf{w}-\Af{g}-\Mf{g̱}-		&⁎				&⁎			&⁎			&\Af{g}\Rf{u}\Mf{x̱}\Df{d}\Ef{a}		&\Af{g}\Rf{u}\Mf{g̱}\Ef{a}\df{\Ff{s}}		&\Af{g}\Rf{u}\Mf{x̱}\Ff{s}\Ef{a}		&⁎		&\Af{g}\Rf{u}\Mf{g̱}\Ef{a}\\
			&			&		&				&				&			&			&					&…\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\df{\Ff{s}}		&					&		&…\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\\
\Qf{a}- arg./expl.	&\Rf{w}-\Af{g}-\Mf{g̱}-	&—		&\Qf{a}-\Rf{w}-\Af{g}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{a}\Af{g}\Rf{u}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{a}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{a}\Af{g}\Rf{u}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\\
\Qf{ka}- qualifier	&\Rf{w}-\Af{g}-\Mf{g̱}-	&—		&\Qf{ka}-\Rf{w}-\Af{g}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{ka}\Af{g}\Rf{u}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{ka}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{ka}\Af{g}\Rf{u}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&—		&\Qf{x̱ʼe}-\Rf{w}-\Af{g}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Af{g}\Rf{u}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{g}\Rf{u}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Rf{w}-\Af{g}-\Mf{g̱}-	&—		&\Qf{ji}-\Rf{w}-\Af{g}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{ji}\Af{g}\Rf{u}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{ji}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{ji}\Af{g}\Rf{u}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&—		&\Qf{tu}-\Rf{w}-\Af{g}-\Mf{g̱}-	&⁎				&⁎			&⁎			&\Qf{tu}\Af{g}\Rf{u}\Mf{x̱}\Df{d}\Ef{a}	&\Qf{tu}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{tu}\Af{g}\Rf{u}\Mf{x̱}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Af{k}\Mf{g̱}\Rf{w}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect \textit{w-g-g̱-}, unmarked subject (third person or no subject)}
\end{table}

%% Prospective, 3, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrcr}
\toprule
(IPA)			&			&		&				&\multicolumn{8}{c}{Classifier prefixes}\\
												\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes			&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-						&\Df{t}-\Ff{s}\rlap{-}					&\Ff{s}-						&\If{i}-	&—\\
\midrule
—			&\Rf{ʷ}-\Af{k}-\Mf{q}-	&—		&\Rf{ʷ}-\Af{k}-\Mf{q}-		&⁎				&⁎			&⁎			&\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}			&\Af{k}\Rf{ʷu}.\Mf{q}\Ef{a}\df{\Ff{s}}			&\Af{k}\Rf{ʷu}\Mf{χ}\Ff{s}\Ef{a}			&⁎		&\Af{k}\Rf{ʷu}.\Mf{q}\Ef{a}\\
			&			&		&				&				&			&			&							&…\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\df{\Ff{s}}			&							&		&…\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\\
\Qf{ʔa}- arg./expl.	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&—		&\Qf{ʔa}-\Rf{ʷ}-\Af{k}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{ʔa}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}		&\Qf{ʔa}\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\df{\Ff{s}}		&\Qf{ʔa}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}		&⁎		&\Qf{ʔa}\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&—		&\Qf{kʰa}-\Rf{ʷ}-\Af{k}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{kʰa}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}	&\Qf{kʰa}\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\df{\Ff{s}}		&\Qf{kʰa}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}	&⁎		&\Qf{kʰa}\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&—		&\Qf{χʼe}-\Rf{ʷ}-\Af{k}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{χʼa}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}	&\Qf{χʼa}\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\df{\Ff{s}}		&\Qf{χʼa}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}	&⁎		&\Qf{χʼa}\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&—		&\Qf{tʃi}-\Rf{ʷ}-\Af{k}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{tʃi}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}	&\Qf{tʃi}\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\df{\Ff{s}}		&\Qf{tʃi}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʃi}\Af{k}.\Mf{q}\Rf{ʷ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&—		&\Qf{tʰu}-\Rf{ʷ}-\Af{k}-\Mf{q}-	&⁎				&⁎			&⁎			&\Qf{tʰu}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Df{t}\Ef{a}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Rf{ʷ}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}.\Af{k}\Rf{ʷu}\Mf{χ}\Rf{ʷ}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Rf{ʷ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect /{ʷ-k-q-}/, unmarked subject (third person or no subject), IPA}
\end{table}

\clearpage
%% Prospective, 1SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-						&\Df{d}-\Ff{s}\rlap{-}					&\Ff{s}-						&\If{i}-	&—\\
\midrule
—			&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{x̱}-	&\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{x̱}-		&⁎				&⁎			&⁎			&\Af{k}\Rf{u}\mf{\Sf{ḵ}}\Ef{a}\Df{d}\Ef{a}		&\Af{k}\Rf{u}\mf{\Sf{ḵ}}\Ef{a}\df{\Ff{s}}		&\Af{k}\Rf{u}\mf{\Sf{ḵ}}\Ef{a}\Ff{s}\Ef{a}		&⁎		&\Af{k}\Rf{u}\mf{\Sf{ḵ}}\Ef{a}\\
			&			&		&					&				&			&			&…\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}		&							&							&		&…\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
\Qf{a}- expletive	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{a}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{x̱}-	&⁎				&⁎			&⁎			&\Qf{a}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}	&\Qf{a}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}		&\Qf{a}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
\Qf{ka}- qualifier	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{ka}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{x̱}-	&⁎				&⁎			&⁎			&\Qf{ka}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}	&\Qf{ka}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{ka}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{x̱ʼe}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{x̱}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
\Qf{ji}- ‘hand’		&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{ji}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{x̱}-	&⁎				&⁎			&⁎			&\Qf{ji}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}	&\Qf{ji}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{ji}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
\Qf{tu}- ‘inside’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{x̱}-	&\Qf{tu}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{x̱}-	&⁎				&⁎			&⁎			&\Qf{tu}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Df{d}\Ef{a}	&\Qf{tu}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\df{\Ff{s}}	&\Qf{tu}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Af{k}\mf{\Sf{ḵ}}\Rf{w}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect \textit{w-g-g̱-}, first person singular subject \textit{x̱-}}
\end{table}

%% Prospective, 1SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
(IPA)			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-							&\Df{t}-\Ff{s}\rlap{-}						&\Ff{s}-							&\If{i}-	&—\\
\midrule
—			&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{χ}-	&\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{χ}-		&⁎				&⁎			&⁎			&\Af{k}\Sf{ʰ}\Rf{ʷu}.\Mf{q}\Sf{ʰ}\Ef{a}.\Df{t}\Ef{a}		&\Af{k}\Sf{ʰ}\Rf{ʷu}.\Mf{q}\Sf{ʰ}\Ef{a}\df{\Ff{s}}		&\Af{k}\Sf{ʰ}\Rf{u}.\Mf{q}\Sf{ʰ}\Ef{a}.\Ff{s}\Ef{a}		&⁎		&\Af{k}\Sf{ʰ}\Rf{ʷu}.\Mf{q}\Sf{ʰ}\Ef{a}\\
			&			&		&					&				&			&			&…\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}			&								&								&		&…\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
\Qf{ʔa}- expletive	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{χ}-	&\Qf{ʔa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{ʔa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}		&\Qf{ʔa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}		&\Qf{ʔa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{w}\Ef{a}.\Ff{s}\Ef{a}		&⁎		&\Qf{ʔa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
\Qf{kʰa}- qualifier	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{χ}-	&\Qf{kʰa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{kʰa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}		&\Qf{kʰa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}		&\Qf{kʰa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{w}\Ef{a}.\Ff{s}\Ef{a}		&⁎		&\Qf{kʰa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
\Qf{χʼe}- ‘mouth’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{χ}-	&\Qf{χʼe}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{χʼa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}		&\Qf{χʼa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}		&\Qf{χʼa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{w}\Ef{a}.\Ff{s}\Ef{a}		&⁎		&\Qf{χʼa}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
\Qf{tʃi}- ‘hand’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{χ}-	&\Qf{tʃi}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{tʃi}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}		&\Qf{tʃi}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}		&\Qf{tʃi}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{w}\Ef{a}.\Ff{s}\Ef{a}		&⁎		&\Qf{tʃi}\Af{k}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
\Qf{tʰu}- ‘inside’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{χ}-	&\Qf{tʰu}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{χ}-	&⁎				&⁎			&⁎			&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}.\Df{t}\Ef{a}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\df{\Ff{s}}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Sf{ʰ}\Rf{w}\Ef{a}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Sf{ʰ}\Rf{ʷ}\Ef{a}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect /{ʷ-k-q-}/, first person singular subject /{χ-}/, IPA}
\end{table}

\clearpage
%% Prospective, 1PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-					&\Df{d}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-	&—\\
\midrule
—			&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{tu-}	&\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{tu-}		&⁎				&⁎			&⁎			&\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}		&\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\df{\Ff{s}}		&\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}		&⁎		&\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\\
\Qf{a}- expletive	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{tu-}	&\Qf{a}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\\
\Qf{ka}- qualifier	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{tu-}	&\Qf{ka}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{tu-}	&\Qf{x̱ʼe}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\\
\Qf{ji}- ‘hand’		&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{tu-}	&\Qf{ji}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\\
\Qf{tu}- ‘inside’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{tu-}	&\Qf{tu}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{tu}-	&⁎				&⁎			&⁎			&\Qf{tu}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Df{d}\Ef{a}	&\Qf{tu}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\df{\Ff{s}}	&\Qf{tu}\Af{g}\Ef{a}\Mf{x̱}\Sf{tu}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Af{g}\Ef{a}\Mf{x̱}\Sf{too}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect \textit{w-g-g̱-}, first person plural subject \textit{tu-}}
\end{table}

%% Prospective, 1PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
(IPA)			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}				
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-						&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-							&\If{i}-	&—\\
\midrule
—			&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tʰu}-	&\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tʰu-}		&⁎				&⁎			&⁎			&\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}		&\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}		&\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}		&⁎		&\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\\
\Qf{ʔa}- expletive	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tʰu}-	&\Qf{ʔa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tʰu}-	&⁎				&⁎			&⁎			&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}	&⁎		&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\\
\Qf{kʰa}- qualifier	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tʰu}-	&\Qf{kʰa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tʰu}-&⁎				&⁎			&⁎			&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}	&⁎		&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\\
\Qf{χʼe}- ‘mouth’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tʰu}-	&\Qf{χʼe}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tʰu}-&⁎				&⁎			&⁎			&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}	&⁎		&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\\
\Qf{tʃi}- ‘hand’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tʰu}-	&\Qf{tʃi}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tʰu}-&⁎				&⁎			&⁎			&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\\
\Qf{tʰu}- ‘inside’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tʰu}-	&\Qf{tʰu}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tʰu}-&⁎				&⁎			&⁎			&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Df{t}\Ef{a}	&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\df{\Ff{s}}	&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰu}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tʰuː}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect /{ʷ-k-q-}/, first person plural subject /{tʰu-}/}
\end{table}

\clearpage
%% Prospective, 2SG
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-				&\Df{d}-\Ff{s}\rlap{-}			&\Ff{s}-				&\If{i}-	&—\\
\midrule
—			&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{i}-	&\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{i}-		&⁎				&⁎			&⁎			&\Af{g}\Ef{a}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Af{g}\Ef{a}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Af{g}\Ef{a}\Sf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Af{g}\Ef{a}\Mf{g̱}\Sf{ee}\\
			&			&		&					&				&			&			&…\Af{k}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&					&					&		&…\Af{k}\Mf{g̱}\Sf{ee}\\
\Qf{a}- expletive	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{i}-	&\Qf{a}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{a}\Af{k}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{a}\Af{k}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{a}\Af{k}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\Af{k}\Mf{g̱}\Sf{ee}\\
\Qf{ka}- qualifier	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{i}-	&\Qf{ka}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{ka}\Af{k}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{ka}\Af{k}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{ka}\Af{k}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Af{k}\Mf{g̱}\Sf{ee}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{i}-	&\Qf{x̱ʼe}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Af{k}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{k}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{k}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Af{k}\Mf{g̱}\Sf{ee}\\
\Qf{ji}- ‘hand’		&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{i}-	&\Qf{ji}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{ji}\Af{k}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{ji}\Af{k}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{ji}\Af{k}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Af{k}\Mf{g̱}\Sf{ee}\\
\Qf{tu}- ‘inside’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{i}-	&\Qf{tu}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{tu}\Af{k}\Mf{g̱}\Sf{i}\Df{d}\Ef{a}	&\Qf{tu}\Af{k}\Mf{g̱}\Sf{ee}\df{\Ff{s}}	&\Qf{tu}\Af{k}\Mf{g̱}\Sf{i}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Af{k}\Mf{g̱}\Sf{ee}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect \textit{w-g-g̱-}, second person singular subject \textit{i-}}
\end{table}

%% Prospective, 2SG, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
(IPA)			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-					&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-	&—\\
\midrule
—			&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{i}-	&\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{i}-		&⁎				&⁎			&⁎			&\Af{k}\Ef{a}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}		&\Af{k}\Ef{a}.\Mf{q}\Sf{iː}\df{\Ff{s}}		&\Af{k}\Ef{a}.\Sf{q}\Sf{i}.\Ff{s}\Ef{a}		&⁎		&\Af{k}\Ef{a}.\Mf{q}\Sf{iː}\\
			&			&		&					&				&			&			&…\Af{k}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}		&						&						&		&…\Af{k}.\Mf{q}\Sf{iː}\\
\Qf{ʔa}- expletive	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{i}-	&\Qf{ʔa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{ʔa}\Af{k}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{ʔa}\Af{k}.\Mf{q}\Sf{iː}\df{\Ff{s}}		&\Qf{ʔa}\Af{k}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{ʔa}\Af{k}.\Mf{q}\Sf{iː}\\
\Qf{kʰa}- qualifier	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{i}-	&\Qf{kʰa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{kʰa}\Af{k}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{kʰa}\Af{k}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{kʰa}\Af{k}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{kʰa}\Af{k}.\Mf{q}\Sf{iː}\\
\Qf{χʼe}- ‘mouth’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{i}-	&\Qf{χʼe}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{χʼa}\Af{k}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{χʼa}\Af{k}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{χʼa}\Af{k}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{χʼa}\Af{k}.\Mf{q}\Sf{iː}\\
\Qf{tʃi}- ‘hand’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{i}-	&\Qf{tʃi}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{tʃi}\Af{k}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʃi}\Af{k}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{tʃi}\Af{k}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʃi}\Af{k}.\Mf{q}\Sf{iː}\\
\Qf{tʰu}- ‘inside’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{i}-	&\Qf{tʰu}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{i}-	&⁎				&⁎			&⁎			&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Sf{i}.\Df{t}\Ef{a}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Sf{iː}\df{\Ff{s}}	&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Sf{i}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}\Af{k}\Qf{ʷ}.\Mf{q}\Sf{iː}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect /{ʷ-k-q-}/, second person singular subject /{i-}/}
\end{table}

\clearpage
%% Prospective, 2PL
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-					&\Df{d}-\Ff{s}\rlap{-}				&\Ff{s}-					&\If{i}-	&—\\
\midrule
—			&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{yi}-	&\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{yi}-		&⁎				&⁎			&⁎			&\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}		&\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\df{\Ff{s}}		&\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}		&⁎		&\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\\
\Qf{a}- expletive	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{yi}-	&\Qf{a}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\df{\Ff{s}}	&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\\
\Qf{ka}- qualifier	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{yi}-	&\Qf{ka}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\df{\Ff{s}}	&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{yi}-	&\Qf{x̱ʼe}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\df{\Ff{s}}	&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\\
\Qf{ji}- ‘hand’		&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{yi}-	&\Qf{ji}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\df{\Ff{s}}	&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\\
\Qf{tu}- ‘inside’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{yi}-	&\Qf{tu}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{yi}-	&⁎				&⁎			&⁎			&\Qf{tu}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Df{d}\Ef{a}	&\Qf{tu}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\df{\Ff{s}}	&\Qf{tu}\Af{g}\Ef{a}\Mf{x̱}\Sf{yi}\Ff{s}\Ef{a}	&⁎		&\Qf{tu}\Af{g}\Ef{a}\Mf{x̱}\Sf{yee}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect \textit{w-g-g̱-}, second person plural subject \textit{yi-}}
\end{table}

%% Prospective, 2PL, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
(IPA)			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-						&\Df{t}-\Ff{s}\rlap{-}					&\Ff{s}-						&\If{i}-	&—\\
\midrule
—			&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{ji}-	&\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{ji}-		&⁎				&⁎			&⁎			&\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Df{d}\Ef{a}		&\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\df{\Ff{s}}			&\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}		&⁎		&\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\\
\Qf{ʔa}- expletive	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{ji}-	&\Qf{ʔa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Df{d}\Ef{a}	&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\df{\Ff{s}}		&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}	&⁎		&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\\
\Qf{kʰa}- qualifier	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{ji}-	&\Qf{kʰa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Df{d}\Ef{a}	&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\df{\Ff{s}}	&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}	&⁎		&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\\
\Qf{χʼe}- ‘mouth’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{ji}-	&\Qf{χʼe}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Df{d}\Ef{a}	&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\df{\Ff{s}}	&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}	&⁎		&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\\
\Qf{tʃi}- ‘hand’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{ji}-	&\Qf{tʃi}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Df{d}\Ef{a}	&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\df{\Ff{s}}	&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\\
\Qf{tʰu}- ‘inside’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{ji}-	&\Qf{tʰu}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{ji}-	&⁎				&⁎			&⁎			&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Df{d}\Ef{a}	&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\df{\Ff{s}}	&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{ji}.\Ff{s}\Ef{a}	&⁎		&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{jiː}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect /{ʷ-k-q-}/, second person plural subject /{ji-}/}
\end{table}

\clearpage
%% Prospective, 4H
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{d}-\Ff{s}-\If{i}\rlap{-}	&\Df{d}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{d}-	&\Df{d}-\Ff{s}\rlap{-}				&\Ff{s}-	&\If{i}-	&—\\
\midrule
—			&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{du}-	&\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{du-}		&⁎				&⁎			&⁎			&⁎		&\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\df{\Ff{s}}		&⁎		&⁎		&\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\\
\Qf{a}- expletive	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{du}-	&\Qf{a}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{a}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\\
\Qf{ka}- qualifier	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{du}-	&\Qf{ka}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{ka}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\\
\Qf{x̱ʼe}- ‘mouth’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{du}-	&\Qf{x̱ʼe}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{x̱ʼa}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\\
\Qf{ji}- ‘hand’		&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{du}-	&\Qf{ji}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{ji}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\\
\Qf{tu}- ‘inside’	&\Rf{w}-\Af{g}-\Mf{g̱}-	&\Sf{du}-	&\Qf{du}-\Rf{w}-\Af{g}-\Mf{g̱}-\Sf{du}-	&⁎				&⁎			&⁎			&⁎		&\Qf{du}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\df{\Ff{s}}	&⁎		&⁎		&\Qf{du}\Af{g}\Ef{a}\Mf{x̱}\Sf{du}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect \textit{w-g-g̱-}, fourth person (indefinite) human subject \textit{du-}}
\end{table}

%% Prospective, 4H, IPA
\begin{table}
\centerfloat
\begin{tabular}{lccr
		cccr
		rrrr}
\toprule
(IPA)			&			&		&					&\multicolumn{8}{c}{Classifier prefixes}\\
													\cmidrule(lr){5-12}
Disjunct\rlap{\quad{}+}	& Asp.\rlap{ +}		& Subj.\rlap{ →}& Prefixes				&\Df{t}-\Ff{s}-\If{i}\rlap{-}	&\Df{t}-\If{i}\rlap{-}	&\Ff{s}-\If{i}\rlap{-}	&\Df{t}-	&\Df{t}-\Ff{s}\rlap{-}				&\Ff{s}-	&\If{i}-	&—\\
\midrule
—			&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tu}-	&\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tu-}		&⁎				&⁎			&⁎			&⁎		&\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\df{\Ff{s}}		&⁎		&⁎		&\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\\
\Qf{ʔa}- expletive	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tu}-	&\Qf{ʔa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\df{\Ff{s}}	&⁎		&⁎		&\Qf{ʔa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\\
\Qf{kʰa}- qualifier	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tu}-	&\Qf{kʰa}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\df{\Ff{s}}	&⁎		&⁎		&\Qf{kʰa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\\
\Qf{χʼe}- ‘mouth’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tu}-	&\Qf{χʼe}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\df{\Ff{s}}	&⁎		&⁎		&\Qf{χʼa}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\\
\Qf{tʃi}- ‘hand’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tu}-	&\Qf{tʃi}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\df{\Ff{s}}	&⁎		&⁎		&\Qf{tʃi}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\\
\Qf{tʰu}- ‘inside’	&\Rf{ʷ}-\Af{k}-\Mf{q}-	&\Sf{tu}-	&\Qf{tʰu}-\Rf{ʷ}-\Af{k}-\Mf{q}-\Sf{tu}-	&⁎				&⁎			&⁎			&⁎		&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\df{\Ff{s}}	&⁎		&⁎		&\Qf{tʰu}.\Af{k}\Ef{a}\Mf{χ}.\Sf{tu}\\
\bottomrule
\end{tabular}
\caption{Prospective aspect /{ʷ-k-q-}/, fourth person (indefinite) human subject /{tu-}/, IPA}
\end{table}

\end{document}
